---
title: "npm_preprocessing"
author: "adam gordon-fennell"
date: '2023-05-18'
output: html_document
---

todo:
- check on cat6 connectivity between boxes and clock arduino (ids are not as expected)
- increase sampling rate (many samples below 20Hz)
- resample time prior to exporting dataset
- convert arduino beh dataset to system time using clock approach
- determine what is in the TDT output and replicate... 
- 

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r}
library(tidyverse)
library(afex)
library(emmeans)
library(janitor)
library(readxl)
library(googlesheets4)
library(ggh4x) # force_panelsizes
library(arrow)
library(zoo)
library(lubridate)
library(patchwork)
library(ggbeeswarm)
library(ggpubr) #r2 on correlation
library(rstatix)
library(plotly)
library(viridis)

source('.//functions/r_plots.R')
source('.//functions/r_stats.R')
source('.//functions/r_general.R')
source('.//functions/r_fp.R')
source('./functions/r_head_fixed_processing.R')
```

# setup
```{r}
dir_npm_raw <- './data//data_npm/data_raw/'
dir_npm_extracted <- './data//data_npm/data_extracted/'
dir_npm_processed <- './data//data_npm/data_processed/'
  
log_npm <- read_sheet('https://docs.google.com/spreadsheets/d/1v-G8GHYPGtJWXARZYqcndO03d23umsTo98BAb5_WnrY/edit#gid=0', na = c('', 'NA'))

log_data_stim_char_param <- read_sheet("https://docs.google.com/spreadsheets/d/1GOVg5to5MliU6TFIBCR9YUZYx-b4dYGB-qd2uiX7Vrc/edit#gid=0", sheet = 'stim_parameters')

log_data_stim <- read_sheet("https://docs.google.com/spreadsheets/d/1GOVg5to5MliU6TFIBCR9YUZYx-b4dYGB-qd2uiX7Vrc/edit#gid=0")

manual_experiments <- 'abw'

```

# pre-processsing
## arduino
```{r}
# directories 
dir_arduino_extraction <- './data/arduino/extracted/'
dir_arduino_processed <- './data/arduino/processed/'
dir_arduino_raw <- './data/arduino/raw/'
dir_output <- './analysis_output/'

key_events <- read_sheet('https://docs.google.com/spreadsheets/d/1e3ltGi7oNBvIpCgUCcZL2Jm8nmv8eVBoPXvdoowNZx4') 
log_subject <- read_sheet("https://docs.google.com/spreadsheets/d/17GC2tzKHKuWCZAyj84ubsPTvLsfepKFjl_LnaZ8jxdw/edit#gid=0", na = 'NA', sheet = 'subject')
```




```{r, meassage = FALSE}
file_format_output <- 'csv'

manual_blocknames <- log_npm %>%
  filter(experiment == 'abw') %>%
  filter(procedure %>% str_detect('opto_char')) %>%
  select(blockname) %>%
  unique() %>%
  pull(blockname)

extract_serial_output(dir_arduino_raw, key_events, dir_arduino_extraction, manual_experiments, manual_blocknames = manual_blocknames, file_format_output, overwrite = 0)
```


## npm
```{r, meassage = FALSE}
manual_sessions_to_process <- log_npm %>%
  filter(experiment == manual_experiments) %>%
  filter(procedure %>% str_detect('opto_char')) %>%
  filter(exclude != 1) %>%
  pull(session_name) %>% unique() 

manual_sessions_to_process <- 
  manual_sessions_to_process[
    manual_sessions_to_process %>% str_detect('08_12') |
      manual_sessions_to_process %>% str_detect('08_14') |
      manual_sessions_to_process %>% str_detect('08_15')
      ]

npm_extract(log_npm, dir_npm_raw, dir_npm_extracted, manual_session_names = manual_sessions_to_process, overwrite = 0, filter_red_opto_sd = 5)

fp_preprocess_npm(
  dir_npm_extracted,
  dir_npm_processed,
  log_npm,
  manual_session_names = manual_sessions_to_process,
  overwrite = 0,
  dir_arduino_extracted = './data/arduino/extracted/'
)
```


## tdt
```{r}
# filter events
# error in ttl recoridng with multiple pulses instead of a single pulse per stim period, filtered here to match 50 trials of stim in npm

redo_filtering <- 0

if(redo_filtering){
  fns <- list.files('./data//data_fp/data_extracted')
  fns <- fns[fns %>% str_detect('abw')]
  fns <- fns[fns %>% str_detect('_epocs_data.feather')]
  
  for(fn in fns){
    df <- read_feather(str_c('./data//data_fp/data_extracted/', fn))
    
    df <- df %>%
      filter(name == 'PC1/') %>%
      mutate(dur = offset - onset)  %>%
      filter(dur > 0.9) %>%
      
      mutate(iti = onset - lag(onset)) %>%
      filter(iti > 0.5 | is.na(iti)) %>%
      mutate(trial_num = row_number()) %>%
      filter(trial_num > max(trial_num) - 50) %>%
      select(-dur, -iti, -trial_num)
    
    df %>% 
      write_feather(str_c('./data//data_fp/data_extracted/', fn))
  }
}
```

```{r, echo = TRUE}
dir_tdt_extracted <- './data//data_fp/data_extracted'
dir_tdt_processed <- './data//data_fp/data_processed'

log_tdt <- read_sheet("https://docs.google.com/spreadsheets/d/1-_aV_inR-hg108or2Pj2K7iWZRnt8pg4-IZNe1sLVQ8", na = 'NA') 
```

```{r}
fp_preprocess(dir_tdt_extracted, dir_tdt_processed, log_tdt, manual_experiments = c('abw'), manual_blocknames = c('2024_02_02_abw01'), overwrite = 0)
```

## functions
```{r}
key_regions <- tibble(
  region_temp = c('nac', 'dms', 'dls', 'ts'),
  region_label = c('NAcCR', 'DMS', 'DLS', 'TS')
)

format_regions <- function(df, var_region, key_regions){
  df %>%
    rename(region_temp = !!as.name(var_region)) %>%
    left_join(key_regions) %>%
    mutate(region_label = factor(region_label, levels = key_regions$region_label)) %>%
    select(-region_temp) %>%
    rename(!!var_region := region_label) %>%
    select(!!var_region, everything())
}
```


```{r}
library(corrplot)
library(Hmisc)

tidy_cor_output_reshape <- function(df, n_table, var_name){
  df_tidy <- df[[n_table]] %>%
    as_tibble()
  
  df_tidy <- df_tidy %>%
    mutate(var_y = colnames(df_tidy)) %>%
    gather('var_x', !!as.name(var_name), -var_y) 
  
  return(df_tidy)
}

tidy_cor_output <- function(df){
  tidy_cor_output_reshape(df, 1, 'r') %>%
    left_join(tidy_cor_output_reshape(df, 2, 'n'), by = c("var_y", "var_x")) %>%
    left_join(tidy_cor_output_reshape(df, 3, 'p'), by = c("var_y", "var_x"))
}


get_cormatrix <- function(df){
  df_corr = rcorr(as.matrix(df))
  tidy_cor_output(df_corr)
}

tidy_cormatrix <- function(df, var_cors, var_groups = NA){
  require(Hmisc)
  
  df <- df %>%
    ungroup()


  if(sum(is.na(var_groups)) > 0){
    df <- df %>% select(var_cors)
  
    df %>%
      group_modify(~ get_cormatrix(.))
    
  } else {
    df <- df %>% select(var_cors, var_groups)
    
    df %>%
      group_by_at(var_groups) %>%
      group_modify(~ get_cormatrix(.))
    
  }
}

```


```{r}
filter_counterbalance_days <- function(df){
  df %>%
    filter(
      blockname %>% str_detect('2024_01_16') | #cohort1
      blockname %>% str_detect('2024_01_18') | 
      blockname %>% str_detect('2024_01_17') |
      blockname %>% str_detect('2024_01_19') |
      blockname %>% str_detect('2024_01_20') |
      blockname %>% str_detect('2024_01_24') |
      blockname %>% str_detect('2024_01_25') |
      blockname %>% str_detect('2024_08_05') | #cohort 2
      blockname %>% str_detect('2024_08_06') |
      blockname %>% str_detect('2024_08_07') |
      blockname %>% str_detect('2024_08_08') |
      blockname %>% str_detect('2024_08_09') |
      blockname %>% str_detect('2024_08_12') |
      blockname %>% str_detect('2024_08_13') |
      blockname %>% str_detect('2024_08_14') |
      blockname %>% str_detect('2024_08_15')
  )
}
```

# str opto stim
```{r}
dir_output <- './analysis_output_final/opto_characterization/'


color_values_regions <- c('#000004FF', '#AD347CFF', '#EA5661FF', '#FE9F6DFF')
                        #  NAcCorR      DMS        DLS        TS
```

## import / process
### opto stim ids
```{r}
# filter to first 4 sessions
import_fns <-  log_npm %>%
  filter(exclude == 0) %>%
  filter_counterbalance_days() %>%
  filter(experiment == manual_experiments) %>%
  pull(blockname) %>% unique() 


stim_params <- return_stim_params(import_fns, dir_arduino_extraction, file_format_output) 

stim_params <- stim_params %>%
  select(blockname, stim_num, trial_stim_frequency) %>%
  filter(trial_stim_frequency != 0) %>%
  arrange(blockname, stim_num) %>%
  group_by(blockname) %>%
  mutate(event_number_arduino = row_number())
```

```{r}
df_stim_in_dataset <- log_data_stim %>%
  filter(blockname %in% import_fns) %>%
  select(subject, date, region_stim) 

df_stim_in_dataset %>%
  group_by(subject) %>%
  summarise(count = n())

df_stim_in_dataset %>%
  ggplot(aes(region_stim, subject)) +
  geom_point(size = 3)

```
- note, dms missing for abw03


### npm
```{r}
data_list <- combined_import(import_directory = dir_npm_processed, 
                             filter_strings = import_fns,
                             prefixes = NA,
                             suffixes = c('streams_session.feather', 'streams_peth.feather', 'events.feather'), 
                             verbose = 0
                             )


streams      <- data_list[[1]] %>% filter(!blockname %>% str_detect('nolaser')) %>% filter(signal_wavelength == 470)
streams_peth <- data_list[[2]] %>% filter(!blockname %>% str_detect('nolaser')) %>% filter(signal_wavelength == 470) 
events       <- data_list[[3]] %>% filter(!blockname %>% str_detect('nolaser'))

```


```{r}
filter_subjects <-  function(df){
  df %>%
    left_join(log_npm %>% select(blockname, subject) %>% unique()) %>%
    filter(!subject %in% c('abw03', 'abw10')) %>%
    select(-subject)
}

streams <- streams %>%  filter_subjects()
streams_peth <- streams_peth %>% filter_subjects()
events <- events %>% filter_subjects()
```


```{r}
events %>%
  ungroup() %>%
  select(blockname) %>%
  unique() %>%
  left_join(log_npm %>% select(blockname, subject) %>% unique()) %>%
  group_by(subject) %>%
  summarise(count = n()) %>%
  ggplot(aes(count, subject)) +
  geom_point()
```
- verified 09/18/24: all subjects have 4 sessions in analysis (1 for each stimulation region)


```{r}
streams <- streams %>% 
    mutate(subject = blockname %>% str_sub(12,16))

streams_peth <- streams_peth %>% 
    mutate(subject = blockname %>% str_sub(12,16))

streams_peth <- streams_peth %>%
  left_join(log_npm %>% select(blockname, branch_id, region)) %>%
  mutate(region = region %>% factor(levels = c('nac', 'dms', 'dls', 'ts'))) 

streams_peth <- streams_peth %>%
  left_join(log_subject %>% select(subject, line)) %>%
  filter(time_rel > -3, time_rel < 9)
```


```{r}
events <- events %>%
  group_by(blockname) %>%
  arrange(blockname, event_ts) %>%
  filter(event_id_char == 'trial_start') %>%
  rename(stim_num = event_number) %>%
  left_join(stim_params, by = c("blockname", "stim_num"))


events %>%
  select(blockname, event_ts, trial_stim_frequency) %>%
  filter(!is.na(trial_stim_frequency)) %>%
  group_by(blockname, trial_stim_frequency) %>%
  summarise(count = n()) %>%
  mutate(trial_stim_frequency = factor(trial_stim_frequency, levels = c(1,2,5,10,20))) %>%
  ggplot(aes(trial_stim_frequency, blockname, fill = count)) +
  geom_tile()
  
```
- verified 09/18/24: 10 trials for each stimulation frequency in all sessions

```{r}
streams_peth <- streams_peth %>%
  rename(stim_num = event_number) %>%
  left_join(
    events %>%
      select(blockname, stim_num, trial_stim_frequency)) %>%
  filter(!is.na(trial_stim_frequency))


# create z-score based on pre-stimulation window
local_zs_window <- c(-3, 0)

streams_peth <- streams_peth %>%
  group_by(blockname, signal_wavelength, region) %>%
    filter(time_rel > local_zs_window[1], time_rel < local_zs_window[2]) %>%
    summarise(
      delta_signal_poly_local_bl_mu = mean(delta_signal_poly),
      delta_signal_poly_local_bl_sd = sd(delta_signal_poly),
      delta_control_poly_local_bl_mu = mean(delta_control_poly),
      delta_control_poly_local_bl_sd = sd(delta_control_poly),
      .groups = 'drop'
      ) %>%
    left_join(streams_peth, ., by = c("blockname", "signal_wavelength", "region")) %>%
    mutate(
      delta_signal_poly_zscore_local = (delta_signal_poly - delta_signal_poly_local_bl_mu) / delta_signal_poly_local_bl_sd,
      delta_control_poly_zscore_local = (delta_control_poly - delta_control_poly_local_bl_mu) / delta_control_poly_local_bl_sd
      ) %>%
    select(-delta_signal_poly_local_bl_mu, -delta_signal_poly_local_bl_sd, -delta_control_poly_local_bl_mu, -delta_control_poly_local_bl_sd)


# join in stimulation region
streams_peth <- streams_peth %>%
  left_join(log_data_stim %>% select(blockname, region_stim)) %>%
  mutate(region_stim = region_stim %>% factor(levels = c('nac', 'dms', 'dls', 'ts'))) 


# remove NA trial_stim_frequency trials (0Hz)
streams_peth <- streams_peth %>%
  filter(!is.na(trial_stim_frequency))

events <- events %>%
  filter(!is.na(trial_stim_frequency))
```


```{r}
streams_peth %>%
  filter(time_rel == 0) %>%
  filter(branch_id == 1) %>%
  group_by(blockname, trial_stim_frequency) %>%
  summarise(count = n(), .groups = 'drop') %>%
  select(count) %>%
  unique()
```
- verified 09/18/24: streams_peth - 10 trials for each stimulation frequency in all sessions


```{r}
var_iv <- 'delta_signal_poly_zscore_local'

# baseline subtract
streams_peth <- streams_peth %>%
  filter(time_rel > -3, time_rel < 0) %>%
  group_by(blockname, stim_num, region_stim, region, signal_wavelength) %>%
  summarise(bl = mean(!!as.name(var_iv)), .groups = 'drop') %>%
  left_join(streams_peth,.) %>%
  mutate(!!as.name(var_iv) := !!as.name(var_iv) - bl) %>%
  select(-bl)

# format streams_peth
streams_peth <- streams_peth %>%
  format_regions('region', key_regions) %>%
  format_regions('region_stim', key_regions) %>%
  left_join(log_subject %>% select(subject, line), by = join_by(subject, line))

# create summary based on 0.5s post stimulation window
streams_peth_summary <- streams_peth %>%
  filter(time_rel > 3, time_rel < 3.5) %>% 
  group_by(blockname, subject, region_stim, trial_stim_frequency, region) %>%
  summarise(
    delta_signal_poly_zscore_local = mean(delta_signal_poly_zscore_local),
    .groups = 'drop') %>%
  mutate(trial_stim_frequency = as.character(trial_stim_frequency) %>% factor(levels = c(1,2,5,10,20,40)))

streams_peth_summary_group <- streams_peth_summary %>%
  group_by(trial_stim_frequency, region_stim, region) %>%
  summarise(
    count_subjects = n(),
    delta_signal_poly_zscore_local = mean(delta_signal_poly_zscore_local),
    .groups = 'drop') %>%
  mutate(trial_stim_frequency = as.character(trial_stim_frequency) %>% factor(levels = c(1,2,5,10,20,40)))
```


```{r}

```

## plot / analyze
### trace: time vs zscore 20Hz
```{r}
fn_stem <- 'trace_tm_vs_zscore_20hz'
  
data_plt <- streams_peth %>%
  filter(trial_stim_frequency == 20) %>%
  mutate(time_set = ifelse((time_rel > -3 & time_rel < 0), 'pre', NA)) %>%
  mutate(time_set = ifelse((time_rel > 3 & time_rel < 9), 'post', time_set)) %>%
  filter(!is.na(time_set)) %>%
  select(blockname, branch_id, region, region_stim, stim_num, time_rel, time_set, delta_signal_poly_zscore_local)

plt <- data_plt %>%
  ggplot(aes(time_rel, delta_signal_poly_zscore_local, group = interaction(region, time_set), color = region, fill = region)) +
  annotate("rect", xmin = 0, xmax = 3, ymin = -Inf, ymax = Inf, alpha = 1/3, fill = "darkgrey") +
  stat_summary(fun.data = 'mean_se', geom = 'ribbon', color = NA, alpha = 1/4) +
  stat_summary(fun = 'mean', geom = 'line') +
  facet_wrap(.~region_stim, scales = 'free', nrow = 1) +
  theme_ag01() +
  scale_color_manual(values = color_values_regions) +
  scale_fill_manual(values = color_values_regions) +
  force_panelsizes(cols = unit(3,'cm'), rows = unit(4, 'cm'))

plt <- plt  %>%
  add_scale_bar(
    origin = c(-3, -0), 
    x_len = 1, 
    y_len = 1
  )

plt

save_pdf(dir_output, str_c(fn_stem,'.pdf'),22,12)

data_plt %>%
  write_csv(str_c(dir_output, fn_stem, '_data.csv'))
```


### heat: frequency vs region
```{r}
fn_stem <- 'heat_frequency_vs_region'

data_plt <- streams_peth_summary_group

plt <- streams_peth_summary_group %>%
  ggplot(aes(trial_stim_frequency, region, fill = delta_signal_poly_zscore_local)) +
  geom_tile() +
  #geom_hline(yintercept = 3.5, size = 1) +
  scale_fill_gradientn(colors = c('blue', 'white', 'red'), limits = c(-4,4), oob = scales::squish) +
  theme_ag01() +
  facet_grid(.~region_stim) +
  ylab('Region') +
  xlab('Stimulation Frequency (Hz)') +
  coord_cartesian(xlim = c(0.5, 5.5), ylim = c(0.5, 4.5), expand = F) +
  theme(panel.spacing = unit(2, "lines")) +
  force_panelsizes(cols = unit(2,'cm'), rows = unit(3, 'cm'))

plt

save_pdf(dir_output, str_c(fn_stem,'.pdf'),22,12)

data_plt %>%
  write_csv(str_c(dir_output, fn_stem, '_data.csv'))
```

#### stats: frequency response for each area 
```{r}
var_dv <- 'delta_signal_poly_zscore_local'

plt_data <- streams_peth_summary 


first_loop <- 1

for(id_region_stim in key_regions$region_label){
  for(id_region_rec in key_regions$region_label){

    plt_data_wide <- plt_data %>%
      filter(region_stim == id_region_stim,
             region == id_region_rec) %>%
      select(subject, trial_stim_frequency, !!as.name(var_dv)) %>%
      spread(trial_stim_frequency, !!as.name(var_dv)) 
    
    result <- friedman.test(as.matrix(plt_data_wide[, -1]))
    
    result_df <- tidy(result) %>%
      clean_names() %>%
      mutate(region_stim = id_region_stim,
             region = id_region_rec) %>%
      select(region_stim, region, everything())
    
    if(first_loop){
      result_df_combined <- result_df
      first_loop = 0
    } else {
      result_df_combined <- result_df %>% bind_rows(result_df_combined,.)
      
    }
  }
}

result_df_combined <- result_df_combined %>%
  mutate(
    region = region %>% factor(levels = key_regions$region_label),
    region_stim = region_stim %>% factor(levels = key_regions$region_label)
  ) %>%
  mutate(
    p_value_notadjusted = p_value,
    p_value = p_value *4)%>% # correct for multiple comparisions
  quick_sig() 

result_df_combined %>%
  write_csv(str_c(dir_output, fn_stem, '_stats.csv'))

plt_data %>%
  write_csv(str_c(dir_output, fn_stem, '_stats_data.csv'))

result_df_combined %>%
  filter(sig_symbol != 'n.s.') %>%
  ggplot(aes(region_stim, region, label = sig_symbol)) +
  geom_text()
```



### heat: region stim vs region recorded 20Hz
```{r}
region_levels <- key_regions %>% slice(n():1) %>% pull(region_label)

fn_str <- 'region_vs_regionstim_matrix_20hz'

plt_data <- streams_peth_summary_group %>%
  mutate(region = factor(region, levels = rev(region_levels))) %>%
  filter(trial_stim_frequency == 20) %>%
  filter(!is.na(region_stim))

plt_data %>%
  ggplot(aes(region_stim, region, fill = !!as.name(var_iv))) +
  geom_tile() +
  scale_fill_gradientn(colors = c('blue', 'white', 'red'), limits = c(-3,3), oob = scales::squish) +
  theme_ag01() +
  coord_cartesian(xlim = c(0.5, 4.5), ylim = c(0.5,4.5), expand = F) +
  theme(
    axis.text.x = element_text(angle = 90, hjust = 1, vjust = 0.3),
    axis.text.y = element_text(hjust = 1)
  ) +
  xlab('Stimulated') +
  ylab('Recorded') +
  force_panelsizes(cols = unit(3,'cm'), rows = unit(3, 'cm'))


save_pdf(dir_output, str_c(fn_str, '.pdf'), 8,8)
plt_data %>% write_csv(str_c(dir_output, fn_str, '.csv'))
```

### line: region vs zscore 20hz
```{r}
fn_stem <- 'line_region_vs_zscore_20hz'

data_plt <- streams_peth_summary %>%
  filter(trial_stim_frequency == 20) 

plt01 <- data_plt %>%
  filter(region_stim == 'NAcCR') %>%
  ggplot(aes(region, delta_signal_poly_zscore_local)) +
  geom_hline(yintercept = 0, color = 'grey', size = 0.5) +
  geom_line(aes(group = subject), color = 'darkgrey', alpha = 1/3) +
  geom_point(aes(group = subject), color = 'darkgrey', size = 1) +
  stat_summary(fun.data = 'mean_se', geom = 'errorbar', width = 0) +
  stat_summary(fun = 'mean', geom = 'line', aes(group = 1)) +
  theme_ag01() +
  coord_cartesian(xlim = c(0.5, 4.5), ylim = c(-10,60), expand = F) +
  scale_y_continuous(breaks = seq(-10,60,10)) +
  theme(axis.text.x = element_text(angle = 90, hjust = 1, vjust = 0.3)) +
  xlab('') +
  ggtitle('NAcCR')

plt02 <- data_plt %>%
  filter(region_stim == 'DMS') %>%
  ggplot(aes(region, delta_signal_poly_zscore_local)) +
  geom_hline(yintercept = 0, color = 'grey', size = 0.5) +
  geom_line(aes(group = subject), color = 'darkgrey', alpha = 1/3) +
  geom_point(aes(group = subject), color = 'darkgrey', size = 1) +
  stat_summary(fun.data = 'mean_se', geom = 'errorbar', width = 0) +
  stat_summary(fun = 'mean', geom = 'line', aes(group = 1)) +
  theme_ag01() +
  coord_cartesian(xlim = c(0.5, 4.5), ylim = c(-2,6), expand = F) +
  theme(axis.text.x = element_text(angle = 90, hjust = 1, vjust = 0.3)) +
  xlab('') +
  ggtitle('DMS')

plt03 <- data_plt %>%
  filter(region_stim == 'DLS') %>%
  ggplot(aes(region, delta_signal_poly_zscore_local)) +
  geom_hline(yintercept = 0, color = 'grey', size = 0.5) +
  geom_line(aes(group = subject), color = 'darkgrey', alpha = 1/3) +
  geom_point(aes(group = subject), color = 'darkgrey', size = 1) +
  stat_summary(fun.data = 'mean_se', geom = 'errorbar', width = 0) +
  stat_summary(fun = 'mean', geom = 'line', aes(group = 1)) +
  theme_ag01() +
  coord_cartesian(xlim = c(0.5, 4.5), ylim = c(-2,8), expand = F) +
  theme(axis.text.x = element_text(angle = 90, hjust = 1, vjust = 0.3)) +
  xlab('') +
  ggtitle('DLS')

plt04 <- data_plt %>%
  filter(region_stim == 'TS') %>%
  ggplot(aes(region, delta_signal_poly_zscore_local)) +
  geom_hline(yintercept = 0, color = 'grey', size = 0.5) +
  geom_line(aes(group = subject), color = 'darkgrey', alpha = 1/3) +
  geom_point(aes(group = subject), color = 'darkgrey', size = 1) +
  stat_summary(fun.data = 'mean_se', geom = 'errorbar', width = 0) +
  stat_summary(fun = 'mean', geom = 'line', aes(group = 1)) +
  theme_ag01() +
  coord_cartesian(xlim = c(0.5, 4.5), ylim = c(-5,15), expand = F) +
  scale_y_continuous(breaks = seq(-5,15,5)) +
  theme(axis.text.x = element_text(angle = 90, hjust = 1, vjust = 0.3)) +
  xlab('') +
  ggtitle('TS')

(plt01 + ylab('Mean z-score 0.0-0.5s')) +
  (plt02 + ylab('')) +
  (plt03 + ylab('') ) +
  (plt04 + ylab('') ) +
  plot_layout(nrow = 1, widths = unit(2, 'cm'), heights = unit(3, 'cm'))


save_pdf(dir_output, str_c(fn_stem,'.pdf'),22,12)

data_plt %>%
  write_csv(str_c(dir_output, fn_stem, '_data.csv'))
```

```{r, fig.height = 8, fig.width = 4}
# alternative visualization

 data_plt %>%
  ggplot(aes(region, delta_signal_poly_zscore_local)) +
  geom_hline(yintercept = 0, color = 'grey', size = 0.5) +
  geom_line(aes(group = subject), color = 'darkgrey', alpha = 1/3) +
  geom_point(aes(group = subject), color = 'darkgrey', size = 1) +
  stat_summary(fun.data = 'mean_se', geom = 'errorbar', width = 0) +
  stat_summary(fun = 'mean', geom = 'line', aes(group = 1)) +
  theme_ag01() +
  #coord_cartesian(xlim = c(0.5, 4.5), ylim = c(-10,60), expand = F) +
  #scale_y_continuous(breaks = seq(-10,60,10)) +
  facet_grid(region_stim~., scales = 'free') +
  theme(axis.text.x = element_text(angle = 90, hjust = 1, vjust = 0.3)) +
  force_panelsizes(cols = unit(3,'cm'), rows = unit(3, 'cm')) 
```

#### statistics
```{r}
var_dv <- 'delta_signal_poly_zscore_local'
id_region_stim <- 'NAcCR'

plt_data <- streams_peth_summary %>%
  filter(trial_stim_frequency == 20) 


for(id_region_stim in key_regions$region_label){
  
  plt_data_wide <- plt_data %>%
    filter(region_stim == id_region_stim) %>%
    select(subject, region, !!as.name(var_dv)) %>%
    spread(region, !!as.name(var_dv)) 
  
  result <- friedman.test(as.matrix(plt_data_wide[, -1]))
  
  result_df <- tidy(result) %>%
    clean_names() %>%
    mutate(region_stim = id_region_stim) %>%
    select(region_stim, everything())
  
  # Convert data back to long format for post hoc test
  plt_data_long <- plt_data_wide %>%
    gather(key = "region", value = !!as.name(var_dv), -subject)
  
  # Conduct pairwise Wilcoxon signed-rank test as a post hoc test
  post_hoc <- pairwise.wilcox.test(
    x = plt_data_long %>% pull(var_dv),
    g = plt_data_long$region,
    p.adjust.method = "bonferroni"
  )
  
  post_hoc_df <- post_hoc$p.value %>% 
    as_tibble() %>%
    mutate(comp1 = rownames(post_hoc$p.value)) %>%
    gather('comp2', 'p_value', -comp1) %>%
    filter(!is.na(p_value), comp1 != comp2) %>%
    mutate(
      region_stim = id_region_stim,
      method = post_hoc$method,
      method_pvaladj = post_hoc$p.adjust.method
      ) %>%
    select(region_stim, everything())
  
  if(id_region_stim == key_regions$region_label[1]){
    result_df_combined <- result_df
    post_hoc_df_combined <- post_hoc_df
  } else {
    result_df_combined <- result_df %>% bind_rows(result_df_combined,.)
    post_hoc_df_combined <- post_hoc_df %>% bind_rows(post_hoc_df_combined,.)
    
  }
}

result_df_combined %>%
  write_csv(str_c(dir_output, fn_stem, '_stats_main.csv'))

post_hoc_df_combined %>%
  quick_sig() %>%
  write_csv(str_c(dir_output, fn_stem, '_stats_posthoc.csv'))
  
```


```{r}
post_hoc_df_combined %>%
  mutate(region_stim = factor(region_stim, levels = key_regions$region_label)) %>%
  mutate(comp1 = factor(comp1, levels = key_regions$region_label)) %>%
  mutate(comp2 = factor(comp2, levels = key_regions$region_label)) %>%
  quick_sig() %>%
  ggplot(aes(comp1, comp2, label = sig_symbol)) +
  geom_text() +
  facet_grid(.~region_stim) +
  force_panelsizes(cols = unit(3,'cm'), rows = unit(3, 'cm')) 
```

## placements
```{r}
log_histology <- read_sheet("https://docs.google.com/spreadsheets/d/1dATNdE46yfeKJmNBi51yeO8Iycv4RaMlfdc8xS4YBiY", sheet = 'placements', na = c('', 'NA'))
```

```{r}
data_plt <- streams_peth_summary %>%
  filter(trial_stim_frequency == 20)  %>%
  left_join(log_histology %>% select(subject, region = target, hit_ap, hit_ml, hit_dv)) 
```

```{r, fig.width = 6, fig.height=8}


plt_nac <- data_plt %>%
  filter(region_stim == 'NAcCR') %>%
  ggplot(aes(hit_ap, hit_dv, color = delta_signal_poly_zscore_local)) +
  geom_point(size = 5, alpha = 1/2) +
  facet_grid(region_stim~.) +
  coord_cartesian(xlim = c(-2.5, 2.5), ylim = c(-2, -6)) +
  scale_color_viridis_c(limits = c(0,20), oob = scales::squish) 

plt_dms <- data_plt %>%
  filter(region_stim == 'DMS') %>%
  ggplot(aes(hit_ap, hit_dv, color = delta_signal_poly_zscore_local)) +
  geom_point(size = 5, alpha = 1/2) +
  facet_grid(region_stim~.) +
  coord_cartesian(xlim = c(-2.5, 2.5), ylim = c(-2, -6)) +
  scale_color_viridis_c(limits = c(0,4), oob = scales::squish) 

plt_dls <- data_plt %>%
  filter(region_stim == 'DLS') %>%
  ggplot(aes(hit_ap, hit_dv, color = delta_signal_poly_zscore_local)) +
  geom_point(size = 5, alpha = 1/2) +
  facet_grid(region_stim~.) +
  coord_cartesian(xlim = c(-2.5, 2.5), ylim = c(-2, -6)) +
  scale_color_viridis_c(limits = c(0,6), oob = scales::squish) 

plt_ts <- data_plt %>%
  filter(region_stim == 'TS') %>%
  ggplot(aes(hit_ap, hit_dv, color = delta_signal_poly_zscore_local)) +
  geom_point(size = 5, alpha = 1/2) +
  facet_grid(region_stim~.) +
  coord_cartesian(xlim = c(-2.5, 2.5), ylim = c(-2, -6)) +
  scale_color_viridis_c(limits = c(0,9), oob = scales::squish) 


plt_nac + plt_dms + plt_dls + plt_ts +
  plot_layout(ncol = 1, widths = unit(6, 'cm'), heights = unit(3, 'cm'))
```


```{r}

plt_str <- function(df, var_color, var_color_name, vars_facet, color_limits, plt_plane, plt_dim_base){
  range_ap <- c(-3, 3)
  range_ml <- c(0, 4)
  range_dv <- c(-6, -1)
  
  var_color <- rlang::enquo(var_color)
  facet_formula <- as.formula(paste(vars_facet[1], '~', vars_facet[2]))
  
  if(plt_plane == 'sagittal'){
    plt <- df %>%
      ggplot(aes(hit_ap, hit_dv, color = !!var_color)) +
      coord_cartesian(xlim = range_ap, ylim = range_dv, expand = F) +
      xlab('Anterior-posterior (mm)')+
      ylab('Dorsal-ventral (mm)') 
  }
  
  if(plt_plane == 'coronal'){
    plt <- df %>%
      ggplot(aes(hit_ml, hit_dv, color = !!var_color)) +
      coord_cartesian(xlim = range_ml, ylim = range_dv, expand = F) +
      xlab('Medial-lateral (mm)')+
      ylab('Dorsal-ventral (mm)')
  }
  
  if(plt_plane == 'horizontal'){
    plt <- df %>%
      ggplot(aes(hit_ap, hit_ml, color = !!var_color)) +
      coord_cartesian(xlim =  range_ap, ylim = range_ml, expand = F) +
      xlab('Anterior-posterior (mm)')+
      ylab('Medial-lateral (mm)') 
  }
  
  plt <- plt +
    geom_point(size = 2, alpha = 1)
  
  if(sum(is.na(color_limits)) == 0){
    plt <- plt +
      scale_color_viridis_c(
        limits = color_limits,
        oob = scales::squish,
        name = var_color_name, 
        breaks = color_limits)
  }
  
   plt <- plt+
    theme_ag01() +
    theme(
      legend.key.size = unit(0.5, "cm"),
      legend.key.width = unit(0.2,"cm"),
      legend.title.position = "right",
      panel.grid.major = element_line(color = 'lightgrey', size = 0.5), 
      legend.title = element_text(angle = 270, hjust = 0.5),
      axis.title = element_text(color = "black", size = 10),
      axis.text.x = element_text(color = "black", size = 8, hjust = 0.5),
      axis.text.y = element_text(color = "black", size = 8, hjust = 1, vjust = 0.3, margin = margin(r = 1)),

    ) 
  
  
  plt <- plt +
    facet_grid(facet_formula)
  
  dim_ap <- range_ap[2] - range_ap[1]
  dim_ml <- range_ml[2] - range_ml[1]
  dim_dv <- range_dv[2] - range_dv[1]
  
  
  aspect_sagital <- dim_ap / dim_dv
  aspect_coronal <- dim_ml / dim_dv
  aspect_horizontal <- dim_ap / dim_ml
  
  if(plt_plane == 'sagittal'){
    plt <- plt +
      force_panelsizes(rows = unit(plt_dim_base, 'cm'), cols = unit(plt_dim_base*aspect_sagital, 'cm'))
  } 
    
  if(plt_plane == 'horizontal'){
    plt <- plt +
      force_panelsizes(rows = unit(plt_dim_base, 'cm'), cols = unit(plt_dim_base*aspect_horizontal, 'cm'))
  } 
  
  if(plt_plane == 'coronal'){
    plt <- plt +
      force_panelsizes(rows = unit(plt_dim_base, 'cm'), cols = unit(plt_dim_base*aspect_coronal, 'cm'))
  }
  
  return(plt)
  
}



plt_str_3d <- function(df, var_color, color_limits, dir_output, fn_stem, toggle_save){
  x_range <- c(-3, 3)
  y_range <- c(0, 4)
  z_range <- c(-5, -2)
  
  font.pref.title <- list(size=30, family="Arial, sans-serif", color="black")
  font.pref.tick <- list(size=18, family="Arial, sans-serif", color="black")
  
  i <- -2.5 # x/y eye position
  ii <- 0.5 # z eye position
  
  # Convert the column name to a symbol
  var_color_sym <- sym(var_color)
  
  # Squish the values of var_color within the specified color_limits
  df <- df %>%
    mutate(!!var_color_sym := ifelse(!!var_color_sym > color_limits[2], color_limits[2], !!var_color_sym)) %>%
    mutate(!!var_color_sym := ifelse(!!var_color_sym < color_limits[1], color_limits[1], !!var_color_sym))
  
  # Create the plot
  plt <- plot_ly(df,
          x = ~hit_ap, 
          y = ~hit_ml, 
          z = ~hit_dv, 
          color = ~.data[[var_color]],  # Use the symbol for the color mapping
          type = 'scatter3d', 
          mode = 'markers',  # Plot points only
          marker = list(
            size = 10,
            colorscale = 'Viridis',  
            cmin = color_limits[1],   # Set the minimum value for color scaling
            cmax = color_limits[2]    # Set the maximum value for color scaling
          )
  ) %>%
    layout(scene = list(
             xaxis = list(
               title = 'AP (mm)', 
               range = x_range, 
               tickvals = seq(x_range[1], x_range[2], by = 1),  # Specify x-axis ticks
               ticktext = seq(x_range[1], x_range[2], by = 1),  # Custom labels
               nticks = sum(abs(x_range)), 
               titlefont = font.pref.title,
               tickfont = font.pref.tick,
               zeroline = FALSE,  # Remove emphasis on zero line
               showline = TRUE,   # Keep the axis line visible
               showgrid = TRUE    # Optionally keep grid lines
             ),
             yaxis = list(
               title = 'ML (mm)', 
               range = y_range, 
               tickvals = seq(y_range[1], y_range[2]-1, by = 1),  # Specify y-axis ticks
               ticktext = seq(y_range[1], y_range[2]-1, by = 1),  # Custom labels
               nticks = sum(abs(y_range)), 
               titlefont = font.pref.title,
               tickfont = font.pref.tick,
               zeroline = FALSE,  # Remove emphasis on zero line
               showline = TRUE,  
               showgrid = TRUE   
             ),
             zaxis = list(
               title = 'DV (mm)', 
               range = z_range, 
               tickvals = seq(z_range[1]+1, z_range[2], by = 1),  # Specify z-axis ticks
               ticktext = seq(z_range[1]+1, z_range[2], by = 1),  # Custom labels
               nticks = 6, 
               titlefont = font.pref.title,
               tickfont = font.pref.tick,
               zeroline = FALSE,  # Remove emphasis on zero line
               showline = TRUE,  
               showgrid = TRUE   
             ), 
              aspectmode = 'manual',
              aspectratio = list(
                x = (x_range[2] - x_range[1])/4.5, 
                y = (y_range[2] - y_range[1])/4.5, 
                z = (z_range[2] - z_range[1])/4.5
              ),
             camera = list(
               eye = list(x = cos(i)*3, y = sin(i)*3, z = ii*3), 
               center = list(x = 0, y = 0, z = -0.1)
             )
           )
    )
  
  if(toggle_save){
    save_image(plt,
               width = 900,
               height = 800,
               scale = 1,
               str_c(dir_output, fn_stem, ".pdf"))
  } else {
    plt
  }
}




### ~ execution ~ ###

fn_stem <- 'placement_vs_optoresponse'

for(region_id in key_regions$region_label){
  df <- data_plt %>% filter(region_stim == region_id)
  
  if(region_id == 'NAcCR'){ color_limits <- c(0,20)}
  if(region_id == 'DMS'){color_limits <- c(0,4)}
  if(region_id == 'DLS'){color_limits <- c(0,6)}
  if(region_id == 'TS'){color_limits <- c(0,9)}
  
  # plt_str(
  #   df = df, 
  #   var_color = delta_signal_poly_zscore_local,
  #   var_color_name = 'z-score',
  #   vars_facet = c('.','.'),
  #   plt_plane = 'sagittal',
  #   plt_dim_base = 3,
  #   color_limits = color_limits
  #   ) 
  # 
  # save_pdf(dir_output, str_c(fn_stem,'_', region_id, '_sagittal.pdf'),6,6)
  # 
  # plt_str(
  #   df = df,
  #   var_color = delta_signal_poly_zscore_local,
  #   var_color_name = 'z-score',
  #   vars_facet = c('.','.'),
  #   plt_plane = 'horizontal',
  #   plt_dim_base = 3,
  #   color_limits = color_limits
  #   ) 
  # 
  # save_pdf(dir_output, str_c(fn_stem,'_', region_id, '_horizontal.pdf'),6,6)
  # 
  # plt_str(
  #   df = df,
  #   var_color = delta_signal_poly_zscore_local,
  #   var_color_name = 'z-score',
  #   vars_facet = c('.','.'),
  #   plt_plane = 'coronal',
  #   plt_dim_base = 3,
  #   color_limits = color_limits
  #   )
  # 
  # save_pdf(dir_output, str_c(fn_stem,'_', region_id, '_coronal.pdf'),6,6)
    
  plt_str_3d(
    df = df, 
    var_color = 'delta_signal_poly_zscore_local', 
    color_limits = color_limits,
    dir_output = dir_output,
    fn_stem = str_c(fn_stem,'_', region_id, '_3d'),
    toggle_save = 1
    )
}

df %>%
  write_csv(str_c(dir_output, 'placement_vs_optoresponse_data.csv' ))
```



