---
title: "npm_preprocessing"
author: "adam gordon-fennell"
date: '2023-05-18'
output: html_document
---

todo:
- check on cat6 connectivity between boxes and clock arduino (ids are not as expected)
- increase sampling rate (many samples below 20Hz)
- resample time prior to exporting dataset
- convert arduino beh dataset to system time using clock approach
- determine what is in the TDT output and replicate... 
- 

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r}
library(tidyverse)
library(afex)
library(emmeans)
library(janitor)
library(readxl)
library(googlesheets4)
library(ggh4x) # force_panelsizes
library(arrow)
library(zoo)
library(lubridate)
library(patchwork)
library(ggbeeswarm)
library(pals)
library(plotly)
library(ggpubr) #r2 on correlation

source('./functions/r_plots.R')
source('./functions/r_general.R')
source('./functions/r_fp.R')
source('./r_head_fixed_processing.R')
source('./functions/stats.R')
```

# setup
```{r}
dir_npm_raw <- './data_raw/'
dir_npm_extracted <- './data_extracted/'
dir_npm_processed <- './data_processed/'
  
log_npm <- read_sheet('https:/docs.google.com/spreadsheets/d/1v-G8GHYPGtJWXARZYqcndO03d23umsTo98BAb5_WnrY/edit#gid=0', na = c('', 'NA'))

log_data_stim_char_param <- read_sheet("https:/docs.google.com/spreadsheets/d/1GOVg5to5MliU6TFIBCR9YUZYx-b4dYGB-qd2uiX7Vrc/edit#gid=0", sheet = 'stim_parameters')

log_data_stim <- read_sheet("https:/docs.google.com/spreadsheets/d/1GOVg5to5MliU6TFIBCR9YUZYx-b4dYGB-qd2uiX7Vrc")

manual_experiments <- c('abo', 'acd')
```

```{r}
dir_tdt_extracted <- './data/data_fp/data_extracted'
dir_tdt_processed <- './data/data_fp/data_processed'
log_tdt <- read_sheet("https:/docs.google.com/spreadsheets/d/1-_aV_inR-hg108or2Pj2K7iWZRnt8pg4-IZNe1sLVQ8", na = 'NA') 
```


# pre-processsing
## arduino
```{r}
# directories 
dir_arduino_extraction <- './data/arduino/extracted/'
dir_arduino_processed <- './data/arduino/processed/'
dir_arduino_raw <- './data/arduino/raw/'
dir_output <- './analysis_output_final/'

key_events <- read_sheet('https:/docs.google.com/spreadsheets/d/1e3ltGi7oNBvIpCgUCcZL2Jm8nmv8eVBoPXvdoowNZx4') 
log_subject <- read_sheet("https:/docs.google.com/spreadsheets/d/17GC2tzKHKuWCZAyj84ubsPTvLsfepKFjl_LnaZ8jxdw", na = 'NA', sheet = 'subject')
log_placements <- read_sheet('https:/docs.google.com/spreadsheets/d/1dATNdE46yfeKJmNBi51yeO8Iycv4RaMlfdc8xS4YBiY', sheet = 'placements', na = c('NA', ''))
```


```{r, meassage = FALSE}
file_format_output <- 'csv'

# npm
manual_blocknames <- log_npm %>%
  filter(experiment %in% manual_experiments) %>%
  filter(procedure %>% str_detect('opto_char')) %>%
  select(blockname) %>%
  unique() %>%
  pull(blockname)

extract_serial_output(dir_arduino_raw, key_events, dir_arduino_extraction, manual_experiments, manual_blocknames = manual_blocknames, file_format_output, overwrite = 0)

# tdt
manual_blocknames <- log_tdt %>%
  filter(experiment %in% manual_experiments) %>%
  filter(procedure %>% str_detect('opto_char')) %>%
  select(blockname) %>%
  unique() %>%
  pull(blockname)

extract_serial_output(dir_arduino_raw, key_events, dir_arduino_extraction, manual_experiments, manual_blocknames = manual_blocknames, file_format_output, overwrite = 0)
```


## npm
```{r, meassage = FALSE}
# extract opto_char stimulation (using filter_red_opto_sd to remove opto stimulation frames)
manual_sessions_to_process <- log_npm %>%
  filter(experiment == manual_experiments) %>%
  filter(procedure %>% str_detect('opto_char')) %>%
  filter(procedure != 'opto_characterization_inhibition') %>%
  filter(procedure != 'opto_characterization_inhibition_extended') %>%
  pull(session_name) %>% unique() 


npm_extract(log_npm, dir_npm_raw, dir_npm_extracted, manual_session_names = manual_sessions_to_process, overwrite = 0, filter_red_opto_sd = 5)
```


```{r, meassage = FALSE}
# extract opto_characterization_inhibition (no red filter)
manual_sessions_to_process <- log_npm %>%
  filter(experiment == manual_experiments) %>%
  filter(procedure == 'opto_characterization_inhibition') %>%
  pull(session_name) %>% unique() 


npm_extract(log_npm, dir_npm_raw, dir_npm_extracted, manual_session_names = manual_sessions_to_process, overwrite = 0, filter_red_opto_sd = NA)
```


```{r, meassage = FALSE}
# process all npm files
fp_preprocess_npm(
  dir_npm_extracted,
  dir_npm_processed,
  log_npm,
  manual_session_names = manual_sessions_to_process,
  overwrite = 0,
  dir_arduino_extracted = './data/arduino/extracted/'
)
```





```{r}
source('./functions/r_fp.R')

manual_sessions_to_process <- log_npm %>%
  filter(experiment == manual_experiments) %>%
  filter(procedure %in% c('opto_characterization_pwr')) %>%
  pull(session_name) %>% unique() 

fp_preprocess_npm(
  dir_npm_extracted,
  dir_npm_processed,
  log_npm,
  manual_session_names = manual_sessions_to_process,
  overwrite = 0,
  dir_arduino_extracted = NA
)
```


## tdt
```{r, echo = TRUE}
manual_blocknames_acd_tdt <- log_tdt %>%
  filter(experiment == 'acd') %>%
  filter(blockname %>% str_detect('2024_08_06')) %>%
  pull(blockname)

```

```{r}
# filter out tdt epocs following initial extraction
#   note: during arduino start up, there was a lengthy period of erroneous detections that need to be removed.
#         removal is accomplished by filtering to a minimum inter-event-interval of 1s
#         takes first 5 events (extra event observed in 2024_04_27_acd07_r02)

filt_tdt_epocs <- 1

if(filt_tdt_epocs){
  for(blockname in manual_blocknames_acd_tdt){
    
    df_epocs <- read_feather(str_c('./data/data_fp/data_extracted/', blockname, '_epocs_data.feather'))
  
    df_epocs_filt <- df_epocs %>%
      filter(name == 'PC0/') %>%
      mutate(iti = onset - lag(onset)) 
    
    if(nrow(df_epocs_filt) > 5){
      df_epocs_filt <- df_epocs_filt %>%
        filter(iti > 10) %>%
        head(5) # 
      
      print(str_c('filtering blockname - ', blockname, ' | nrow: ', df_epocs_filt %>% nrow()))
      
      df_epocs_filt %>% write_feather(str_c('./data/data_fp/data_extracted/', blockname, '_epocs_data.feather'))
    }
  }
}


```

```{r}
fp_preprocess(dir_tdt_extracted, dir_tdt_processed, log_tdt, manual_experiments = NA, manual_blocknames = manual_blocknames_acd_tdt, overwrite = 0)
```



## functions
```{r}
key_regions <- tibble(
  region       = c(  'nac',   'nac_corr', 'nac_shelllat', 'dms', 'dls', 'ts'),
  region_label = c('NAcCR',   'NAcCC',    'NAcShL',       'DMS', 'DLS', 'TS')
)

format_regions <- function(df, var_region, key_regions){
  df %>%
    rename(region = !!as.name(var_region)) %>%
    left_join(key_regions) %>%
    mutate(region_label = factor(region_label, levels = key_regions$region_label)) %>%
    select(-region) %>%
    rename(!!var_region := region_label) %>%
    select(!!var_region, everything())
}
```


```{r}
library(corrplot)
library(Hmisc)

tidy_cor_output_reshape <- function(df, n_table, var_name){
  df_tidy <- df[[n_table]] %>%
    as_tibble()
  
  df_tidy <- df_tidy %>%
    mutate(var_y = colnames(df_tidy)) %>%
    gather('var_x', !!as.name(var_name), -var_y) 
  
  return(df_tidy)
}

tidy_cor_output <- function(df){
  tidy_cor_output_reshape(df, 1, 'r') %>%
    left_join(tidy_cor_output_reshape(df, 2, 'n'), by = c("var_y", "var_x")) %>%
    left_join(tidy_cor_output_reshape(df, 3, 'p'), by = c("var_y", "var_x"))
}


get_cormatrix <- function(df){
  df_corr = rcorr(as.matrix(df))
  tidy_cor_output(df_corr)
}

tidy_cormatrix <- function(df, var_cors, var_groups = NA){
  require(Hmisc)
  
  df <- df %>%
    ungroup()


  if(sum(is.na(var_groups)) > 0){
    df <- df %>% select(var_cors)
  
    df %>%
      group_modify(~ get_cormatrix(.))
    
  } else {
    df <- df %>% select(var_cors, var_groups)
    
    df %>%
      group_by_at(var_groups) %>%
      group_modify(~ get_cormatrix(.))
    
  }
}

```

```{r}
format_group_combined <- function(df){
  df %>%
    mutate(group_combined = ifelse(line %>% str_detect('vglut2'), 'vglut2', NA))%>%
    mutate(group_combined = ifelse(line %>% str_detect('vgat'), 'vgat', group_combined)) %>%
    mutate(group_combined = ifelse(tolower(group) == 'mcherry', 'control', group_combined)) %>%
    mutate(group_combined = ifelse(tolower(group) == 'chrimson', group_combined %>% str_c('_stim'), group_combined)) %>%
    mutate(group_combined = ifelse(tolower(group) == 'hr', group_combined %>% str_c('_inh'), group_combined)) 
  
}


color_group_combined <- c('darkgrey', '#CC2029', '#70BF46')
```


```{r}
format_df <- function(df){
  df <- df %>%
  left_join(log_subject %>% select(subject, line, group)) %>%
  format_group_combined() %>%
  format_regions('region', key_regions)  
}

filter_placements <- function(df){
  df %>%
    left_join(log_placements %>% select(subject, region = target, exclude_optochar, hit_ap, hit_ml, hit_dv)) %>%
    filter(exclude_optochar != 1) %>%
    select(-exclude_optochar)

  
}

join_placements <- function(df){
  df %>%
    left_join(log_placements %>% select(subject, region = target, hit_ap, hit_ml, hit_dv))
}

```

```{r}
plt_corr <- function(df, ylim_all, xlim_ap, xlim_ml, xlim_dv, var_dep, var_dep_label, plt_dims, cor_text_y){
  
  plt_data <- df %>%
    gather('dim', 'mm', starts_with('hit')) %>%
    
    mutate(dim = case_when(
      dim == 'hit_ap' ~ 'AP', #'Anterior-Posterior', 
      dim == 'hit_ml' ~ 'ML', #'Medial-Lateral',
      dim == 'hit_dv' ~ 'DV') #'Dorsal-Ventral'
    ) %>%
    mutate(dim = dim %>% factor(levels = c('AP', 'ML', 'DV'))) # c('Anterior-Posterior', 'Medial-Lateral', 'Dorsal-Ventral')))
  
  f_plt <- function(plt_data, ylim_all, xlim_ap, xlim_ml, xlim_dv, var_dep, var_dep_label, plt_dims, plt_dim){
  
    plt <- plt_data %>%
      filter(dim == plt_dim) %>%
      ggplot(aes(mm, zscore, color = group_combined, fill = group_combined)) +
      geom_hline(yintercept = 0, color = 'darkgrey', size = 0.5) +
      geom_smooth(method = 'lm', size = 0.3, alpha = 1/5) +
      geom_jitter(shape = 21, size = 2, color = 'white', stroke = 1/3) +
      facet_grid(group_combined~dim, scales = 'free') +
      theme_ag01() +
      scale_color_manual(values = color_group_combined) +
      scale_fill_manual(values = color_group_combined) +
      #force_panelsizes(rows = unit(plt_dims[1], 'cm'), cols = unit(plt_dims[2], 'cm'))
      xlab('MM Relative to bregma') +
      ylab(var_dep_label) +
      theme(strip.text.y = element_blank()) +
      theme(panel.spacing.y = unit(0.75, "lines")) 
  
    if(plt_dim == 'AP'){
      plt <- plt +
        coord_cartesian(ylim = ylim_all, xlim = c(min(xlim_ap), max(xlim_ap)), expand = F, clip = 'off') +
      stat_cor(method = "pearson", label.y = cor_text_y, label.x = -3, size = 2) +
        scale_x_continuous(breaks = xlim_ap) +
        theme(axis.title.x = element_blank())
    } 
      
    if(plt_dim == 'ML'){
      plt <- plt +
        coord_cartesian(ylim = ylim_all, xlim =  c(min(xlim_ml), max(xlim_ml)), expand = F, clip = 'off') +
      stat_cor(method = "pearson", label.y = cor_text_y, label.x = 0, size = 2) +
        scale_x_continuous(breaks = xlim_ml) 
      
      plt <- plt %>%
        remove_y_all
    } 
      
    if(plt_dim == 'DV'){
      plt <- plt +
        coord_cartesian(ylim = ylim_all, xlim = c(min(xlim_dv), max(xlim_dv)), expand = F, clip = 'off') +
      stat_cor(method = "pearson", label.y = cor_text_y, label.x = -6, size = 2) +
        scale_x_continuous(breaks = xlim_dv) +
        theme(axis.title.x = element_blank())
      
      plt <- plt %>%
        remove_y_all
    } 
      
      return(plt)
  }
  
  plt_list <- list()
  
  
  for(plt_dim in c('AP', 'ML', 'DV')){
   plt <- f_plt(plt_data, ylim_all, xlim_ap, xlim_ml, xlim_dv, var_dep, var_dep_label, plt_dims, plt_dim)
   plt_list[[plt_dim]] <- plt
   
  }
  
  # compute stats
  stats_output <- plt_data %>%
    tidy_cor('mm', 'zscore', 'dim', 'group_combined')
  
  
  plt_list[['stats_output']] <- stats_output
  
  
  return(plt_list)
  
}
```



```{r}


```


```{r}

plt_str <- function(df, var_color, var_color_name, vars_facet, color_limits, plt_plane, plt_dim_base){
  range_ap <- c(-3, 3)
  range_ml <- c(0, 4)
  range_dv <- c(-6, -1)
  
  var_color <- rlang::enquo(var_color)
  facet_formula <- as.formula(paste(vars_facet[1], '~', vars_facet[2]))
  
  if(plt_plane == 'sagittal'){
    plt <- df %>%
      ggplot(aes(hit_ap, hit_dv, color = !!var_color)) +
      coord_cartesian(xlim = range_ap, ylim = range_dv, expand = F) +
      xlab('Anterior-posterior (mm)')+
      ylab('Dorsal-ventral (mm)') 
  }
  
  if(plt_plane == 'coronal'){
    plt <- df %>%
      ggplot(aes(hit_ml, hit_dv, color = !!var_color)) +
      coord_cartesian(xlim = range_ml, ylim = range_dv, expand = F) +
      xlab('Medial-lateral (mm)')+
      ylab('Dorsal-ventral (mm)')
  }
  
  if(plt_plane == 'horizontal'){
    plt <- df %>%
      ggplot(aes(hit_ap, hit_ml, color = !!var_color)) +
      coord_cartesian(xlim =  range_ap, ylim = range_ml, expand = F) +
      xlab('Anterior-posterior (mm)')+
      ylab('Medial-lateral (mm)') 
  }
  
  plt <- plt +
    geom_point(size = 2, alpha = 1)
  
  if(sum(is.na(color_limits)) == 0){
    plt <- plt +
      scale_color_viridis_c(
        limits = color_limits,
        oob = scales::squish,
        name = var_color_name, 
        breaks = color_limits)
  }
  
   plt <- plt+
    theme_ag01() +
    theme(
      legend.key.size = unit(0.5, "cm"),
      legend.key.width = unit(0.2,"cm"),
      legend.title.position = "right",
      panel.grid.major = element_line(color = 'lightgrey', size = 0.5), 
      legend.title = element_text(angle = 270, hjust = 0.5),
      axis.title = element_text(color = "black", size = 10),
      axis.text.x = element_text(color = "black", size = 8, hjust = 0.5),
      axis.text.y = element_text(color = "black", size = 8, hjust = 1, vjust = 0.3, margin = margin(r = 1)),

    ) 
  
  
  plt <- plt +
    facet_grid(facet_formula)
  
  dim_ap <- range_ap[2] - range_ap[1]
  dim_ml <- range_ml[2] - range_ml[1]
  dim_dv <- range_dv[2] - range_dv[1]
  
  
  aspect_sagital <- dim_ap / dim_dv
  aspect_coronal <- dim_ml / dim_dv
  aspect_horizontal <- dim_ap / dim_ml
  
  if(plt_plane == 'sagittal'){
    plt <- plt +
      force_panelsizes(rows = unit(plt_dim_base, 'cm'), cols = unit(plt_dim_base*aspect_sagital, 'cm'))
  } 
    
  if(plt_plane == 'horizontal'){
    plt <- plt +
      force_panelsizes(rows = unit(plt_dim_base, 'cm'), cols = unit(plt_dim_base*aspect_horizontal, 'cm'))
  } 
  
  if(plt_plane == 'coronal'){
    plt <- plt +
      force_panelsizes(rows = unit(plt_dim_base, 'cm'), cols = unit(plt_dim_base*aspect_coronal, 'cm'))
  }
  
  return(plt)
  
}

plt_str_3d <- function(df, var_color, color_limits, dir_output, fn_stem, toggle_save){
  x_range <- c(-3, 3)
  y_range <- c(0, 4)
  z_range <- c(-5, -2)
  
  font.pref.title <- list(size=30, family="Arial, sans-serif", color="black")
  font.pref.tick <- list(size=18, family="Arial, sans-serif", color="black")
  
  i <- -2.5 # x/y eye position
  ii <- 0.5 # z eye position
  
  # Convert the column name to a symbol
  var_color_sym <- sym(var_color)
  
  # Squish the values of var_color within the specified color_limits
  df <- df %>%
    mutate(!!var_color_sym := ifelse(!!var_color_sym > color_limits[2], color_limits[2], !!var_color_sym)) %>%
    mutate(!!var_color_sym := ifelse(!!var_color_sym < color_limits[1], color_limits[1], !!var_color_sym))
  
  # Create the plot
  plt <- plot_ly(df,
          x = ~hit_ap, 
          y = ~hit_ml, 
          z = ~hit_dv, 
          color = ~.data[[var_color]],  # Use the symbol for the color mapping
          type = 'scatter3d', 
          mode = 'markers',  # Plot points only
          marker = list(
            size = 10,
            colorscale = 'Viridis',  
            cmin = color_limits[1],   # Set the minimum value for color scaling
            cmax = color_limits[2]    # Set the maximum value for color scaling
          )
  ) %>%
    layout(scene = list(
             xaxis = list(
               title = 'AP (mm)', 
               range = x_range, 
               tickvals = seq(x_range[1], x_range[2], by = 1),  # Specify x-axis ticks
               ticktext = seq(x_range[1], x_range[2], by = 1),  # Custom labels
               nticks = sum(abs(x_range)), 
               titlefont = font.pref.title,
               tickfont = font.pref.tick,
               zeroline = FALSE,  # Remove emphasis on zero line
               showline = TRUE,   # Keep the axis line visible
               showgrid = TRUE    # Optionally keep grid lines
             ),
             yaxis = list(
               title = 'ML (mm)', 
               range = y_range, 
               tickvals = seq(y_range[1], y_range[2]-1, by = 1),  # Specify y-axis ticks
               ticktext = seq(y_range[1], y_range[2]-1, by = 1),  # Custom labels
               nticks = sum(abs(y_range)), 
               titlefont = font.pref.title,
               tickfont = font.pref.tick,
               zeroline = FALSE,  # Remove emphasis on zero line
               showline = TRUE,  
               showgrid = TRUE   
             ),
             zaxis = list(
               title = 'DV (mm)', 
               range = z_range, 
               tickvals = seq(z_range[1]+1, z_range[2], by = 1),  # Specify z-axis ticks
               ticktext = seq(z_range[1]+1, z_range[2], by = 1),  # Custom labels
               nticks = 6, 
               titlefont = font.pref.title,
               tickfont = font.pref.tick,
               zeroline = FALSE,  # Remove emphasis on zero line
               showline = TRUE,  
               showgrid = TRUE   
             ), 
             #aspectmode='manual',
             # aspectratio = list(
             #   x = (x_range[2] - x_range[1])/3, 
             #   y = (y_range[2] - y_range[1])/3, 
             #   z = (z_range[2] - z_range[1])/3
             #   ),
             camera = list(
               eye = list(x = cos(i)*3, y = sin(i)*3, z = ii*3), 
               center = list(x = 0, y = 0, z = -0.1)
             )
           )
    )
  
  if(toggle_save){
    save_image(plt,
               width = 900,
               height = 800,
               scale = 1,
               str_c(dir_output, fn_stem, ".pdf"))
  } else {
    plt
  }
}



```

# Opto stim
## import / process
### opto stim ids
```{r}
dir_output <- './analysis_output_final/stimulation/'

plt_dims <- c(3,3)


preprocess <- 0

if(preprocess){
  import_fns <-  log_npm %>%
    filter(experiment == manual_experiments) %>%
    filter(procedure == 'opto_characterization') %>%
    pull(blockname) %>% unique() 
  
  
  stim_params <- return_stim_params(import_fns, dir_arduino_extraction, file_format_output) 
  
  stim_params <- stim_params %>%
    select(blockname, stim_num, trial_stim_frequency) %>%
    filter(trial_stim_frequency != 0) %>%
    arrange(blockname, stim_num) %>%
    group_by(blockname) %>%
    mutate(event_number_arduino = ifelse(blockname %>% str_detect('2023_07_29'), row_number(), stim_num)) # filter data and renumber for 2023/07/29
  
    
  data_list <- combined_import(import_directory = dir_npm_processed, 
                               filter_strings = import_fns,
                               prefixes = NA,
                               suffixes = c('streams_session.feather', 'streams_peth.feather', 'events.feather'), 
                               verbose = 0
                               )
  
  streams      <- data_list[[1]]
  streams_peth <- data_list[[2]]
  events       <- data_list[[3]]

  streams <- streams %>% 
      mutate(subject = blockname %>% str_sub(12,16))
  
  streams_peth <- streams_peth %>% 
      mutate(subject = blockname %>% str_sub(12,16))
  
  streams_peth <- streams_peth %>%
    left_join(log_npm %>% select(blockname, branch_id, region)) %>%
    mutate(region = region %>% factor(levels = c('nac_shelllat', 'nac', 'nac_corr', 'dms', 'dls', 'ts'))) 
  
  streams_peth <- streams_peth %>%
    left_join(log_subject %>% select(subject, line)) %>%
    filter(time_rel > -3, time_rel < 12)


  # remove stimulations not included in analysis (early cohorts with additional freq)
  antijoin_events <- read_csv('./data/antijoin_events.csv')
  
  events <- events %>%
    anti_join(antijoin_events)
  
  events <- events %>%
    group_by(blockname)  %>% 
    filter(event_id_char %in% c('opto_stim', 'trial_start')) %>%
    arrange(blockname, event_ts) %>%
    mutate(event_number_arduino = row_number()) %>%
    left_join(stim_params, by = c("blockname", "event_number_arduino")) 
  
  
  streams_peth <- streams_peth %>%
    left_join(
      events %>%
        select(blockname, event_number, trial_stim_frequency)) %>%
    filter(!is.na(trial_stim_frequency))

  
  local_zs_window <- c(-3, 0)
  
  streams_peth <- streams_peth %>%
    group_by(blockname, signal_wavelength, region) %>%
      filter(time_rel > local_zs_window[1], time_rel < local_zs_window[2]) %>%
      summarise(
        delta_signal_poly_local_bl_mu = mean(delta_signal_poly),
        delta_signal_poly_local_bl_sd = sd(delta_signal_poly),
        delta_control_poly_local_bl_mu = mean(delta_control_poly),
        delta_control_poly_local_bl_sd = sd(delta_control_poly),
        .groups = 'drop'
        ) %>%
      left_join(streams_peth, ., by = c("blockname", "signal_wavelength", "region")) %>%
      mutate(
        delta_signal_poly_zscore_local = (delta_signal_poly - delta_signal_poly_local_bl_mu) / delta_signal_poly_local_bl_sd,
        delta_control_poly_zscore_local = (delta_control_poly - delta_control_poly_local_bl_mu) / delta_control_poly_local_bl_sd
        ) %>%
      select(-delta_signal_poly_local_bl_mu, -delta_signal_poly_local_bl_sd)
  
  
  var_iv <- 'delta_signal_poly_zscore_local'
  
  streams_peth <- streams_peth %>%
    filter(time_rel > -3, time_rel < 0) %>%
    group_by(blockname, event_number, region, signal_wavelength) %>%
    summarise(bl = mean(delta_signal_poly_zscore_local), .groups = 'drop') %>%
    left_join(streams_peth,.) %>%
    mutate(delta_signal_poly_zscore_local = delta_signal_poly_zscore_local - bl) %>%
    select(-bl) %>%
    left_join(log_subject %>% select(subject, group), by = c('subject'))
  

  streams_peth <- streams_peth %>% format_df()
  
  streams_peth <- streams_peth %>% filter_placements()
  
  
  streams_peth_summary <- streams_peth %>%
    filter(time_rel > 0, time_rel < 3) %>% 
    group_by(blockname, subject, group_combined, line, group, trial_stim_frequency, region) %>%
    summarise(delta_signal_poly_zscore_local := mean(delta_signal_poly_zscore_local), .groups = 'drop') %>%
    mutate(trial_stim_frequency = as.character(trial_stim_frequency) %>% factor(levels = c(0,1,2,5,10,20,40)))
  
  streams_peth_summary_group <- streams_peth_summary %>%
    group_by(group_combined, group, line, trial_stim_frequency, region) %>%
    summarise(delta_signal_poly_zscore_local := mean(delta_signal_poly_zscore_local), .groups = 'drop') %>%
    mutate(trial_stim_frequency = as.character(trial_stim_frequency) %>% factor(levels = c(0,1,2,5,10,20,40)))
  
  
  
  streams_peth <- streams_peth %>%  mutate(region = region %>% factor(levels = key_regions$region_label))
  streams_peth_summary <- streams_peth_summary %>%  mutate(region = region %>% factor(levels = key_regions$region_label))
  streams_peth_summary_group <- streams_peth_summary_group %>%  mutate(region = region %>% factor(levels = key_regions$region_label))
  
  
  streams_peth_subject <- streams_peth %>%
      format_group_combined() %>%
      group_by(group_combined, subject, region, time_rel, trial_stim_frequency) %>%
      summarise(delta_signal_poly_zscore_local = mean(delta_signal_poly_zscore_local), .groups = 'drop') 
  
  streams_peth_group <- streams_peth %>%
      format_group_combined() %>%
      group_by(group_combined, region, time_rel, trial_stim_frequency) %>%
      summarise(
        delta_signal_poly_zscore_local_sem = sd(delta_signal_poly_zscore_local)/sqrt(n()),
        delta_signal_poly_zscore_local = mean(delta_signal_poly_zscore_local),
        .groups = 'drop') 
  
  
  streams_peth %>%
    select(blockname, line, group, group_combined, subject, branch_id, region, time, time_rel, event_number, trial_stim_frequency,  delta_signal_poly_zscore_local) %>%
    write_csv(str_c(dir_output, 'data_streams_peth_full.csv'))
  
  
  streams_peth_summary %>%
    write_csv(str_c(dir_output, 'data_streams_peth_summary.csv'))
  
  
  streams_peth_summary_group %>%
    write_csv(str_c(dir_output, 'data_streams_peth_summary_group.csv'))
  
  
  streams_peth_subject <- streams_peth %>%
    write_csv(str_c(dir_output, 'data_streams_peth_summary_trace_subject.csv'))
  
  streams_peth_group <- streams_peth_group %>%
    write_csv(str_c(dir_output, 'data_streams_peth_summary_trace_group.csv'))
  
} else {
  
  streams_peth <- read.csv(str_c(dir_output, 'data_streams_peth_full.csv')) %>% format_group_combined() %>% mutate(region = region %>% factor(levels = key_regions$region_label))
  streams_peth_summary <- read.csv(str_c(dir_output, 'data_streams_peth_summary.csv')) %>% mutate(region = region %>% factor(levels = key_regions$region_label))
  streams_peth_summary_group <- read.csv(str_c(dir_output, 'data_streams_peth_summary_group.csv')) %>% mutate(region = region %>% factor(levels = key_regions$region_label))
  streams_peth_subject <- read.csv(str_c(dir_output, 'data_streams_peth_summary_trace_subject.csv')) %>% mutate(region = region %>% factor(levels = key_regions$region_label))
  streams_peth_group <- read.csv(str_c(dir_output, 'data_streams_peth_summary_trace_group.csv')) %>% mutate(region = region %>% factor(levels = key_regions$region_label))
  
}

```


## summary of data in analysis
### fiber counts
```{r}
streams_peth_summary %>%
  select(subject, group_combined) %>%
  unique() %>%
  arrange(subject)
```


```{r}
streams_peth_summary %>%
  select(group_combined, region, subject) %>%
  unique() %>%
  group_by(group_combined, region) %>%
  summarise(region_count = n())  %>%
  ggplot(aes(region, group_combined, label = region_count)) +
  geom_text() +
  theme_ag01() +
  theme(axis.text.x = element_text(angle = 90, hjust = 1, vjust = 0.3)) +
  xlab('') +
  ylab('') +
  force_panelsizes(rows = unit(2,'cm'), cols = unit(4, 'cm'))
```
### trial counts
```{r}
streams_peth %>%
  filter(time_rel == 0) %>%
  select(subject, blockname, event_number, trial_stim_frequency) %>%
  unique() %>%
  arrange(subject, event_number) %>%
  group_by(subject, trial_stim_frequency) %>%
  summarise(trial_count = n(), .groups = 'drop') %>%
  mutate(trial_stim_frequency = as.character(trial_stim_frequency)) %>%
  ggplot(aes(trial_stim_frequency, subject, label = trial_count)) +
  geom_text() +
  theme_ag01() +
  theme(axis.text.x = element_text(angle = 90, hjust = 1, vjust = 0.3)) +
  xlab('') +
  ylab('') +
  ggtitle('trial counts') +
  force_panelsizes(rows = unit(6,'cm'), cols = unit(4, 'cm'))

```



```{r}
streams_peth %>%
  filter(time_rel == 0) %>%
  select(subject, blockname, event_number, trial_stim_frequency) %>%
  unique() %>%
  filter(subject == 'abo01') %>%
  filter(trial_stim_frequency == 20) %>%
  arrange(subject, event_number)


streams_peth %>%
  filter(time_rel == 0) %>%
  select(subject, blockname) %>%
  unique() %>%
  group_by(subject) %>%
  summarise(count =n())


streams_peth %>%
  filter(time_rel == 0) %>%
  select(subject, blockname, event_number, trial_stim_frequency) %>%
  unique() %>%
  filter(subject == 'acd05') %>%
  filter(trial_stim_frequency == 20) %>%
  arrange(subject, event_number)
```




## plot / analyze
```{r, fig.width = 9, fig.height = 3}
plt_data <- streams_peth_group %>%
  filter(trial_stim_frequency == 20) %>%
  filter(time_rel > -3, time_rel < 6) 

plt <- plt_data %>%
  ggplot(aes(time_rel, delta_signal_poly_zscore_local, color = region, fill = region)) +
  annotate("rect", xmin = 0, xmax = 3, ymin = -Inf, ymax = Inf, alpha = 1/3, fill = "darkgrey") +
  geom_hline(yintercept = 0, color = 'darkgrey', size = 0.5) +
  geom_ribbon(aes(ymax = delta_signal_poly_zscore_local + delta_signal_poly_zscore_local_sem, 
                  ymin = delta_signal_poly_zscore_local - delta_signal_poly_zscore_local_sem, 
                  fill = region),
              color = NA,
              alpha = 1/3) +
  geom_line() +
  
  facet_grid(.~group_combined) +
  theme_ag01() +
  scale_color_viridis_d(end = 0.8, option = 'magma') +
  scale_fill_viridis_d(end = 0.8, option = 'magma') 

plt <- plt %>%
  add_scale_bar(
    origin = c(-3, -2), 
    x_len = 1, 
    y_len = 1
  )

plt +
  force_panelsizes(cols = unit(plt_dims[1],'cm'), rows = unit(plt_dims[2]*1.8, 'cm'))

save_pdf(dir_output, 'opto_stim_timerel_vs_zscore_trace.pdf', 12, 6)
write_csv(plt_data, str_c(dir_output, 'opto_stim_timerel_vs_zscore_trace_data.csv'))

```

```{r}
plt_data <- streams_peth_group %>%
  filter(time_rel > -1, time_rel < 6) 


plt <- plt_data %>%
  ggplot(aes(time_rel, delta_signal_poly_zscore_local, color = trial_stim_frequency, fill = trial_stim_frequency, group = trial_stim_frequency)) +
  annotate("rect", xmin = 0, xmax = 3, ymin = -Inf, ymax = Inf, alpha = 1/3, fill = "darkgrey") +
  geom_hline(yintercept = 0, color = 'darkgrey', size = 0.5) +
  geom_ribbon(aes(ymax = delta_signal_poly_zscore_local + delta_signal_poly_zscore_local_sem, 
                  ymin = delta_signal_poly_zscore_local - delta_signal_poly_zscore_local_sem),
              color = NA,
              alpha = 1/3) +
  geom_line() +
  facet_grid(group_combined~region) +
  theme_ag01() +
  scale_color_viridis_c(end = 0.8, option = 'magma') +
  scale_fill_viridis_c(end = 0.8, option = 'magma') 

plt <- plt %>%
  add_scale_bar(
    origin = c(-3, -2), 
    x_len = 1, 
    y_len = 1
  )

plt +
  force_panelsizes(cols = unit(plt_dims[1]*1/2.1,'cm'), rows = unit(plt_dims[2], 'cm'))

save_pdf(dir_output, 'optochar_time_vs_zscore_trace_combinedgroup.pdf', 12, 8)
write_csv(plt_data, str_c(dir_output, 'optochar_time_vs_zscore_trace_combinedgroup_data.csv'))
```

```{r}
# initial ~~~~~~~~~~~~~~~~

streams_peth_summary <- streams_peth %>%
  filter(time_rel > 0, time_rel <= 1) %>% 
  group_by(blockname, subject, line, group, trial_stim_frequency, region) %>%
  summarise(delta_signal_poly_zscore_local := mean(delta_signal_poly_zscore_local), .groups = 'drop') %>%
  mutate(trial_stim_frequency = as.character(trial_stim_frequency) %>% factor(levels = c(0,1,2,5,10,20,40)))


streams_peth_summary_group <- streams_peth_summary %>%
  format_group_combined() %>%
  group_by(group_combined, trial_stim_frequency, region) %>%
  summarise(delta_signal_poly_zscore_local := mean(delta_signal_poly_zscore_local), .groups = 'drop') %>%
  mutate(trial_stim_frequency = as.character(trial_stim_frequency) %>% factor(levels = c(0,1,2,5,10,20,40)))

plt_data <- streams_peth_summary_group %>%
  rename(zscore = delta_signal_poly_zscore_local) 

plt_data %>%
  ggplot(aes(trial_stim_frequency, region, fill = zscore)) +
  geom_tile() +
  scale_fill_gradientn(colors = c('blue', 'white', 'red'), limits = c(-6,6), oob = scales::squish) +
  theme_ag01() +
  facet_grid(.~group_combined) +  
  coord_cartesian(xlim = c(0.5, 5.5), ylim = c(0.5, 6.5), expand = F) +
  force_panelsizes(cols = unit(plt_dims[1],'cm'), rows = unit(plt_dims[2], 'cm')) +
  ylab('GRAB-DA Region') +
  xlab('LHA Stim Freq (Hz)') +
  ggtitle('Initial (0-1s)')



save_pdf(dir_output, 'opto_stim_freq_vs_region_heat_initial.pdf', 12, 6)
write_csv(plt_data, str_c(dir_output, 'opto_stim_freq_vs_region_heat_initial_data.csv'))

# sustained ~~~~~~~~~~~~~~~~

streams_peth_summary <- streams_peth %>%
  filter(time_rel > 2, time_rel <= 3) %>% 
  group_by(blockname, subject, group_combined, line, group, trial_stim_frequency, region) %>%
  summarise(delta_signal_poly_zscore_local := mean(delta_signal_poly_zscore_local), .groups = 'drop') %>%
  mutate(trial_stim_frequency = as.character(trial_stim_frequency) %>% factor(levels = c(0,1,2,5,10,20,40)))


streams_peth_summary_group <- streams_peth_summary %>%
  group_by(group_combined, trial_stim_frequency, region) %>%
  summarise(delta_signal_poly_zscore_local := mean(delta_signal_poly_zscore_local), .groups = 'drop') %>%
  mutate(trial_stim_frequency = as.character(trial_stim_frequency) %>% factor(levels = c(0,1,2,5,10,20,40)))

plt_data <- streams_peth_summary_group %>%
  rename(zscore = delta_signal_poly_zscore_local) 


plt_data %>%
  ggplot(aes(trial_stim_frequency, region, fill = zscore)) +
  geom_tile() +
  scale_fill_gradientn(colors = c('blue', 'white', 'red'), limits = c(-6,6), oob = scales::squish) +
  theme_ag01() +
  facet_grid(.~group_combined) +
  coord_cartesian(xlim = c(0.5, 5.5), ylim = c(0.5, 6.5), expand = F) +
  force_panelsizes(cols = unit(plt_dims[1],'cm'), rows = unit(plt_dims[2], 'cm')) +
  ylab('GRAB-DA Region') +
  xlab('LHA Stim Freq (Hz)') +
  ggtitle('Sustained (2-3s)')

save_pdf(dir_output, 'opto_stim_freq_vs_region_heat_sustained.pdf', 12, 6)
write_csv(plt_data, str_c(dir_output, 'opto_stim_freq_vs_region_heat_sustained_data.csv'))
```


## summary
```{r}
plt_data <- streams_peth %>%
  format_group_combined() %>%
  filter(time_rel > 0, time_rel <= 1) %>% 
  group_by(subject, group_combined, line, group, trial_stim_frequency, region) %>%
  summarise(delta_signal_poly_zscore_local := mean(delta_signal_poly_zscore_local), .groups = 'drop') %>%
  mutate(trial_stim_frequency = as.character(trial_stim_frequency) %>% factor(levels = c(0,1,2,5,10,20,40))) %>%
  filter(trial_stim_frequency == 20) %>%
  rename(zscore = delta_signal_poly_zscore_local) 

plt_data %>%
  ggplot(aes(region, zscore, color = group_combined, fill = group_combined)) +
  geom_hline(yintercept = 0, alpha = 1/3) +
  stat_summary(
    fun.data = 'mean_se', 
    geom = 'errorbar', 
    aes(group = group_combined),
    width = 0.3,
    position = position_dodge(width = 0.75)) +
  stat_summary(
    fun = 'mean',
    geom = 'bar',
    color = NA,
    aes(group = group_combined),
    alpha = 1/2,
    width = 0.6,
    position = position_dodge(width = 0.75)) +
  geom_jitter(shape = 21, color = 'white', size = 1.5, stroke = 0.25,
              position = position_jitterdodge(jitter.width = 0.04, dodge.width = 0.75)) +
  theme_ag01() +
  theme(axis.text.x = element_text(angle = 90, hjust = 1, vjust = 0.3)) +
  scale_color_manual(values = color_group_combined) +
  scale_fill_manual(values = color_group_combined) +
  coord_cartesian(xlim = c(0.5, 6.5), ylim = c(-5,20), expand = F) +
  force_panelsizes(cols = unit(plt_dims[1]*1.25,'cm'), rows = unit(plt_dims[2]*2/3, 'cm')) +
  ylab('Z-Score') +
  xlab('') +
  ggtitle('Initial (0-1s) \n')


save_pdf(dir_output, 'optochar_20Hz_regeion_vs_zscore_combinedgroup_initial_bar.pdf', 8, 6)
```


```{r}
loop_regions <- plt_data %>% pull(region) %>% unique() 

for(loop_region in loop_regions){
  
  plt_data_wide <- plt_data %>%
    select(region, subject, group_combined, zscore) %>%
    spread(group_combined, zscore) %>%
    filter(region == loop_region) 
  
  loop_result <- bind_rows(
    plt_data_wide %>%
      tidy_wilcox_unpaired('control','vgat_stim') %>%
      mutate(comparision = 'control_vs_vgat'),
    
    plt_data_wide %>%
      tidy_wilcox_unpaired('control','vglut2_stim') %>%
      mutate(comparision = 'control_vs_vglut2')
  ) %>%
    clean_names() %>%
    mutate(region = loop_region) %>%
    select(region, comparision, everything()) %>%
    mutate(p_value = p_value * 2) %>%
    quick_sig()
  
  if(loop_region == loop_regions[1]){
    combined_result <- loop_result
  } else {
    combined_result <- loop_result %>%
      bind_rows(combined_result,.)
    }
}

combined_result %>%
  mutate(region = region %>% factor(levels = key_regions$region_label)) %>%
  ggplot(aes(region, comparision, label = sig_symbol)) +
  geom_text()

combined_result %>% write_csv(str_c(dir_output, 'optochar_20Hz_regeion_vs_zscore_combinedgroup_initial_bar_stats.csv'))
plt_data %>% write_csv(str_c(dir_output, 'optochar_20Hz_regeion_vs_zscore_combinedgroup_initial_bar_data.csv'))

```

```{r}
plt_data %>%
  select(subject, group_combined) %>%
  arrange(subject) %>%
  unique()
```



```{r}
plt_data <- streams_peth %>%
  
  filter(time_rel > 2, time_rel <= 3) %>% 
  group_by(subject, group_combined, line, group, trial_stim_frequency, region) %>%
  summarise(delta_signal_poly_zscore_local := mean(delta_signal_poly_zscore_local), .groups = 'drop') %>%
  mutate(trial_stim_frequency = as.character(trial_stim_frequency) %>% factor(levels = c(0,1,2,5,10,20,40))) %>%
  filter(trial_stim_frequency == 20) %>%
  rename(zscore = delta_signal_poly_zscore_local)

plt_data %>%
  ggplot(aes(region, zscore, color = group_combined, fill = group_combined)) +
  geom_hline(yintercept = 0, alpha = 1/3) +
  stat_summary(
    fun.data = 'mean_se', 
    geom = 'errorbar', 
    aes(group = group_combined),
    width = 0.3,
    position = position_dodge(width = 0.75)) +
  stat_summary(
    fun = 'mean',
    geom = 'bar',
    color = NA,
    aes(group = group_combined),
    alpha = 1/2,
    width = 0.6,
    position = position_dodge(width = 0.75)) +
  geom_jitter(shape = 21, color = 'white', size = 1.5, stroke = 0.25,
              position = position_jitterdodge(jitter.width = 0.04, dodge.width = 0.75)) +
  theme_ag01() +
  theme(axis.text.x = element_text(angle = 90, hjust = 1, vjust = 0.3)) +
  scale_color_manual(values = color_group_combined) +
  scale_fill_manual(values = color_group_combined) +
  coord_cartesian(xlim = c(0.5, 6.5), ylim = c(-10,30), expand = F, clip = 'off') +
  force_panelsizes(cols = unit(plt_dims[1]*1.25,'cm'), rows = unit(plt_dims[2]*2/3, 'cm')) +
  ylab('Z-Score') +
  xlab('') +
  ggtitle('Sustained (2-3s) \n')

save_pdf(dir_output, 'optochar_20Hz_regeion_vs_zscore_combinedgroup_sustained_bar.pdf', 8, 6)


```



```{r}
loop_regions <- plt_data %>% pull(region) %>% unique() 

for(loop_region in loop_regions){
  
  plt_data_wide <- plt_data %>%
    select(region, subject, group_combined, zscore) %>%
    spread(group_combined, zscore) %>%
    filter(region == loop_region) 
  
  loop_result <- bind_rows(
    plt_data_wide %>%
      tidy_wilcox_unpaired('control','vgat_stim') %>%
      mutate(comparision = 'control_vs_vgat'),
    
    plt_data_wide %>%
      tidy_wilcox_unpaired('control','vglut2_stim') %>%
      mutate(comparision = 'control_vs_vglut2')
  ) %>%
    clean_names() %>%
    mutate(region = loop_region) %>%
    select(region, comparision, everything()) %>%
    mutate(p_value = p_value * 2) %>%
    quick_sig()
  
  if(loop_region == loop_regions[1]){
    combined_result <- loop_result
  } else {
    combined_result <- loop_result %>%
      bind_rows(combined_result,.)
    }
}

combined_result %>%
  mutate(region = region %>% factor(levels = key_regions$region_label)) %>%
  ggplot(aes(region, comparision, label = sig_symbol)) +
  geom_text()

combined_result %>% write_csv(str_c(dir_output, 'optochar_20Hz_regeion_vs_zscore_combinedgroup_sustained_bar_stats.csv'))
plt_data %>% write_csv(str_c(dir_output, 'optochar_20Hz_regeion_vs_zscore_combinedgroup_sustained_bar_data.csv'))
```




```{r}
plt_data <- streams_peth %>%
  filter(time_rel > 2, time_rel <= 3) %>% 
  group_by(subject, group_combined, line, group, trial_stim_frequency, region) %>%
  summarise(delta_signal_poly_zscore_local := mean(delta_signal_poly_zscore_local), .groups = 'drop') %>%
  mutate(trial_stim_frequency = as.character(trial_stim_frequency) %>% factor(levels = c(0,1,2,5,10,20,40))) %>%
  filter(trial_stim_frequency == 20) %>%
  rename(zscore = delta_signal_poly_zscore_local)  %>%
  #filter(!(subject == 'abo11' & region == 'NAcCR'))  %>%
  join_placements() %>%
  select(subject, group_combined, region, zscore, starts_with('hit')) %>%
  mutate(region = region %>% factor(levels = key_regions$region_label))


plt_data %>%
  ggplot(aes(hit_ml, hit_dv, color = zscore)) +
  geom_point(size = 5) +
  scale_color_viridis_c(limits = c(-5, 5),oob = scales::squish) +
  facet_grid(group_combined~region, scales = 'free')
```



## placement plots
```{r}

fn_stem <- 'placement_vs_zscore_sustained'

for(loop_group in c('control', 'vgat_stim', 'vglut2_stim')){
  
  df <- streams_peth %>%
    filter(group_combined == loop_group) %>%
    filter(time_rel > 2, time_rel <= 3) %>% 
    group_by(subject, group_combined, line, group, trial_stim_frequency, region) %>%
    summarise(delta_signal_poly_zscore_local := mean(delta_signal_poly_zscore_local), .groups = 'drop') %>%
    mutate(trial_stim_frequency = as.character(trial_stim_frequency) %>% factor(levels = c(0,1,2,5,10,20,40))) %>%
    filter(trial_stim_frequency == 20) %>%
    rename(zscore = delta_signal_poly_zscore_local)  %>%
    join_placements() %>%
    select(subject, group_combined, region, zscore, starts_with('hit')) %>%
    mutate(region = region %>% factor(levels = key_regions$region_label))
  
  var_color <- 'zscore'
  color_limits <- c(-6,6)
  
  plt_str(
    df = df, 
    var_color = !!sym(var_color),
    var_color_name = 'z-score',
    vars_facet = c('.','.'),
    plt_plane = 'sagittal',
    plt_dim_base = 3,
    color_limits = color_limits
    )
  
  save_pdf(str_c(dir_output, 'placements/'), str_c(fn_stem,'_', loop_group, '_sagittal.pdf'),6,6)
  
  plt_str(
    df = df,
    var_color = !!sym(var_color),
    var_color_name = 'z-score',
    vars_facet = c('.','.'),
    plt_plane = 'horizontal',
    plt_dim_base = 3,
    color_limits = color_limits
    ) 
  
  save_pdf(str_c(dir_output, 'placements/'), str_c(fn_stem,'_', loop_group, '_horizontal.pdf'),6,6)
  
  plt_str(
    df = df,
    var_color = !!sym(var_color),
    var_color_name = 'z-score',
    vars_facet = c('.','.'),
    plt_plane = 'coronal',
    plt_dim_base = 3,
    color_limits = color_limits
    )
  
  save_pdf(str_c(dir_output, 'placements/'), str_c(fn_stem,'_', loop_group, '_coronal.pdf'),6,6)
  
  plt_str_3d(
    df = df, 
    var_color = var_color, 
    color_limits = color_limits,
    dir_output = str_c(dir_output, 'placements/'),
    fn_stem = str_c(fn_stem,'_', loop_group),
    toggle_save = 1
    )

}
```



```{r, fig.height = 6, fig.width = 9}




plt_list <- plt_corr(
  df = plt_data, 
  ylim_all = c(-10,30), 
  xlim_ap = c(-3, 0, 3),
  xlim_ml = c(0, 2, 4),
  xlim_dv = c(-6, -4, -2),
  var_dep = 'zscore', 
  var_dep_label = 'Z-Score', 
  plt_dims = c(3, 3*2/3), 
  cor_text_y = 30
)




# run pearsons
plt_list[['AP']] + 
  plt_list[['ML']] + 
  plt_list[['DV']] +
  plot_layout(nrow = 1, widths = unit(3*2/3, 'cm'), heights = unit(4, 'cm'), guides = 'collect')
  
save_pdf(str_c(dir_output, 'placements/'), 'pos_vs_zscore_sustained.pdf',6,6)

plt_data %>%
  write_csv(str_c(dir_output, 'placements/', 'pos_vs_zscore_sustationd_data.csv'))

plt_list[['stats_output']] %>%
  write_csv(str_c(dir_output, 'placements/', 'pos_vs_zscore_sustationd_corr.csv'))
```



# Opto inhibtion
## import / process
### opto stim ids
```{r}
dir_output <- './analysis_output_final/inhibition/'

preprocess <- 1

if(preprocess){
  
  
  
  import_fns <-  log_tdt %>%
    filter(experiment %in% c('acd')) %>%
    filter(procedure == 'opto_characterization_inhibition') %>%
    
    group_by(subject) %>%
    filter(date == max(date)) %>% # filter to second session
    
    pull(blockname) %>% 
    unique() 
  
  
  stim_params <- return_stim_params(import_fns, dir_arduino_extraction, file_format_output) 
  
  stim_params <- stim_params %>%
    select(blockname, stim_num, trial_stim_frequency) %>%
    filter(trial_stim_frequency != 0) %>%
    arrange(blockname, stim_num) 
  
  
  
  
  # tdt
  data_list <- combined_import(import_directory = dir_tdt_processed, 
                               filter_strings = import_fns,
                               prefixes = NA,
                               suffixes = c('streams_session.feather', 'streams_peth.feather', 'events.feather'), 
                               verbose = 0
  )
  
  streams      <- data_list[[1]] %>% ungroup()
  streams_peth <- data_list[[2]] %>% ungroup()
  events       <- data_list[[3]] %>% ungroup()
  
  # join in region identify from log_tdt
  join_region <- log_tdt %>%
    filter(experiment %in% c('acd')) %>%
    filter(procedure == 'opto_characterization_inhibition') %>%
    select(blockname, fiber_id01, fiber_id02) %>%
    gather(fiber_id, region, starts_with('fiber_id')) %>%
    mutate(fiber_id = fiber_id %>% str_remove('fiber_id0'))
  
  streams <- streams %>%
    left_join(join_region, join_by(blockname, fiber_id)) 
  
  streams_peth <- streams_peth %>%
    left_join(join_region, join_by(blockname, fiber_id))
  
  streams_peth <- streams_peth %>%
    left_join(log_tdt %>% select(blockname, subject)) %>%
    left_join(log_subject %>% select(subject, line)) %>%
    filter(time_rel > -3, time_rel < 20)
  
  
  local_zs_window <- c(-3, 0)
  
  streams_peth <- streams_peth %>%
    group_by(blockname, signal_wavelength, region) %>%
    filter(time_rel > local_zs_window[1], time_rel < local_zs_window[2]) %>%
    summarise(
      delta_signal_poly_local_bl_mu = mean(delta_signal_poly),
      delta_signal_poly_local_bl_sd = sd(delta_signal_poly),
      delta_control_poly_local_bl_mu = mean(delta_control_poly),
      delta_control_poly_local_bl_sd = sd(delta_control_poly),
      .groups = 'drop'
    ) %>%
    left_join(streams_peth, ., by = c("blockname", "signal_wavelength", "region")) %>%
    mutate(
      delta_signal_poly_zscore_local = (delta_signal_poly - delta_signal_poly_local_bl_mu) / delta_signal_poly_local_bl_sd,
      delta_control_poly_zscore_local = (delta_control_poly - delta_control_poly_local_bl_mu) / delta_control_poly_local_bl_sd
    ) %>%
    select(-delta_signal_poly_local_bl_mu, -delta_signal_poly_local_bl_sd)
  
  
  streams_peth <- streams_peth %>%
    filter(time_rel > -3, time_rel < 0) %>%
    group_by(blockname, event_number, region, signal_wavelength) %>%
    summarise(bl = mean(delta_signal_poly_zscore_local), .groups = 'drop') %>%
    left_join(streams_peth,.) %>%
    mutate(delta_signal_poly_zscore_local := delta_signal_poly_zscore_local - bl) %>%
    select(-bl) %>%
    left_join(log_subject %>% select(subject, group), by = c('subject'))
  
  streams_peth_summary <- streams_peth %>%
    filter(time_rel > 5, time_rel < 10) %>% 
    group_by(blockname, subject, line, group, region) %>%
    summarise(delta_signal_poly_zscore_local := mean(delta_signal_poly_zscore_local), .groups = 'drop') 
  
  streams_peth_summary_group <- streams_peth_summary %>%
    group_by(group, line, region) %>%
    summarise(delta_signal_poly_zscore_local := mean(delta_signal_poly_zscore_local), .groups = 'drop')
  
  # format regions
  streams_peth <- streams_peth %>% format_df()
  
  streams_peth <- streams_peth %>% filter_placements()
  
  # remove outlier determined with Grubbs test
  streams_peth <- streams_peth %>% filter(!(subject == 'acd18' & region == 'NAcCR'))
  
  #Grubbs test for one outlier
  #data:  plt_data$zscore 
  #G = 5.41080, U = 0.67474, p-value = 1.356e-07
  #alternative hypothesis: lowest value -6.97189769496844 is an outlier
  
  streams_peth_summary <- streams_peth %>%
    filter(time_rel > 2, time_rel < 10) %>% 
    group_by(blockname, subject, group_combined, line, group, region) %>%
    summarise(delta_signal_poly_zscore_local = mean(delta_signal_poly_zscore_local), .groups = 'drop') 
  
  streams_peth_summary_group <- streams_peth_summary %>%
    group_by(group_combined, group, line, region) %>%
    summarise(delta_signal_poly_zscore_local = mean(delta_signal_poly_zscore_local), .groups = 'drop')
  
  
  
  streams_peth <- streams_peth %>%  mutate(region = region %>% factor(levels = key_regions$region_label))
  streams_peth_summary <- streams_peth_summary %>%  mutate(region = region %>% factor(levels = key_regions$region_label))
  streams_peth_summary_group <- streams_peth_summary_group %>%  mutate(region = region %>% factor(levels = key_regions$region_label))
  
  streams_peth_subject <- streams_peth %>%
    format_group_combined() %>%
    group_by(group_combined, subject, region, time_rel) %>%
    summarise(delta_signal_poly_zscore_local = mean(delta_signal_poly_zscore_local), .groups = 'drop') 
  
  streams_peth_group <- streams_peth %>%
    format_group_combined() %>%
    group_by(group_combined, region, time_rel) %>%
    summarise(
      delta_signal_poly_zscore_local_sem = sd(delta_signal_poly_zscore_local)/sqrt(n()),
      delta_signal_poly_zscore_local = mean(delta_signal_poly_zscore_local),
      .groups = 'drop') 
    
  # save data
  streams_peth %>%
    select(blockname, line, group, subject, fiber_id, region, time, time_rel, event_number,  delta_signal_poly_zscore_local) %>%
    write_csv(str_c(dir_output, 'data_streams_peth_full.csv'))
  
  
  streams_peth_summary %>%
    write_csv(str_c(dir_output, 'data_streams_peth_summary.csv'))
  
  
  streams_peth_summary_group %>%
    write_csv(str_c(dir_output, 'data_streams_peth_summary_group.csv'))
  
  
  streams_peth_subject <- streams_peth %>%
    write_csv(str_c(dir_output, 'data_streams_peth_summary_trace_subject.csv'))
  
  streams_peth_group <- streams_peth_group %>%
    write_csv(str_c(dir_output, 'data_streams_peth_summary_trace_group.csv'))
    
} else {
  streams_peth <-  read.csv(str_c(dir_output, 'data_streams_peth_full.csv'))  %>% mutate(region = region %>% factor(levels = key_regions$region_label))
  streams_peth_summary <- read.csv(str_c(dir_output, 'data_streams_peth_summary.csv')) %>% mutate(region = region %>% factor(levels = key_regions$region_label))
  streams_peth_summary_group <- read.csv(str_c(dir_output, 'data_streams_peth_summary_group.csv')) %>% mutate(region = region %>% factor(levels = key_regions$region_label))
  streams_peth_subject <- read.csv(str_c(dir_output, 'data_streams_peth_summary_trace_subject.csv')) %>% mutate(region = region %>% factor(levels = key_regions$region_label))
  streams_peth_group <- read.csv(str_c(dir_output, 'data_streams_peth_summary_trace_group.csv')) %>% mutate(region = region %>% factor(levels = key_regions$region_label))
    
}
```


## summary of data in analysis
### fiber counts
```{r}
streams_peth_summary %>%
  select(group_combined, region, subject) %>%
  unique() %>%
  group_by(group_combined, region) %>%
  summarise(region_count = n())  %>%
  ggplot(aes(region, group_combined, label = region_count)) +
  geom_text() +
  theme_ag01() +
  theme(axis.text.x = element_text(angle = 90, hjust = 1, vjust = 0.3)) +
  xlab('') +
  ylab('') +
  force_panelsizes(rows = unit(2,'cm'), cols = unit(4, 'cm'))
```

### trial counts
```{r}
streams_peth %>%
  filter(time_rel == 0) %>%
  select(subject, blockname, region, event_number) %>%
  arrange(subject, region, event_number) %>%
  group_by(subject, region) %>%
  summarise(trial_count = n(), .groups = 'drop') %>%
  ggplot(aes(region, subject, label = trial_count)) +
  geom_text() +
  theme_ag01() +
  theme(axis.text.x = element_text(angle = 90, hjust = 1, vjust = 0.3)) +
  xlab('') +
  ylab('') +
  ggtitle('trial counts') +
  force_panelsizes(rows = unit(6,'cm'), cols = unit(4, 'cm'))

```

## plot / analyze
```{r, fig.width = 9, fig.height = 3}
plt_data <- streams_peth_group %>%
  filter(time_rel > -3, time_rel < 20) 

plt <- plt_data %>%
  ggplot(aes(time_rel, delta_signal_poly_zscore_local, color = region, fill = region)) +
  annotate("rect", xmin = 0, xmax = 10, ymin = -Inf, ymax = Inf, alpha = 1/3, fill = "darkgrey") +
  geom_hline(yintercept = 0, color = 'darkgrey', size = 0.5) +
  geom_ribbon(aes(ymax = delta_signal_poly_zscore_local + delta_signal_poly_zscore_local_sem, 
                  ymin = delta_signal_poly_zscore_local - delta_signal_poly_zscore_local_sem, 
                  fill = region),
              color = NA,
              alpha = 1/3) +
  geom_line() +
  
  facet_grid(.~group_combined) +
  theme_ag01() +
  scale_color_viridis_d(end = 0.8, option = 'magma') +
  scale_fill_viridis_d(end = 0.8, option = 'magma') 

plt <- plt %>%
  add_scale_bar(
    origin = c(-3, -2), 
    x_len = 1, 
    y_len = 1
  )

plt +
  force_panelsizes(cols = unit(plt_dims[1],'cm'), rows = unit(plt_dims[2]*1.8, 'cm'))

save_pdf(dir_output, 'opto_stim_timerel_vs_zscore_trace.pdf', 12, 6)
write_csv(plt_data, str_c(dir_output, 'opto_stim_timerel_vs_zscore_trace_data.csv'))

```


```{r}
# sustained ~~~~~~~~~~~~~~~~
plt_data <- streams_peth_summary_group %>%
  rename(zscore = delta_signal_poly_zscore_local) 


plt_data %>%
  ggplot(aes(group_combined, region, fill = zscore)) +
  geom_tile() +
  scale_fill_gradientn(colors = c('blue', 'white', 'red'), limits = c(-3,3), oob = scales::squish) +
  theme_ag01() +
  #facet_grid(.~group_combined) +
  coord_cartesian(xlim = c(0.5, 3.5), ylim = c(0.5, 6.5), expand = F) +
  force_panelsizes(cols = unit(plt_dims[1]/2,'cm'), rows = unit(plt_dims[2], 'cm')) +
  ylab('GRAB-DA Region') +
  xlab('') +
  theme(axis.text.x = element_text(angle = 90, hjust = 1, vjust = 0.3)) +
  ggtitle('Sustained (2-10s)')

save_pdf(dir_output, 'opto_inh_freq_vs_region_heat_sustained.pdf', 12, 6)
write_csv(plt_data, str_c(dir_output, 'opto_inh_freq_vs_region_heat_sustained_data.csv'))
```


## summary
```{r}
plt_data <- streams_peth_summary %>%
  rename(zscore = delta_signal_poly_zscore_local) 

plt_data %>%
  ggplot(aes(region, zscore, color = group_combined, fill = group_combined)) +
  geom_hline(yintercept = 0, alpha = 1/3) +
  stat_summary(
    fun.data = 'mean_se', 
    geom = 'errorbar', 
    aes(group = group_combined),
    width = 0.3,
    position = position_dodge(width = 0.75)) +
  stat_summary(
    fun = 'mean',
    geom = 'bar',
    color = NA,
    aes(group = group_combined),
    alpha = 1/2,
    width = 0.6,
    position = position_dodge(width = 0.75)) +
  geom_jitter(shape = 21, color = 'white', size = 1.5, stroke = 0.25,
              position = position_jitterdodge(jitter.width = 0.04, dodge.width = 0.75)) +
  theme_ag01() +
  theme(axis.text.x = element_text(angle = 90, hjust = 1, vjust = 0.3)) +
  scale_color_manual(values = color_group_combined) +
  scale_fill_manual(values = color_group_combined) +
  coord_cartesian(xlim = c(0.5, 6.5), ylim = c(-5,5), expand = F, clip = 'off') +
  force_panelsizes(cols = unit(plt_dims[1]*1.25,'cm'), rows = unit(plt_dims[2]*4/3, 'cm')) +
  ylab('Z-Score') +
  xlab('') +
  ggtitle('Sustained (2-10s) \n')


save_pdf(dir_output, 'optochar_region_vs_zscore_combinedgroup_sustained_bar.pdf', 8, 6)
```



```{r}
loop_regions <- plt_data %>% pull(region) %>% unique() 

for(loop_region in loop_regions){
  
  plt_data_wide <- plt_data %>%
    select(region, subject, group_combined, zscore) %>%
    spread(group_combined, zscore) %>%
    filter(region == loop_region) 
  
  loop_result <- bind_rows(
    plt_data_wide %>%
      tidy_wilcox_unpaired('control','vgat_inh') %>%
      mutate(comparision = 'control_vs_vgat'),
    
    plt_data_wide %>%
      tidy_wilcox_unpaired('control','vglut2_inh') %>%
      mutate(comparision = 'control_vs_vglut2')
  ) %>%
    clean_names() %>%
    mutate(region = loop_region) %>%
    select(region, comparision, everything()) %>%
    mutate(p_value = p_value * 2) %>%
    quick_sig()
  
  if(loop_region == loop_regions[1]){
    combined_result <- loop_result
  } else {
    combined_result <- loop_result %>%
      bind_rows(combined_result,.)
    }
}

combined_result %>%
  mutate(region = region %>% factor(levels = key_regions$region_label)) %>%
  ggplot(aes(region, comparision, label = sig_symbol)) +
  geom_text()

combined_result %>% write_csv(str_c(dir_output, 'optochar_region_vs_zscore_combinedgroup_sustained_bar_stats.csv'))
```




## placement plots

```{r}
fn_stem <- 'placement_vs_zscore_sustained'

for(loop_group in c('control', 'vgat_inh', 'vglut2_inh')){
  
  df <- streams_peth_summary %>%
    filter(group_combined == loop_group) %>%
    rename(zscore = delta_signal_poly_zscore_local)  %>%
    join_placements() %>%
    select(subject, group_combined, region, zscore, starts_with('hit')) %>%
    mutate(region = region %>% factor(levels = key_regions$region_label))
  
  var_color <- 'zscore'
  color_limits <- c(-3,3)
  
  plt_str(
    df = df, 
    var_color = !!sym(var_color),
    var_color_name = 'z-score',
    vars_facet = c('.','.'),
    plt_plane = 'sagittal',
    plt_dim_base = 3,
    color_limits = color_limits
    )
  
  save_pdf(str_c(dir_output, 'placements/'), str_c(fn_stem,'_', loop_group, '_sagittal.pdf'),6,6)
  
  plt_str(
    df = df,
    var_color = !!sym(var_color),
    var_color_name = 'z-score',
    vars_facet = c('.','.'),
    plt_plane = 'horizontal',
    plt_dim_base = 3,
    color_limits = color_limits
    ) 
  
  save_pdf(str_c(dir_output, 'placements/'), str_c(fn_stem,'_', loop_group, '_horizontal.pdf'),6,6)
  
  plt_str(
    df = df,
    var_color = !!sym(var_color),
    var_color_name = 'z-score',
    vars_facet = c('.','.'),
    plt_plane = 'coronal',
    plt_dim_base = 3,
    color_limits = color_limits
    )
  
  save_pdf(str_c(dir_output, 'placements/'), str_c(fn_stem,'_', loop_group, '_coronal.pdf'),6,6)
  
  plt_str_3d(
    df = df, 
    var_color = var_color, 
    color_limits = color_limits,
    dir_output = str_c(dir_output, 'placements/'),
    fn_stem = str_c(fn_stem,'_', loop_group),
    toggle_save = 1
    )

}
```



```{r, fig.height = 6, fig.width = 9}

plt_data <- streams_peth_summary %>%
    rename(zscore = delta_signal_poly_zscore_local)  %>%
    join_placements()




plt_list <- plt_corr(
  df = plt_data, 
  ylim_all = c(-4,4), 
  xlim_ap = c(-3, 0, 3),
  xlim_ml = c(0, 2, 4),
  xlim_dv = c(-6, -4, -2),
  var_dep = 'zscore', 
  var_dep_label = 'Z-Score', 
  plt_dims = c(3, 3*2/3),
  cor_text_y = 4
)




# run pearsons
plt_list[['AP']] + 
  plt_list[['ML']] + 
  plt_list[['DV']] +
  plot_layout(nrow = 1, widths = unit(3*2/3, 'cm'), heights = unit(4, 'cm'), guides = 'collect')
  
save_pdf(str_c(dir_output, 'placements/'), 'pos_vs_zscore_sustained.pdf',6,6)

plt_data %>%
  write_csv(str_c(dir_output, 'placements/', 'pos_vs_zscore_sustationd_data.csv'))

plt_list[['stats_output']] %>%
  write_csv(str_c(dir_output, 'placements/', 'pos_vs_zscore_sustationd_corr.csv'))

```



















