---
title: "abo_analysis_opto_multispout"
author: "adam gordon-fennell"
date: "2024-04-15"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


```{r}
library(tidyverse)
library(afex)
library(emmeans)
library(janitor)
library(readxl)
library(googlesheets4)
library(ggh4x) # force_panelsizes
library(arrow)
library(zoo)
library(lubridate)
library(patchwork)
library(ggbeeswarm)
library(ggpubr) #r2 on correlation
library(pals)
library(plotly)

source('./functions/r_plots.R')
source('./functions/r_stats.R')
source('./functions/r_general.R')
source('./functions/r_fp.R')
source('./functions/r_head_fixed_processing.R')
```

# setup
```{r}
manual_experiments <- c('abw')
file_format_output <- 'csv'
```


# preprocessing
## arduino
```{r}
# directories 
dir_arduino_extraction <- './data/arduino/extracted/'
dir_arduino_processed <- './data/arduino/processed/'
dir_arduino_raw <- './data/arduino/raw/'
dir_output <- './analysis_output/'

key_events <- read_sheet('https://docs.google.com/spreadsheets/d/1e3ltGi7oNBvIpCgUCcZL2Jm8nmv8eVBoPXvdoowNZx4') 

log_subject <- read_sheet("https://docs.google.com/spreadsheets/d/17GC2tzKHKuWCZAyj84ubsPTvLsfepKFjl_LnaZ8jxdw/edit#gid=0", na = 'NA', sheet = 'subject')

log_npm <- read_sheet('https://docs.google.com/spreadsheets/d/1v-G8GHYPGtJWXARZYqcndO03d23umsTo98BAb5_WnrY', na = c('','NA'))


# multi-spout
log_data_multi <- read_sheet("https://docs.google.com/spreadsheets/d/1x0O82yfHucLKToSwA5IU38FnBFcSAg_tdZwx-depFZI/edit#gid=861277778", na = c('NA','')) 

log_multi_spout_ids <- read_sheet("https://docs.google.com/spreadsheets/d/1x0O82yfHucLKToSwA5IU38FnBFcSAg_tdZwx-depFZI", na = c('NA',''), sheet = 'multi_spout_ids')
```


## multi-spout
```{r, meassage = FALSE}
manual_blocknames <- log_data_multi %>%
  filter(experiment %in% manual_experiments) %>%
  pull(blockname)

extract_serial_output(dir_arduino_raw, key_events, dir_arduino_extraction, manual_experiments, manual_blocknames = manual_blocknames, file_format_output, overwrite = 0)

manual_blocknames_multi <- log_data_multi %>%
  filter(experiment %in% manual_experiments) %>%
  filter(procedure %in% c('water_nacl_opto', 'water_nacl_dry_opto')) %>%
  pull(blockname) 

process_multi_spout(
  dir_arduino_extraction,
  dir_arduino_processed,
  log_data_multi,
  log_multi_spout_ids,
  file_format_output = file_format_output, 
  manual_blocknames_multi,
  overwrite = 0,
  time_bin_width = 100,
  time_bin_range = c(0,3000), 
  session_trial_width = 10,
  session_trial_range = c(0,100))
```

## combine data
```{r, message = FALSE}
data_list <- combined_import(import_directory = dir_arduino_processed,
                             filter_strings = manual_blocknames_multi,
                             prefixes = NA,
                             suffixes = c('_data_trial_summary.csv')
                             )

trial_summary_behavior <- data_list[[1]]

```

```{r}

data_list_extraction <- combined_import(import_directory = dir_arduino_extraction,
                             filter_strings = manual_blocknames_multi,
                             prefixes = NA,
                             suffixes = c('_param.csv', '_param_dynamic.csv')
                             )

param <- data_list_extraction[[1]]
param_dynamic <- data_list_extraction[[2]]

```


## opto stim info
```{r, message = FALSE}
manual_fns <- log_data_multi %>% 
  filter(experiment %in% manual_experiments) %>%
  filter(procedure %>% str_detect('_opto')) %>%
  pull(blockname)


log_opto_stim_ids <- suppressWarnings(
  read_sheet("https://docs.google.com/spreadsheets/d/1x0O82yfHucLKToSwA5IU38FnBFcSAg_tdZwx-depFZI", 
             sheet = 'opto_stimulation_ids', 
             na = c('NA', '')
             )
  )%>%
  select(-today) %>%
  filter(experiment %in% manual_experiments)

trial_stim_ids <- return_trial_ids(dir_arduino_extraction, manual_fns, file_format_output, filt_last = 0) %>%
  left_join(log_data_multi %>%
              select(blockname, experiment, date, subject)) %>%
  #mutate(trial_stim_id = trial_stim_id + 1) %>%
  left_join(log_opto_stim_ids %>%
              select(experiment, date, subject, trial_stim_id, stim_power_uw, pulse_frequency, delay, region, id))

```


## functions
```{r}
format_group_combined <- function(df){
  df %>%
    mutate(group_combined = ifelse(line %>% str_detect('vglut2'), 'vglut2', NA))%>%
    mutate(group_combined = ifelse(line %>% str_detect('vgat'), 'vgat', group_combined)) %>%
    mutate(group_combined = ifelse(tolower(group) == 'mcherry', 'control', group_combined)) %>%
    mutate(group_combined = ifelse(tolower(group) == 'chrimson', group_combined %>% str_c('_stim'), group_combined)) %>%
    mutate(group_combined = ifelse(tolower(group) == 'hr', group_combined %>% str_c('_inh'), group_combined)) 
  
}


color_group_combined <- c('darkgrey', '#CC2029', '#70BF46')



key_regions <- tibble(
  region = c(NA, 'nac', 'nac_corr', 'nac_shelllat',  'dms', 'dls', 'ts'),
  region_label = c('None', 'NAcCR', 'NAcCC', 'NAcShL', 'DMS', 'DLS', 'TS')
)

format_regions <- function(df, var_region, key_regions){
  df %>%
    ungroup() %>%
    rename(region = !!as.name(var_region)) %>%
    left_join(key_regions) %>%
    mutate(region_label = factor(region_label, levels = key_regions$region_label)) %>%
    select(-region) %>%
    rename(!!var_region := region_label) %>%
    select(!!var_region, everything())
}


format_stim_id <- function(df){
  df %>%
    mutate(stim_id = case_when(
      stim_id == 'lha' ~ 'LHA',
      stim_id == 'no_stim' ~ 'No stim'
    )) %>%
    mutate(stim_id = factor(stim_id, levels = c('No stim', 'LHA')))
}
```

```{r}
subract_artifact_continuouslaser <- function(df, window_bl, window_artifact, var_grouping){
  
  # filter to baseline window and compute average for variables of intrest
  df %>%
    filter(time_rel >= window_bl[1], time_rel <= window_bl[2]) %>%
    group_by(across(all_of(var_grouping))) %>% 
    summarise(
      zscore_bldist = delta_signal_poly_zscore_blsubdist %>% mean(),
      control_bldist = delta_control_poly_zscore_blsubdist %>% mean(),
      lls_bldist = delta_signal_fitted_control_zscore_blsubdist %>% mean(),
      .groups = 'drop'
    ) %>%
    left_join(df) %>% # join back into original dataset
    
    mutate( # for each variable, subtract out the baseline from time following the baseline window
      
      delta_signal_poly_zscore_blsubdist = ifelse(
        time_rel >= window_artifact[1] & time_rel <= window_artifact[2], 
        delta_signal_poly_zscore_blsubdist - zscore_bldist,
        delta_signal_poly_zscore_blsubdist),
      
      delta_control_poly_zscore_blsubdist = ifelse(
        time_rel >= window_artifact[1] & time_rel <= window_artifact[2],
        delta_control_poly_zscore_blsubdist - control_bldist,
        delta_control_poly_zscore_blsubdist),
      
      delta_signal_fitted_control_zscore_blsubdist = ifelse(
        time_rel >= window_artifact[1] & time_rel <= window_artifact[2],
        delta_signal_fitted_control_zscore_blsubdist - lls_bldist, 
        delta_signal_fitted_control_zscore_blsubdist)
      
    ) %>%
    
    select(
      -zscore_bldist,
      -control_bldist,
      -lls_bldist
    )
  
}
```



```{r}

plt_str <- function(df, var_color, var_color_name, vars_facet, color_limits, plt_plane, plt_dim_base){
  range_ap <- c(-3, 3)
  range_ml <- c(0, 4)
  range_dv <- c(-6, -1)
  
  var_color <- rlang::enquo(var_color)
  facet_formula <- as.formula(paste(vars_facet[1], '~', vars_facet[2]))
  
  if(plt_plane == 'sagittal'){
    plt <- df %>%
      ggplot(aes(hit_ap, hit_dv, color = !!var_color)) +
      coord_cartesian(xlim = range_ap, ylim = range_dv, expand = F) +
      xlab('Anterior-posterior (mm)')+
      ylab('Dorsal-ventral (mm)') 
  }
  
  if(plt_plane == 'coronal'){
    plt <- df %>%
      ggplot(aes(hit_ml, hit_dv, color = !!var_color)) +
      coord_cartesian(xlim = range_ml, ylim = range_dv, expand = F) +
      xlab('Medial-lateral (mm)')+
      ylab('Dorsal-ventral (mm)')
  }
  
  if(plt_plane == 'horizontal'){
    plt <- df %>%
      ggplot(aes(hit_ap, hit_ml, color = !!var_color)) +
      coord_cartesian(xlim =  range_ap, ylim = range_ml, expand = F) +
      xlab('Anterior-posterior (mm)')+
      ylab('Medial-lateral (mm)') 
  }
  
  plt <- plt +
    geom_point(size = 2, alpha = 1)
  
  if(sum(is.na(color_limits)) == 0){
    plt <- plt +
      scale_color_viridis_c(
        limits = color_limits,
        oob = scales::squish,
        name = var_color_name, 
        breaks = color_limits)
  }
  
   plt <- plt+
    theme_ag01() +
    theme(
      legend.key.size = unit(0.5, "cm"),
      legend.key.width = unit(0.2,"cm"),
      legend.title.position = "right",
      panel.grid.major = element_line(color = 'lightgrey', size = 0.5), 
      legend.title = element_text(angle = 270, hjust = 0.5),
      axis.title = element_text(color = "black", size = 10),
      axis.text.x = element_text(color = "black", size = 8, hjust = 0.5),
      axis.text.y = element_text(color = "black", size = 8, hjust = 1, vjust = 0.3, margin = margin(r = 1)),

    ) 
  
  
  plt <- plt +
    facet_grid(facet_formula)
  
  dim_ap <- range_ap[2] - range_ap[1]
  dim_ml <- range_ml[2] - range_ml[1]
  dim_dv <- range_dv[2] - range_dv[1]
  
  
  aspect_sagital <- dim_ap / dim_dv
  aspect_coronal <- dim_ml / dim_dv
  aspect_horizontal <- dim_ap / dim_ml
  
  if(plt_plane == 'sagittal'){
    plt <- plt +
      force_panelsizes(rows = unit(plt_dim_base, 'cm'), cols = unit(plt_dim_base*aspect_sagital, 'cm'))
  } 
    
  if(plt_plane == 'horizontal'){
    plt <- plt +
      force_panelsizes(rows = unit(plt_dim_base, 'cm'), cols = unit(plt_dim_base*aspect_horizontal, 'cm'))
  } 
  
  if(plt_plane == 'coronal'){
    plt <- plt +
      force_panelsizes(rows = unit(plt_dim_base, 'cm'), cols = unit(plt_dim_base*aspect_coronal, 'cm'))
  }
  
  return(plt)
  
}

plt_str_3d <- function(df, var_color, color_limits, dir_output, fn_stem, toggle_save){
  x_range <- c(-3, 3)
  y_range <- c(0, 4)
  z_range <- c(-5, -2)
  
  font.pref.title <- list(size=30, family="Arial, sans-serif", color="black")
  font.pref.tick <- list(size=18, family="Arial, sans-serif", color="black")
  
  i <- -2.5 # x/y eye position
  ii <- 0.5 # z eye position
  
  # Convert the column name to a symbol
  var_color_sym <- sym(var_color)
  
  # Squish the values of var_color within the specified color_limits
  df <- df %>%
    mutate(!!var_color_sym := ifelse(!!var_color_sym > color_limits[2], color_limits[2], !!var_color_sym)) %>%
    mutate(!!var_color_sym := ifelse(!!var_color_sym < color_limits[1], color_limits[1], !!var_color_sym))
  
  # Create the plot
  plt <- plot_ly(df,
          x = ~hit_ap, 
          y = ~hit_ml, 
          z = ~hit_dv, 
          color = ~.data[[var_color]],  # Use the symbol for the color mapping
          type = 'scatter3d', 
          mode = 'markers',  # Plot points only
          marker = list(
            size = 10,
            colorscale = 'Viridis',  
            cmin = color_limits[1],   # Set the minimum value for color scaling
            cmax = color_limits[2]    # Set the maximum value for color scaling
          )
  ) %>%
    layout(scene = list(
             xaxis = list(
               title = 'AP (mm)', 
               range = x_range, 
               tickvals = seq(x_range[1], x_range[2], by = 1),  # Specify x-axis ticks
               ticktext = seq(x_range[1], x_range[2], by = 1),  # Custom labels
               nticks = sum(abs(x_range)), 
               titlefont = font.pref.title,
               tickfont = font.pref.tick,
               zeroline = FALSE,  # Remove emphasis on zero line
               showline = TRUE,   # Keep the axis line visible
               showgrid = TRUE    # Optionally keep grid lines
             ),
             yaxis = list(
               title = 'ML (mm)', 
               range = y_range, 
               tickvals = seq(y_range[1], y_range[2]-1, by = 1),  # Specify y-axis ticks
               ticktext = seq(y_range[1], y_range[2]-1, by = 1),  # Custom labels
               nticks = sum(abs(y_range)), 
               titlefont = font.pref.title,
               tickfont = font.pref.tick,
               zeroline = FALSE,  # Remove emphasis on zero line
               showline = TRUE,  
               showgrid = TRUE   
             ),
             zaxis = list(
               title = 'DV (mm)', 
               range = z_range, 
               tickvals = seq(z_range[1]+1, z_range[2], by = 1),  # Specify z-axis ticks
               ticktext = seq(z_range[1]+1, z_range[2], by = 1),  # Custom labels
               nticks = 6, 
               titlefont = font.pref.title,
               tickfont = font.pref.tick,
               zeroline = FALSE,  # Remove emphasis on zero line
               showline = TRUE,  
               showgrid = TRUE   
             ), 
             #aspectmode='manual',
             # aspectratio = list(
             #   x = (x_range[2] - x_range[1])/3, 
             #   y = (y_range[2] - y_range[1])/3, 
             #   z = (z_range[2] - z_range[1])/3
             #   ),
             camera = list(
               eye = list(x = cos(i)*3, y = sin(i)*3, z = ii*3), 
               center = list(x = 0, y = 0, z = -0.1)
             )
           )
    )
  
  if(toggle_save){
    save_image(plt,
               width = 900,
               height = 800,
               scale = 1,
               str_c(dir_output, fn_stem, ".pdf"))
  } else {
    plt
  }
}

plt_corr <- function(df, ylim_all, xlim_ap, xlim_ml, xlim_dv, var_dep, var_dep_label, plt_dims){
  
  plt_data <- df %>%
    gather('dim', 'mm', starts_with('hit')) %>%
    
    mutate(dim = case_when(
      dim == 'hit_ap' ~ 'AP', #'Anterior-Posterior', 
      dim == 'hit_ml' ~ 'ML', #'Medial-Lateral',
      dim == 'hit_dv' ~ 'DV') #'Dorsal-Ventral'
    ) %>%
    mutate(dim = dim %>% factor(levels = c('AP', 'ML', 'DV'))) # c('Anterior-Posterior', 'Medial-Lateral', 'Dorsal-Ventral')))
  
  f_plt <- function(plt_data, ylim_all, xlim_ap, xlim_ml, xlim_dv, var_dep, var_dep_label, plt_dims, plt_dim){
  
    plt <- plt_data %>%
      filter(dim == plt_dim) %>%
      ggplot(aes(mm, !!as.name(var_dep), color = group_combined, fill = group_combined)) +
      geom_hline(yintercept = 0, color = 'darkgrey', size = 0.5) +
      geom_smooth(method = 'lm', size = 0.3, alpha = 1/5) +
      geom_jitter(shape = 21, size = 2, color = 'white', stroke = 1/3) +
      facet_grid(group_combined~dim, scales = 'free') +
      theme_ag01() +
      scale_color_manual(values = color_group_combined) +
      scale_fill_manual(values = color_group_combined) +
      #force_panelsizes(rows = unit(plt_dims[1], 'cm'), cols = unit(plt_dims[2], 'cm'))
      xlab('MM Relative to bregma') +
      ylab(var_dep_label) +
      theme(strip.text.y = element_blank()) +
      theme(panel.spacing.y = unit(0.75, "lines")) 
  
    if(plt_dim == 'AP'){
      plt <- plt +
        coord_cartesian(ylim = ylim_all, xlim = c(min(xlim_ap), max(xlim_ap)), expand = F, clip = 'off') +
      stat_cor(method = "pearson", label.y = ylim_all[2], label.x = -3, size = 2) +
        scale_x_continuous(breaks = xlim_ap) +
        theme(axis.title.x = element_blank())
    } 
      
    if(plt_dim == 'ML'){
      plt <- plt +
        coord_cartesian(ylim = ylim_all, xlim =  c(min(xlim_ml), max(xlim_ml)), expand = F, clip = 'off') +
      stat_cor(method = "pearson", label.y = ylim_all[2], label.x = 0, size = 2) +
        scale_x_continuous(breaks = xlim_ml) 
      
      plt <- plt %>%
        remove_y_all
    } 
      
    if(plt_dim == 'DV'){
      plt <- plt +
        coord_cartesian(ylim = ylim_all, xlim = c(min(xlim_dv), max(xlim_dv)), expand = F, clip = 'off') +
      stat_cor(method = "pearson", label.y = ylim_all[2], label.x = -6, size = 2) +
        scale_x_continuous(breaks = xlim_dv) +
        theme(axis.title.x = element_blank())
      
      plt <- plt %>%
        remove_y_all
    } 
      
      return(plt)
  }
  
  plt_list <- list()
  
  
  for(plt_dim in c('AP', 'ML', 'DV')){
   plt <- f_plt(plt_data, ylim_all, xlim_ap, xlim_ml, xlim_dv, var_dep, var_dep_label, plt_dims, plt_dim)
   plt_list[[plt_dim]] <- plt
   
  }
  
  # compute stats
  stats_output <- plt_data %>%
    tidy_cor('mm', var_dep, 'dim', 'group_combined')
  
  
  plt_list[['stats_output']] <- stats_output
  
  
  return(plt_list)
  
}
```


```{r}
library(corrplot)
library(Hmisc)

tidy_cor_output_reshape <- function(df, n_table, var_name){
  df_tidy <- df[[n_table]] %>%
    as_tibble()
  
  df_tidy <- df_tidy %>%
    mutate(var_y = colnames(df_tidy)) %>%
    gather('var_x', !!as.name(var_name), -var_y) 
  

  
  return(df_tidy)
}

tidy_cor_output <- function(df){
  tidy_cor_output_reshape(df, 1, 'r') %>%
    left_join(tidy_cor_output_reshape(df, 2, 'n'), by = c("var_y", "var_x")) %>%
    left_join(tidy_cor_output_reshape(df, 3, 'p'), by = c("var_y", "var_x"))
}


get_cormatrix <- function(df){
  df_corr = rcorr(as.matrix(df))
  tidy_cor_output(df_corr)
}

tidy_cormatrix <- function(df, var_cors, var_groups = NA){
  require(Hmisc)
  
  df <- df %>%
    ungroup()


  if(sum(is.na(var_groups)) > 0){
    df <- df %>% select(var_cors)
  
    df %>%
      group_modify(~ get_cormatrix(.))
    
  } else {
    df <- df %>% select(var_cors, var_groups)
    
    df %>%
      group_by_at(var_groups) %>%
      group_modify(~ get_cormatrix(.))
    
  }
}
```


# Final: Multi-DA + Water / NaCl + LHA Opto

```{r}
dir_output <- './analysis_output_final/multispout_inhibition_lha/'

plt_dims <- c(3,3)

import_fns <- log_npm %>%
  filter(experiment %in% c('acd')) %>%
  filter(procedure == 'water_nacl_opto') %>%
  filter(exclude == 0) %>%
  pull(blockname)  %>%
  unique()
```



### arduino
```{r} 
data_list <- combined_import(import_directory = dir_arduino_processed,
                             filter_strings = import_fns,
                             prefixes = NA,
                             suffixes = c('_data_trial_summary.csv')
)

trial_summary_behavior <- data_list[[1]]
```


```{r}
trial_summary_behavior <- trial_summary_behavior %>%
  left_join(trial_stim_ids %>%
              select(blockname, trial_num, trial_stim_delay, trial_stim_id, stim_power_uw, pulse_frequency, delay, id), 
            by = c("blockname", "trial_num")) %>%
  left_join(log_data_multi %>%
              select(blockname, subject, procedure, deprivation), 
            by = 'blockname') %>%
  left_join(
    log_subject %>%
      select(subject, group, line), 
    by = "subject"
  ) %>%
  mutate(stim_id = ifelse(is.na(id), 'no_stim', id))


solution_summary_behavior <- trial_summary_behavior %>%
  group_by(experiment, date, group, subject, procedure, stim_id, solution, trial_stim_id) %>%
  summarise(
    lick_count = lick_count %>% mean(), 
    trial_lick_prop = sum(trial_lick) / n(),
    .groups = 'drop') 


```

### npm
```{r}
log_placements <- read_sheet('https://docs.google.com/spreadsheets/d/1dATNdE46yfeKJmNBi51yeO8Iycv4RaMlfdc8xS4YBiY/edit?gid=752886601#gid=752886601', na = c('NA',''), sheet = 'placements') %>%
  filter(experiment == 'acd')

fibers_to_remove <- log_placements %>%
  filter(exclude_da_consumption == 1) %>%
  select(subject, region = target)

```



```{r}
dir_npm_processed <- './data/data_npm/data_processed/'

data_list <- combined_import(import_directory = dir_npm_processed, 
                             filter_strings = import_fns,
                             prefixes = NA,
                             suffixes = c('streams_peth.feather', 'events.feather'), 
                             verbose = 0
)

events       <- data_list[[2]]

streams_peth <- data_list[[1]] %>%
  filter(signal_wavelength == 470) 

streams_peth <- streams_peth %>% 
  mutate(subject = blockname %>% str_sub(12,16))

# subtract out laser artifact
streams_peth <- streams_peth %>% 
  filter(time_rel > -9, time_rel < -6) %>%
  group_by(blockname, event_id_char, branch_id, signal_wavelength, event_number) %>%
  summarise(
    zscore_bl = mean(delta_signal_poly_zscore),
    control_bl = mean(delta_control_poly_zscore),
    zscorells_bl = mean(delta_signal_fitted_control_zscore)
  ) %>%
  left_join(streams_peth,.) %>%
  mutate(
    delta_signal_poly_zscore_blsubdist = delta_signal_poly_zscore - zscore_bl,
    delta_control_poly_zscore_blsubdist = delta_control_poly_zscore - control_bl, 
    delta_signal_fitted_control_zscore_blsubdist = delta_signal_fitted_control_zscore - zscorells_bl
    
    ) %>%
  select(-zscore_bl, -control_bl, -zscorells_bl)
  
streams_peth <- streams_peth %>% 
  subract_artifact_continuouslaser(
    window_bl = c(-5.9, -5.8), 
    window_artifact = c(-5.9, 9),
    var_grouping = c('blockname', 'event_id_char', 'signal_wavelength', 'branch_id', 'event_number'))

# subtract out pre-access response
streams_peth <- streams_peth %>% 
  filter(time_rel > -3, time_rel < 0) %>%
  group_by(blockname, event_id_char, branch_id, signal_wavelength, event_number) %>%
  summarise(
    zscore_bl = mean(delta_signal_poly_zscore_blsubdist),
    control_bl = mean(delta_control_poly_zscore_blsubdist),
    zscorells_bl = mean(delta_signal_fitted_control_zscore_blsubdist)
  ) %>%
  left_join(streams_peth,.) %>%
  mutate(
    delta_signal_poly_zscore_blsub = delta_signal_poly_zscore_blsubdist - zscore_bl,
    delta_control_poly_zscore_blsub = delta_control_poly_zscore_blsubdist - control_bl, 
    delta_signal_fitted_control_zscore_blsub = delta_signal_fitted_control_zscore_blsubdist - zscorells_bl
    
    ) %>%
  select(-zscore_bl, -control_bl, -zscorells_bl)
```




```{r}

trial_summary_behavior %>%
  format_group_combined() %>%
  ggplot(aes(stim_id, lick_count, color = stim_id)) +
  geom_hline(yintercept = seq(0, 20, 5), color = 'gray') +
  geom_quasirandom() +
  facet_grid(solution~group_combined) +
  scale_color_manual(values = c('blue', 'darkgrey'))


trial_summary_behavior %>%
  format_group_combined() %>%
  mutate(lick_count_bin = cut(lick_count, seq(0,20,5))) %>%
  filter(!is.na(lick_count_bin)) %>%
  group_by(group_combined, subject, solution, stim_id, lick_count_bin) %>%
  summarise(number_of_trials = n()) %>%
  ggplot(aes(stim_id, lick_count_bin, fill = number_of_trials)) +
  geom_tile() +
  facet_grid(solution~group_combined, scales = 'free')

```

```{r}
plt_data <- trial_summary_behavior %>%
  format_group_combined() %>%
  mutate(stim_id = stim_id %>% factor(levels = c('no_stim', 'lha'))) %>%
  group_by(group_combined, subject, solution, stim_id) %>%
  summarise(lick_count = lick_count %>% mean()) 

plt_data %>%
  ggplot(aes(stim_id, lick_count, color = solution)) +
  geom_line(aes(group = interaction(subject, solution)), alpha = 1/3) +
  stat_summary(fun = 'mean', geom = 'line', aes(group = solution)) +
  stat_summary(fun.data = 'mean_se', geom = 'errorbar', aes(group = solution), width = 0.1) +
  facet_grid(.~group_combined) 


plt_data %>%
  filter(group_combined %in% c('control', 'vgat_inh')) %>%
  filter(solution == 'water') %>%
  aov_rm_one_between_one_within(NA,NA,'subject','lick_count','group_combined','stim_id')


plt_data %>%
  filter(group_combined %in% c('control', 'vglut2_inh')) %>%
  filter(solution == 'nacl100') %>%
  aov_rm_one_between_one_within(NA,NA,'subject','lick_count','group_combined','stim_id')
```




```{r}
# create streamd_peth_solution and join trial ids
join_trial_summary_behavior <- trial_summary_behavior %>%
  filter(blockname %in% import_fns) %>%
  select(blockname, line, group, trial_num, lick_count, lick_ts_last, solution, stim_id)

streams_peth_solution <- streams_peth %>%
  rename(trial_num = event_number) %>%
  left_join(join_trial_summary_behavior) %>%
  filter(!is.na(solution ))

# join event_number_solution
join_event_number_solution <- streams_peth_solution %>%
  select(blockname, solution, trial_num) %>%
  unique() %>%
  arrange(blockname, trial_num) %>%
  group_by(blockname, solution) %>%
  mutate(event_number_solution = row_number())


streams_peth_solution <- streams_peth_solution %>%
  left_join(join_event_number_solution)
```


```{r}
# filter based on placement and signal quality

# join branch ids  
streams_peth_solution <- streams_peth_solution %>%
  left_join(log_npm %>% select(blockname, branch_id, region)) %>%
  format_regions('region', key_regions) 

# filter out fibers / session x fibers
streams_peth_solution <- streams_peth_solution %>%
  anti_join(fibers_to_remove)


# exclude fibers with poor quality session x branches
fns_qc_metrics <- list.files('C:/Users/stuberadmin/Dropbox/post_doc/experiments/summaries/multi_spout_brief_access_fp_20231229/data/sessions/', pattern = 'quality_metrics.csv', recursive = T, full.names = T)
combined_qc_metrics <- bind_rows(lapply(fns_qc_metrics, read.csv)) 

combined_qc_metrics <- combined_qc_metrics %>%
  format_regions('region', key_regions)

streams_peth_solution <- streams_peth_solution %>%
  left_join(combined_qc_metrics %>% select(blockname, region, exclude_poor_signal), by = c('blockname', 'region')) %>%
  filter(exclude_poor_signal == 0 | is.na(exclude_poor_signal)) %>% # is.na for lha ratio
  select(-exclude_poor_signal)

```



## write info for external use
```{r}
# same trial_summary_behavior for external use 
trial_summary_behavior %>% write.csv(
  './data/behavior_opto_inh/data_trial_summary.csv'
)
```

```{r}
tt <- streams_peth_solution %>%
  filter(time_rel == 0) %>%
  select(blockname) %>%
  unique() %>%
  left_join(log_data_multi) %>%
  select(experiment, date, subject, day, cohort, blockname, box, procedure, beh_program, solution, exclude, exclude_note, block_set, stim_set, deprivation, final_multi_average, imaging, note_general, note_subject)

tt %>%
  write_csv(str_c(dir_output, 'analysis_blocknames.csv'))
```

```{r}
trial_summary_behavior %>%
  filter(blockname %in% tt$blockname) %>%
  select(blockname, trial_num, solution, stim_id)  %>%
  mutate(solution = ifelse(solution == 'Water', 0, 1)) %>%
  mutate(stim_id = ifelse(stim_id == 'No stim', 0, 1)) %>%
  write_csv(str_c(dir_output, 'analysis_trial_ids.csv'))
```



## plotting / analysis
```{r}
df <- streams_peth_solution %>%
  #filter(lick_count > 0) %>% # filter to trails with licking (beware reduction in trials w/ vgat inhibition)
  select(blockname, subject, line, group, region, solution, stim_id, time_rel, delta_signal_poly_zscore, delta_signal_poly_zscore_blsub, delta_signal_poly_zscore_blsubdist, delta_control_poly_zscore_blsub, delta_control_poly_zscore_blsubdist) %>%
  format_group_combined() %>%
  group_by(subject, group_combined, region, solution, stim_id, time_rel) %>%
  summarise(
    delta_signal_poly_zscore = delta_signal_poly_zscore %>% mean(),
    delta_signal_poly_zscore_blsub = delta_signal_poly_zscore_blsub %>% mean(),
    delta_signal_poly_zscore_blsubdist = delta_signal_poly_zscore_blsubdist %>% mean(),
    delta_control_poly_zscore_blsub = delta_control_poly_zscore_blsub %>% mean(), 
    delta_control_poly_zscore_blsubdist = delta_control_poly_zscore_blsubdist %>% mean()
    ) 

df_summary <- df %>%
  group_by(group_combined, region, solution, stim_id, time_rel) %>%
  summarise(
    delta_signal_poly_zscore_sem = sd(delta_signal_poly_zscore) / sqrt(n()),
    delta_signal_poly_zscore = delta_signal_poly_zscore %>% mean(),
    delta_signal_poly_zscore_blsub_sem = sd(delta_signal_poly_zscore_blsub) / sqrt(n()),
    delta_signal_poly_zscore_blsub = delta_signal_poly_zscore_blsub %>% mean(),
    delta_signal_poly_zscore_blsubdist_sem = sd(delta_signal_poly_zscore_blsubdist) / sqrt(n()),
    delta_signal_poly_zscore_blsubdist = delta_signal_poly_zscore_blsubdist %>% mean()
    ) 
  

df_diff <- df %>%
  filter(time_rel > -3, time_rel < 6) %>%
  select(subject, group_combined, region, solution, time_rel, delta_signal_poly_zscore_blsubdist) %>%
  spread(stim_id, delta_signal_poly_zscore_blsubdist) %>%
  mutate(diff = lha - no_stim) 

df_diff_summary <- df_diff %>%
  group_by(group_combined, region, solution, time_rel) %>%
  summarise(diff_sem = sd(diff) / sqrt(n()),
            diff = diff %>% mean()) 


df_diff_summary_solution <- df_diff %>%
  filter(time_rel > 0, time_rel < 3) %>%
  group_by(subject, group_combined, region, solution) %>%
  summarise(diff = mean(diff),.groups = 'drop')



## binned based on licking data
df_licking_binned <- streams_peth_solution %>%
  format_group_combined() %>%
  filter(lick_count > 0) %>% # filter to trails with licking (beware reduction in trials w/ vgat inhibition)
  mutate(lick_count_bin = cut(lick_count, seq(0,20,5))) %>% # bin based on licking
  filter(!is.na(lick_count_bin)) %>%
  group_by(subject, group_combined, lick_count_bin, region, solution, stim_id, time_rel) %>%
  summarise(delta_signal_poly_zscore_blsub = delta_signal_poly_zscore_blsub %>% mean(),
            delta_signal_poly_zscore_blsubdist = delta_signal_poly_zscore_blsubdist %>% mean()) 

df_licking_binned_summary <- df_licking_binned %>%
  group_by(group_combined, lick_count_bin, region, solution, stim_id, time_rel) %>%
  summarise(delta_signal_poly_zscore_blsub_sem = sd(delta_signal_poly_zscore_blsub) / sqrt(n()),
            delta_signal_poly_zscore_blsub = delta_signal_poly_zscore_blsub %>% mean(),
            delta_signal_poly_zscore_blsubdist = delta_signal_poly_zscore_blsubdist %>% mean()) 


df_licking_binned_diff <- df_licking_binned %>%
  filter(time_rel > -3, time_rel < 6) %>%
  select(-delta_signal_poly_zscore_blsubdist) %>%
  spread(stim_id, delta_signal_poly_zscore_blsub) %>%
  mutate(diff = lha - no_stim) 

df_licking_binned_diff_summary <- df_licking_binned_diff %>%
  filter(time_rel > 0, time_rel < 3) %>%
  group_by(subject, group_combined, lick_count_bin, region, solution) %>%
  summarise(diff = mean(diff),.groups = 'drop')
```



```{r, fig.width = 12, fig.height = 5}
df_plt_sbj <- streams_peth_solution %>%
  filter(region == 'DLS') %>%
  filter(subject == 'acd09') %>%
  format_group_combined() %>%
  filter(group_combined == 'control') %>%
  group_by(subject, group_combined, region, stim_id, time_rel) %>%
  summarise(
    delta_signal_poly_zscore = mean(delta_signal_poly_zscore),
    delta_signal_poly_zscore_blsubdist = mean(delta_signal_poly_zscore_blsubdist),
    delta_signal_poly_zscore_blsub = mean(delta_signal_poly_zscore_blsub)
  )


### ___________________________________________________________
fn_stem <- 'preprocessing_examplesubject_nobaseline'

plt01 <- df_plt_sbj %>%
  filter(time_rel > -9, time_rel < 12) %>%
  ggplot(aes(time_rel, delta_signal_poly_zscore, color = stim_id)) +
  annotate("rect", xmin = -6, xmax = 9, ymin = -Inf, ymax = Inf, alpha = 1/8, fill = "#2baee4") +
  annotate("rect", xmin = 0, xmax = 3, ymin = -Inf, ymax = Inf, alpha = 1/3, fill = "darkgrey") +
  geom_line() +
  facet_grid(group_combined~subject) +
  ylab('Z-score') +
  xlab('Time relative to access start (s)') +
  ggtitle('No baseline subtraction') +
  theme_ag01() +
  scale_color_manual(values = c('#2baee4', 'black')) +
  force_panelsizes(rows = unit(2.5, 'cm'), cols = unit(2.5,'cm'))


plt01 %>%
  add_scale_bar(
    origin = c(-9, -0.5), 
    x_len = 1, 
    y_len = 1
  )

save_pdf(dir_output, str_c(fn_stem, '.pdf'), 4,4)

df_plt_sbj %>%
  select(subject, group_combined, region, stim_id, time_rel, delta_signal_poly_zscore) %>%
  write_csv(str_c(dir_output, fn_stem, '_data.csv'))
  

### ___________________________________________________________
fn_stem <- 'preprocessing_examplesubject_prelaser'

plt02 <- df_plt_sbj %>%
  filter(time_rel > -9, time_rel < 12) %>%
  ggplot(aes(time_rel, delta_signal_poly_zscore_blsubdist, color = stim_id)) +
  annotate("rect", xmin = -6, xmax = 9, ymin = -Inf, ymax = Inf, alpha = 1/8, fill = "#2baee4") +
  annotate("rect", xmin = 0, xmax = 3, ymin = -Inf, ymax = Inf, alpha = 1/3, fill = "darkgrey") +
  geom_line() +
  facet_grid(group_combined~subject) +
  ylab('Z-score') +
  xlab('Time relative to access start (s)') +
  ggtitle('Pre-laser baseline subtraction') +
  theme_ag01() +
  scale_color_manual(values = c('#2baee4', 'black')) +
  force_panelsizes(rows = unit(2.5, 'cm'), cols = unit(2.5,'cm'))



plt02 %>%
  add_scale_bar(
    origin = c(-9, -0.5), 
    x_len = 1, 
    y_len = 1
  )


save_pdf(dir_output, str_c(fn_stem, '.pdf'), 4,4)

df_plt_sbj %>%
  select(subject, group_combined, region, stim_id, time_rel, delta_signal_poly_zscore_blsubdist) %>%
  write_csv(str_c(dir_output, fn_stem, '_data.csv'))

### ___________________________________________________________
fn_stem <- 'preprocessing_examplesubject_preaccess'

plt03 <- df_plt_sbj %>%
  filter(time_rel > -9, time_rel < 12) %>%
  ggplot(aes(time_rel, delta_signal_poly_zscore_blsub, color = stim_id)) +
  annotate("rect", xmin = -6, xmax = 9, ymin = -Inf, ymax = Inf, alpha = 1/8, fill = "#2baee4") +
  annotate("rect", xmin = 0, xmax = 3, ymin = -Inf, ymax = Inf, alpha = 1/3, fill = "darkgrey") +
  geom_line() +
  facet_grid(group_combined~subject) +
  ylab('Z-score') +
  xlab('Time relative to access start (s)') +
  ggtitle('Pre-laser baseline subtraction') +
  theme_ag01() +
  scale_color_manual(values = c('#2baee4', 'black')) +
  force_panelsizes(rows = unit(2.5, 'cm'), cols = unit(2.5,'cm'))



plt03 %>%
  add_scale_bar(
    origin = c(-9, -0.5), 
    x_len = 1, 
    y_len = 1
  )


save_pdf(dir_output, str_c(fn_stem, '.pdf'), 4,4)

df_plt_sbj %>%
  select(subject, group_combined, region, stim_id, time_rel, delta_signal_poly_zscore_blsub) %>%
  write_csv(str_c(dir_output, fn_stem, '_data.csv'))

```

```{r}
#breakplease
```


```{r, fig.width = 12, fig.height = 5}
df_plt <- streams_peth_solution %>%
  format_group_combined() %>%
  group_by(group_combined, region, stim_id, time_rel) %>%
  summarise(
    delta_signal_poly_zscore = mean(delta_signal_poly_zscore),
    delta_signal_poly_zscore_blsubdist = mean(delta_signal_poly_zscore_blsubdist),
    delta_signal_poly_zscore_blsub = mean(delta_signal_poly_zscore_blsub)
  ) 

### ___________________________________________________________
fn_stem <- 'preprocessing_group_nobaseline'

plt01 <- df_plt %>%
  filter(time_rel > -9, time_rel < 12) %>%
  ggplot(aes(time_rel, delta_signal_poly_zscore, color = stim_id)) +
  annotate("rect", xmin = -6, xmax = 9, ymin = -Inf, ymax = Inf, alpha = 1/8, fill = "#2baee4") +
  annotate("rect", xmin = 0, xmax = 3, ymin = -Inf, ymax = Inf, alpha = 1/3, fill = "darkgrey") +
  geom_line() +
  facet_grid(group_combined~region) +
  ylab('Z-score') +
  xlab('Time relative to access start (s)') +
  ggtitle('No baseline subtraction') +
  theme_ag01() +
  scale_color_manual(values = c('#2baee4', 'black')) +
  force_panelsizes(rows = unit(2.5, 'cm'), cols = unit(2.5,'cm'))

plt01 %>%
  add_scale_bar(
    origin = c(-9, -0.5), 
    x_len = 1, 
    y_len = 1
  )


save_pdf(dir_output, str_c(fn_stem, '.pdf'), 8,4)

df_plt %>%
  select(group_combined, region, stim_id, time_rel, delta_signal_poly_zscore) %>%
  write_csv(str_c(dir_output, fn_stem, '_data.csv'))

### ___________________________________________________________
fn_stem <- 'preprocessing_group_prelaser'

plt02 <- df_plt %>%
  filter(time_rel > -9, time_rel < 12) %>%
  ggplot(aes(time_rel, delta_signal_poly_zscore_blsubdist, color = stim_id)) +
  annotate("rect", xmin = -6, xmax = 9, ymin = -Inf, ymax = Inf, alpha = 1/8, fill = "#2baee4") +
  annotate("rect", xmin = 0, xmax = 3, ymin = -Inf, ymax = Inf, alpha = 1/3, fill = "darkgrey") +
  geom_line() +
  facet_grid(group_combined~region) +
  ylab('Z-score') +
  xlab('Time relative to access start (s)') +
  ggtitle('Pre-laser baseline subtraction') +
  theme_ag01() +
  scale_color_manual(values = c('#2baee4', 'black')) +
  force_panelsizes(rows = unit(2.5, 'cm'), cols = unit(2.5,'cm'))

plt02 %>%
  add_scale_bar(
    origin = c(-9, -0.5), 
    x_len = 1, 
    y_len = 1
  )

save_pdf(dir_output, str_c(fn_stem, '.pdf'), 8,4)

df_plt %>%
  select(group_combined, region, stim_id, time_rel, delta_signal_poly_zscore_blsubdist) %>%
  write_csv(str_c(dir_output, fn_stem, '_data.csv'))

### ___________________________________________________________
fn_stem <- 'preprocessing_group_preaccess'

plt03 <- df_plt %>%
  filter(time_rel > -9, time_rel < 12) %>%
  ggplot(aes(time_rel, delta_signal_poly_zscore_blsub, color = stim_id)) +
  annotate("rect", xmin = -6, xmax = 9, ymin = -Inf, ymax = Inf, alpha = 1/8, fill = "#2baee4") +
  annotate("rect", xmin = 0, xmax = 3, ymin = -Inf, ymax = Inf, alpha = 1/3, fill = "darkgrey") +
  geom_line() +
  facet_grid(group_combined~region) +
  ylab('Z-score') +
  xlab('Time relative to access start (s)') +
  ggtitle('Pre-access baseline subtraction') +
  theme_ag01() +
  scale_color_manual(values = c('#2baee4', 'black')) +
  force_panelsizes(rows = unit(2.5, 'cm'), cols = unit(2.5,'cm'))

plt03 %>%
  add_scale_bar(
    origin = c(-9, -0.5), 
    x_len = 1, 
    y_len = 1
  )

save_pdf(dir_output, str_c(fn_stem, '.pdf'), 8,4)

df_plt %>%
  select(group_combined, region, stim_id, time_rel, delta_signal_poly_zscore_blsub) %>%
  write_csv(str_c(dir_output, fn_stem, '_data.csv'))
```


## final: inhibtion baseline effect
```{r, fig.width = 9, fig.height = 3}
fn_stem <- 'inh_baseline_prelaserbl_trace'


plt_data <-   df %>%
  filter(time_rel >= -9, time_rel <= 0) %>%
  select(group_combined, subject, region, solution, stim_id, time_rel, 
         zscore  = delta_signal_poly_zscore_blsubdist           # speify variables to plot here 
         ) 

plt_data <- plt_data %>%
  spread(stim_id, zscore) %>%
  mutate(diff = lha - no_stim) %>%
  group_by(group_combined, region, solution, time_rel) %>%
  summarise(
    diff_sem = sd(diff) / sqrt(n()),
    diff = mean(diff)
  )


plt <- plt_data %>%
  ggplot(aes(time_rel, diff, color = region, fill = region)) +
  annotate("rect", xmin = -6, xmax = 0, ymin = -Inf, ymax = Inf, alpha = 1/8, fill = "#2baee4") +
  geom_hline(yintercept = 0, color = 'darkgrey', size = 0.5) +
  geom_ribbon(aes(ymax = diff + diff_sem, 
                  ymin = diff - diff_sem, 
                  fill = region),
              color = NA,
              alpha = 1/3) +
  geom_line() +
  
  facet_grid(solution~group_combined) +
  theme_ag01() +
  scale_color_viridis_d(end = 0.8, option = 'magma') +
  scale_fill_viridis_d(end = 0.8, option = 'magma') 

plt <- plt %>%
  add_scale_bar(
    origin = c(-9, -1), 
    x_len = 1, 
    y_len = 1
  )

plt +
  force_panelsizes(cols = unit(4.3553,'cm'), rows = unit(2.5955 , 'cm'))

save_pdf(dir_output, str_c(fn_stem, '.pdf'), 8, 4)
write_csv(plt_data, str_c(fn_stem, '_data.csv'))

```

```{r}
fn_stem <- 'inh_baseline_region_vs_difference'


plt_data_summary <- df %>%
  filter(time_rel > -5, time_rel < 0) %>%
  group_by(subject, region, stim_id, group_combined) %>%
  summarise(zscore = delta_signal_poly_zscore_blsubdist %>% mean())  

plt_data_summary_delta <- plt_data_summary %>%
  spread(stim_id, zscore) %>%
  mutate(diff = lha - no_stim) 


plt_data_summary_delta %>%
  ggplot(aes(region, diff, color = group_combined, fill = group_combined)) +
  geom_hline(yintercept = 0, alpha = 1/3) +
  stat_summary(
    fun.data = 'mean_se', 
    geom = 'errorbar', 
    aes(group = group_combined),
    width = 0.3,
    position = position_dodge(width = 0.75)) +
  stat_summary(
    fun = 'mean',
    geom = 'bar',
    color = NA,
    aes(group = group_combined),
    alpha = 1/2,
    width = 0.6,
    position = position_dodge(width = 0.75)) +
  geom_jitter(shape = 21, color = 'white', size = 1.5, stroke = 0.25,
              position = position_jitterdodge(jitter.width = 0.04, dodge.width = 0.75)) +
  theme_ag01() +
  theme(axis.text.x = element_text(angle = 90, hjust = 1, vjust = 0.3)) +
  scale_color_manual(values = color_group_combined) +
  scale_fill_manual(values = color_group_combined) +
  coord_cartesian(xlim = c(0.5, 6.5), ylim = c(-2,1.5), expand = F) +
  scale_y_continuous(breaks = seq(-2,1.5,0.5)) +
  force_panelsizes(cols = unit(plt_dims[1]*1.25,'cm'), rows = unit(4.1758 , 'cm')) +
  ylab('Z-Score difference') +
  xlab('')

save_pdf(dir_output, str_c(fn_stem, '.pdf'), 4,4)

loop_regions <- plt_data_summary_delta %>% pull(region) %>% unique() 


for(loop_region in loop_regions){
  
  plt_data_wide <- plt_data_summary_delta %>%
    select(region, subject, group_combined, diff) %>%
    spread(group_combined, diff) %>%
    filter(region == loop_region) 
  
  loop_result <- bind_rows(
    plt_data_wide %>%
      tidy_wilcox_unpaired('control','vgat_inh') %>%
      mutate(comparision = 'control_vs_vgat'),
    
    plt_data_wide %>%
      tidy_wilcox_unpaired('control','vglut2_inh') %>%
      mutate(comparision = 'control_vs_vglut2')
  ) %>%
    clean_names() %>%
    mutate(region = loop_region) %>%
    select(region, comparision, everything()) %>%
    mutate(p_value = p_value * 2) %>%
    quick_sig()
  
  if(loop_region == loop_regions[1]){
    combined_result <- loop_result
  } else {
    combined_result <- loop_result %>%
      bind_rows(combined_result,.)
    }
}

combined_result %>%
  mutate(region = region %>% factor(levels = key_regions$region_label)) %>%
  ggplot(aes(region, comparision, label = sig_symbol)) +
  geom_text()

save_pdf(dir_output, str_c(fn_stem, '_ph.pdf'), 6,2)

plt_data_summary_delta %>%  write_csv(str_c(dir_output, fn_stem, '_data.csv'))
combined_result %>%  write_csv(str_c(dir_output, fn_stem, '_stats_ph.csv'))

```
mixture of mice are outliners within the vgat_inh group
- acd13 (vgat_inh) is high on NAcCC
- acd17 (vgat_inh) is high on NAcCC



## final: consumption effect - distant baseline
#### trace
```{r, fig.width = 9, fig.height = 3}
fn_stem <- 'inh_access_prelaserbl_trace'


plt_data <-   df %>%
  filter(time_rel >= -9, time_rel <= 12) %>%
  select(group_combined, subject, region, solution, stim_id, time_rel, 
         zscore  = delta_signal_poly_zscore_blsubdist           # speify variables to plot here 
         ) 

plt_data <- plt_data %>%
  spread(stim_id, zscore) %>%
  mutate(diff = lha - no_stim) %>%
  group_by(group_combined, region, solution, time_rel) %>%
  summarise(
    diff_sem = sd(diff) / sqrt(n()),
    diff = mean(diff)
  )


plt <- plt_data %>%
  ggplot(aes(time_rel, diff, color = region, fill = region)) +
  annotate("rect", xmin = -6, xmax = 9, ymin = -Inf, ymax = Inf, alpha = 1/8, fill = "#2baee4") +
  annotate("rect", xmin = 0, xmax = 3, ymin = -Inf, ymax = Inf, alpha = 1/3, fill = "darkgrey") +
  geom_hline(yintercept = 0, color = 'darkgrey', size = 0.5) +
  geom_ribbon(aes(ymax = diff + diff_sem, 
                  ymin = diff - diff_sem, 
                  fill = region),
              color = NA,
              alpha = 1/3) +
  geom_line() +
  
  facet_grid(solution~group_combined) +
  theme_ag01() +
  scale_color_viridis_d(end = 0.8, option = 'magma') +
  scale_fill_viridis_d(end = 0.8, option = 'magma') 

plt <- plt %>%
  add_scale_bar(
    origin = c(-9, -1), 
    x_len = 1, 
    y_len = 1
  )

plt +
  force_panelsizes(cols = unit(4.3,'cm'), rows = unit(2.5955, 'cm'))

save_pdf(dir_output, str_c(fn_stem, '.pdf'), 8, 4)
write_csv(plt_data, str_c(fn_stem, '_data.csv'))

```

#### summary
```{r}
fn_stem <- 'inh_access_prelaserbl_region_vs_difference'

plt_data_summary <- df %>%
  filter(time_rel > 0, time_rel < 2) %>%
  group_by(subject, region, stim_id, group_combined, solution) %>%
  summarise(zscore = delta_signal_poly_zscore_blsubdist %>% mean()) 

plt_data_summary_delta <- plt_data_summary %>%
  spread(stim_id, zscore) %>%
  mutate(diff = lha - no_stim) 


plt_data_summary_delta %>%
  ggplot(aes(region, diff, color = group_combined, fill = group_combined)) +
  geom_hline(yintercept = 0, alpha = 1/3) +
  stat_summary(
    fun.data = 'mean_se', 
    geom = 'errorbar', 
    aes(group = group_combined),
    width = 0.3,
    position = position_dodge(width = 0.75)) +
  stat_summary(
    fun = 'mean',
    geom = 'bar',
    color = NA,
    aes(group = group_combined),
    alpha = 1/2,
    width = 0.6,
    position = position_dodge(width = 0.75)) +
  geom_jitter(shape = 21, color = 'white', size = 1.5, stroke = 0.25,
              position = position_jitterdodge(jitter.width = 0.04, dodge.width = 0.75)) +
  theme_ag01() +
  theme(axis.text.x = element_text(angle = 90, hjust = 1, vjust = 0.3)) +
  scale_color_manual(values = color_group_combined) +
  scale_fill_manual(values = color_group_combined) +
  coord_cartesian(xlim = c(0.5, 6.5), ylim = c(-2,2), expand = F) +
  facet_grid(solution~.) +
  force_panelsizes(cols = unit(plt_dims[1]*1.25,'cm'), rows = unit(plt_dims[2]*2/3, 'cm')) +
  theme(panel.spacing.y = unit(0.8, 'lines')) +
  ylab('Z-Score difference') +
  xlab('') 

save_pdf(dir_output, str_c(fn_stem, '.pdf'), 8,4)

loop_regions <- plt_data_summary_delta %>% pull(region) %>% unique() 
loop_solutions <- plt_data_summary_delta %>% pull(solution) %>% unique() 

for(loop_solution in loop_solutions){
  for(loop_region in loop_regions){
    
    plt_data_wide <- plt_data_summary_delta %>%
      filter(solution == loop_solution) %>%
      select(region, subject, group_combined, diff) %>%
      spread(group_combined, diff) %>%
      filter(region == loop_region) 
    
    loop_result <- bind_rows(
      plt_data_wide %>%
        tidy_wilcox_unpaired('control','vgat_inh') %>%
        mutate(comparision = 'control_vs_vgat'),
      
      plt_data_wide %>%
        tidy_wilcox_unpaired('control','vglut2_inh') %>%
        mutate(comparision = 'control_vs_vglut2')
    ) %>%
      clean_names() %>%
      mutate(region = loop_region) %>%
      mutate(solution = loop_solution) %>%
      select(solution, region, comparision, everything()) %>%
      mutate(p_value = p_value * 2) %>%
      quick_sig()
    
    if(loop_region == loop_regions[1] & loop_solution == loop_solutions[1]){
      combined_result <- loop_result
    } else {
      combined_result <- loop_result %>%
        bind_rows(combined_result,.)
      }
  }
}

combined_result %>%
  mutate(region = region %>% factor(levels = key_regions$region_label)) %>%
  ggplot(aes(region, comparision, label = sig_symbol)) +
  facet_grid(solution~.) +
  geom_text()

save_pdf(dir_output, str_c(fn_stem, '_ph.pdf'), 6,4)

plt_data_summary_delta %>%  write_csv(str_c(dir_output, fn_stem, '_data.csv'))
combined_result %>%  write_csv(str_c(dir_output, fn_stem, '_stats_ph.csv'))
```

```{r}
plt_data_summary_delta %>%
  select(group_combined, region, subject) %>%
  unique() %>%
  group_by(group_combined, region) %>%
  summarise(count = n()) %>%
  spread(group_combined, count)
  
```


#### placements
```{r}

plt_data_summary_delta_mean <- plt_data_summary_delta %>%
  group_by(group_combined, subject, region) %>%
  summarise(diff = mean(diff)) 

plt_data_summary_delta_mean <- plt_data_summary_delta_mean %>%
  left_join(log_placements %>% select(subject, region = target, hit_ap, hit_ml, hit_dv)) 
```



```{r}

fn_stem <- 'inh_access_prelaserbl_placement_vs_deltasummary'

for(loop_group in c('control', 'vgat_inh', 'vglut2_inh')){
  
  df_loop <- plt_data_summary_delta_mean %>%
    filter(group_combined == loop_group)
  
  var_color <- 'diff'
  color_limits <- c(-1,1)
  
  plt_str(
    df = df_loop, 
    var_color = !!sym(var_color),
    var_color_name = 'Delta',
    vars_facet = c('.','.'),
    plt_plane = 'sagittal',
    plt_dim_base = 3,
    color_limits = color_limits
    )
  
  save_pdf(str_c(dir_output, 'placements/'), str_c(fn_stem,'_', loop_group, '_sagittal.pdf'),6,6)
  
  plt_str(
    df = df_loop,
    var_color = !!sym(var_color),
    var_color_name = 'z-score',
    vars_facet = c('.','.'),
    plt_plane = 'horizontal',
    plt_dim_base = 3,
    color_limits = color_limits
    ) 
  
  save_pdf(str_c(dir_output, 'placements/'), str_c(fn_stem,'_', loop_group, '_horizontal.pdf'),6,6)
  
  plt_str(
    df = df_loop,
    var_color = !!sym(var_color),
    var_color_name = 'z-score',
    vars_facet = c('.','.'),
    plt_plane = 'coronal',
    plt_dim_base = 3,
    color_limits = color_limits
    )
  
  save_pdf(str_c(dir_output, 'placements/'), str_c(fn_stem,'_', loop_group, '_coronal.pdf'),6,6)
  
  plt_str_3d(
    df = df_loop, 
    var_color = var_color, 
    color_limits = color_limits,
    dir_output = str_c(dir_output, 'placements/'),
    fn_stem = str_c(fn_stem,'_', loop_group),
    toggle_save = 1
    )

}
```


```{r, fig.height = 6, fig.width = 9}
plt_list <- plt_corr(
  df = plt_data_summary_delta_mean, 
  ylim_all = c(-2,2), 
  xlim_ap = c(-3, 0, 3),
  xlim_ml = c(0, 2, 4),
  xlim_dv = c(-6, -4, -2),
  var_dep = 'diff', 
  var_dep_label = 'Delta', 
  plt_dims = c(3, 3*2/3)
)




# run pearsons
plt_list[['AP']] + 
  plt_list[['ML']] + 
  plt_list[['DV']] +
  plot_layout(nrow = 1, widths = unit(3*2/3, 'cm'), heights = unit(4, 'cm'), guides = 'collect')
  
save_pdf(str_c(dir_output, 'placements/'), str_c(fn_stem, '_corr.pdf'),6,3.5)

plt_list[['stats_output']] %>%
  write_csv(str_c(dir_output, 'placements/',  fn_stem, '_corr.csv'))


```



## final: consumption effect - proximal baseline
#### trace
```{r, fig.width = 9, fig.height = 3}
fn_stem <- 'inh_access_preaccessbl_trace'


plt_data <-   df %>%
  filter(time_rel >= -3, time_rel <= 6) %>%
  select(group_combined, subject, region, solution, stim_id, time_rel, 
         zscore  = delta_signal_poly_zscore_blsub           # speify variables to plot here 
         ) 

plt_data <- plt_data %>%
  spread(stim_id, zscore) %>%
  mutate(diff = lha - no_stim) %>%
  group_by(group_combined, region, solution, time_rel) %>%
  summarise(
    diff_sem = sd(diff) / sqrt(n()),
    diff = mean(diff)
  )


plt <- plt_data %>%
  ggplot(aes(time_rel, diff, color = region, fill = region)) +
  annotate("rect", xmin = -3, xmax = 6, ymin = -Inf, ymax = Inf, alpha = 1/8, fill = "#2baee4") +
  annotate("rect", xmin = 0, xmax = 3, ymin = -Inf, ymax = Inf, alpha = 1/3, fill = "darkgrey") +
  geom_hline(yintercept = 0, color = 'darkgrey', size = 0.5) +
  geom_ribbon(aes(ymax = diff + diff_sem, 
                  ymin = diff - diff_sem, 
                  fill = region),
              color = NA,
              alpha = 1/3) +
  geom_line() +
  
  facet_grid(solution~group_combined) +
  theme_ag01() +
  scale_color_viridis_d(end = 0.8, option = 'magma') +
  scale_fill_viridis_d(end = 0.8, option = 'magma') 

plt <- plt %>%
  add_scale_bar(
    origin = c(-3, -1), 
    x_len = 1, 
    y_len = 1
  )

plt +
  force_panelsizes(cols = unit(4.3553,'cm'), rows = unit(2.5955 , 'cm'))

save_pdf(dir_output, str_c(fn_stem, '.pdf'), 8, 4)
write_csv(plt_data, str_c(fn_stem, '_data.csv'))

```

#### summary
```{r}
fn_stem <- 'inh_access_preaccessbl_region_vs_difference'

plt_data_summary <- df %>%
  filter(time_rel > 0, time_rel < 2) %>%
  group_by(subject, region, stim_id, group_combined, solution) %>%
  summarise(zscore = delta_signal_poly_zscore_blsub %>% mean()) 


plt_data_summary_delta <- plt_data_summary %>%
  spread(stim_id, zscore) %>%
  mutate(diff = lha - no_stim) 


plt <- plt_data_summary_delta %>%
  ggplot(aes(region, diff, color = group_combined, fill = group_combined)) +
  geom_hline(yintercept = 0, alpha = 1/3) +
  stat_summary(
    fun.data = 'mean_se', 
    geom = 'errorbar', 
    aes(group = group_combined),
    width = 0.3,
    position = position_dodge(width = 0.75)) +
  stat_summary(
    fun = 'mean',
    geom = 'bar',
    color = NA,
    aes(group = group_combined),
    alpha = 1/2,
    width = 0.6,
    position = position_dodge(width = 0.75)) +
  theme_ag01() +
  theme(axis.text.x = element_text(angle = 90, hjust = 1, vjust = 0.3)) +
  scale_color_manual(values = color_group_combined) +
  scale_fill_manual(values = color_group_combined) +
  facet_grid(solution~.) +
  force_panelsizes(cols = unit(plt_dims[1]*1.25,'cm'), rows = unit(plt_dims[2]*2/3, 'cm')) +
  theme(panel.spacing.y = unit(0.8, 'lines')) +
  ylab('Z-Score difference') +
  xlab('') 

plt + 
  geom_jitter(shape = 21, color = 'white', size = 1.5, stroke = 0.25,
              position = position_jitterdodge(jitter.width = 0.04, dodge.width = 0.75)) +
  coord_cartesian(xlim = c(0.5, 6.5), ylim = c(-1.5,1), expand = F) 

save_pdf(dir_output, str_c(fn_stem, '.pdf'), 4,4)
  

loop_regions <- plt_data_summary_delta %>% pull(region) %>% unique() 
loop_solutions <- plt_data_summary_delta %>% pull(solution) %>% unique() 

for(loop_solution in loop_solutions){
  for(loop_region in loop_regions){
    
    plt_data_wide <- plt_data_summary_delta %>%
      filter(solution == loop_solution) %>%
      select(region, subject, group_combined, diff) %>%
      spread(group_combined, diff) %>%
      filter(region == loop_region) 
    
    loop_result <- bind_rows(
      plt_data_wide %>%
        tidy_wilcox_unpaired('control','vgat_inh') %>%
        mutate(comparision = 'control_vs_vgat'),
      
      plt_data_wide %>%
        tidy_wilcox_unpaired('control','vglut2_inh') %>%
        mutate(comparision = 'control_vs_vglut2')
    ) %>%
      clean_names() %>%
      mutate(region = loop_region) %>%
      mutate(solution = loop_solution) %>%
      select(solution, region, comparision, everything()) %>%
      mutate(p_value = p_value * 2) %>%
      quick_sig()
    
    if(loop_region == loop_regions[1] & loop_solution == loop_solutions[1]){
      combined_result <- loop_result
    } else {
      combined_result <- loop_result %>%
        bind_rows(combined_result,.)
      }
  }
}

combined_result %>%
  mutate(region = region %>% factor(levels = key_regions$region_label)) %>%
  ggplot(aes(region, comparision, label = sig_symbol)) +
  facet_grid(.~solution) +
  geom_text()

save_pdf(dir_output, str_c(fn_stem, '_ph.pdf'), 4,4)

plt_data_summary_delta %>%  write_csv(str_c(dir_output, fn_stem, '_data.csv'))
combined_result %>%  write_csv(str_c(dir_output, fn_stem, '_stats_ph.csv'))
```

#### placements
```{r}

plt_data_summary_delta_mean <- plt_data_summary_delta %>%
  group_by(group_combined, subject, region) %>%
  summarise(diff = mean(diff)) 

plt_data_summary_delta_mean <- plt_data_summary_delta_mean %>%
  left_join(log_placements %>% select(subject, region = target, hit_ap, hit_ml, hit_dv)) 
```



```{r}


fn_stem <- 'inh_access_preaccessbl_placement_vs_deltasummary'

for(loop_group in c('control', 'vgat_inh', 'vglut2_inh')){
  
  df_loop <- plt_data_summary_delta_mean %>%
    filter(group_combined == loop_group)
  
  var_color <- 'diff'
  color_limits <- c(-0.5,0.5)
  
  plt_str(
    df = df_loop, 
    var_color = !!sym(var_color),
    var_color_name = 'Delta',
    vars_facet = c('.','.'),
    plt_plane = 'sagittal',
    plt_dim_base = 3,
    color_limits = color_limits
    )
  
  save_pdf(str_c(dir_output, 'placements/'), str_c(fn_stem,'_', loop_group, '_sagittal.pdf'),6,6)
  
  plt_str(
    df = df_loop,
    var_color = !!sym(var_color),
    var_color_name = 'z-score',
    vars_facet = c('.','.'),
    plt_plane = 'horizontal',
    plt_dim_base = 3,
    color_limits = color_limits
    ) 
  
  save_pdf(str_c(dir_output, 'placements/'), str_c(fn_stem,'_', loop_group, '_horizontal.pdf'),6,6)
  
  plt_str(
    df = df_loop,
    var_color = !!sym(var_color),
    var_color_name = 'z-score',
    vars_facet = c('.','.'),
    plt_plane = 'coronal',
    plt_dim_base = 3,
    color_limits = color_limits
    )
  
  save_pdf(str_c(dir_output, 'placements/'), str_c(fn_stem,'_', loop_group, '_coronal.pdf'),6,6)
  
  plt_str_3d(
    df = df_loop, 
    var_color = var_color, 
    color_limits = color_limits,
    dir_output = str_c(dir_output, 'placements/'),
    fn_stem = str_c(fn_stem,'_', loop_group),
    toggle_save = 1
    )

}
```


```{r, fig.height = 6, fig.width = 9}
plt_list <- plt_corr(
  df = plt_data_summary_delta_mean, 
  ylim_all = c(-1.5,1), 
  xlim_ap = c(-3, 0, 3),
  xlim_ml = c(0, 2, 4),
  xlim_dv = c(-6, -4, -2),
  var_dep = 'diff', 
  var_dep_label = 'Delta', 
  plt_dims = c(3, 3*2/3)
)




# run pearsons
plt_list[['AP']] + 
  plt_list[['ML']] + 
  plt_list[['DV']] +
  plot_layout(nrow = 1, widths = unit(3*2/3, 'cm'), heights = unit(4, 'cm'), guides = 'collect')
  
save_pdf(str_c(dir_output, 'placements/'), str_c(fn_stem, '_corr.pdf'),6,6)

plt_list[['stats_output']] %>%
  write_csv(str_c(dir_output, 'placements/',  fn_stem, '_corr.csv'))


```








