---
title: "compiler"
author: "adam gordon-fennell"
date: '2023-12-28'
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# setup
## libraries
```{r}
library(tidyverse)
library(afex)
library(emmeans)
library(janitor)
library(readxl)
library(googlesheets4)
library(ggh4x) # force_panelsizes
library(arrow)
library(zoo)
library(lubridate)
library(patchwork)
library(ggbeeswarm)
library(ggpubr) #r2 on correlation
library(pals)
library(boot) #bootstrapping
library(corrplot)
library(Hmisc)
library(plotly)

arrow::set_cpu_count(4)

source('./functions/r_head_fixed_processing.R')
source('./functions/r_general.R')
source('./functions/r_plots.R')
source('./functions/r_stats.R')
source('./functions/general.R')
source('./functions/pca.R')
source('./functions/plotting_placements.R')
source('./functions/analysis_peth.R')

writeLines(capture.output(sessionInfo()), "./analysis_output/session_info_r.txt")

library(viridisLite)

color_values_nacl <- inferno(5, begin = 0, end = 0.8)
color_values_suc <- mako(5, begin = 0, end = 0.8)
color_values_misc01 <-  c('black', 'grey', '#BCD634', '#34BCD6')
color_values_misc02 <-  c('black', '#D634BC', '#BCD634', '#34BCD6')
color_values_groupcombined <- c('darkgrey', '#CC2029', '#70BF46')
color_values_regions <- c('#72BF45', '#CD202A', '#7B8137', '#000004FF', '#2A115CFF', '#6C1D81FF', '#AD347CFF', '#EA5661FF', '#FE9F6DFF')
color_values_regions_da <- c('#000004FF', '#2A115CFF', '#6C1D81FF', '#AD347CFF', '#EA5661FF', '#FE9F6DFF')
color_values_regions_da7 <- c("#000004FF", "#20114BFF", "#57157EFF", "#8C2981FF", "#C43C75FF", "#F1605DFF", "#FE9F6DFF")
color_values_experiment_set <- c('#7edb00', '#007edb', '#db007e')
```



## directories
```{r}
dir_output <- './data/combined_setid/'

dir_localdata_sessions <- './data/sessions/' #end with "/"
dir_sessions_combined_subject <- './data/sessions_combined_subject/'
```


## logs / keys
```{r}
log_analysis_subjects <- read_xlsx('./log_data_analysis.xlsx', sheet = 'subjects',    na = c('NA', ''))
log_subjects <- read_xlsx('log_data_analysis.xlsx', sheet = 'subjects') 
log_analysis_fp <- read_xlsx('./log_data_analysis.xlsx', sheet = 'fp',          na = c('NA', ''))
log_analysis_exp <- read_xlsx('./log_data_analysis.xlsx', sheet = 'experiments', na = c('NA', ''))
log_npm <- read_sheet('https://docs.google.com/spreadsheets/d/1v-G8GHYPGtJWXARZYqcndO03d23umsTo98BAb5_WnrY/edit#gid=0', na = c('', 'NA'))
log_placements <- read_sheet('https://docs.google.com/spreadsheets/d/1dATNdE46yfeKJmNBi51yeO8Iycv4RaMlfdc8xS4YBiY', sheet = 'placements', na = c('na','NA',''))
```


```{r}
join_info <- log_analysis_fp %>% 
  get_set_id() %>% 
  select(blockname, experiment, subject, set_id)
```


```{r}
region_ids <- c(
  'nac', 
  'nac_corr',
  'nac_shelllat',
  'nacsh_lat',
  'nacsh_med',
  'dms',
  'dls',
  'ts', 
  'lha_gaba',
  'lha_glut', 
  'lha_ratio'
)


signal_ids <- c(
  'zscore',
  'zscoreblsub'
)
```

# functions
```{r}
key_regions <- tibble(
  region =       c('lha_gaba', 'lha_glut', 'lha_ratio', 'nac',   'nac_corr', 'nacsh_med', 'nac_shelllat', 'nacsh_lat',  'dms', 'dls', 'ts'),
  region_label = c('LHA:GABA', 'LHA:Glut', 'LHA:Ratio', 'NAcCR', 'NAcCC',    'NAcShM',    'NAcShL',       'NAcShL',     'DMS', 'DLS', 'TS')
)

key_solutions <- tibble(
  solution =       c('sucrose00', 'sucrose05', 'sucrose10', 'sucrose20',   'sucrose30', 'nacl000', 'nacl025', 'nacl050',  'nacl100', 'nacl150'),
  solution_label = c('0',         '5',         '10',        '20',          '30',        '0.00',    '0.25',    '0.50',     '1.00',    '1.50'),
  solution_set   = c('sucrose',   'sucrose',   'sucrose',   'sucrose',     'sucrose',   'nacl',    'nacl',    'nacl',     'nacl',    'nacl')
)

format_solutions <- function(df, key_regions){
  df %>%
    ungroup() %>%
    left_join(key_solutions) %>%
    mutate(solution_label = factor(solution_label, levels = key_solutions$solution_label %>% unique())) %>%
    select(-solution) %>%
    rename(solution = solution_label) %>%
    select(solution, everything())
}

key_set_id <- tibble(
  set_id =       c('wrsuc', 'frsuc', 'wrnacl'),
  set_id_label = c('WR:Suc','FR:Suc','WR:NaCl')
)

format_pc <- function(df){
  df %>%
    mutate(pc_id = case_when(
         pc_id == 'pc1' ~ 'PC1',
         pc_id == 'pc2' ~ 'PC2',
         pc_id == 'pc3' ~ 'PC3',
         pc_id == 'da_mean' ~ 'Mean DA'
  )
  )
}


join_solution_x <- tibble(
  solution = c('sucrose00', 'sucrose05', 'sucrose10', 'sucrose20', 'sucrose30', 'nacl000', 'nacl025', 'nacl050', 'nacl100', 'nacl150'),
  plt_x =    c(           1,           2,           3,           4,           5,        5,         4,         3,         2,        1),
  plt_f =    c(           1,           1,           1,           1,           1,        2,         2,         2,         2,        2)
)

format_group_combined <- function(df){
  df %>%
    mutate(group_combined = case_when(
      group_combined == 'control' ~ 'Control',
      group_combined == 'vgat_stim' ~ 'LHA GABA',
      group_combined == 'vglut2_stim' ~ 'LHA Glut'
    ))
}
```



```{r}
combine_session_files <- function(process_blocknames, dir_localdata_sessions, fn_suffix){
  
  for(process_blockname in process_blocknames){
    dir_session_process <- str_c(dir_localdata_sessions, process_blockname, '/')
    
    # read in behavior data
    if(fn_suffix %>% str_detect('.csv')){
      df <- read.csv(str_c(dir_session_process, process_blockname, fn_suffix)) 
    } else if(fn_suffix %>% str_detect('.feather')){
      df <- read_feather(str_c(dir_session_process, process_blockname, fn_suffix)) 
    }
    
    if(process_blockname == process_blocknames[1]){ # if first loop
      df_combined <- df
    } else {
      df_combined <- df %>% bind_rows(df_combined,.)
    }
  }
  
  return(df_combined)
}



combine_session_fp <- function(process_blocknames, dir_localdata_sessions){
  
  for(process_blockname in process_blocknames){
    dir_session_process <- str_c(dir_localdata_sessions, process_blockname, '/')
    
    ## read in fp data
    df <- read_feather(str_c(dir_session_process, process_blockname, '_streams_peth_preprocessed.feather')) %>%
      filter(event_id_char %in% c('access_period', 'spout_extended')) %>%
      rename(trial_num = event_number) %>%
      select(any_of(c("blockname", "region", "trial_num", "time_rel", "time", "signal", "delta_signal_poly", "zscore", "zscore_blsub")))
  
    df_trial_info <- read.csv(str_c(dir_session_process, process_blockname, '_data_trial_summary.csv')) %>%
      select(blockname, trial_num, spout, solution, trial_lick, lick_count, lick_ts_first, lick_ts_last) %>%
      mutate(solution_previous = lag(solution))
  
    df <- df %>%
      left_join(df_trial_info, by = join_by(blockname, trial_num))
    
    if(process_blockname == process_blocknames[1]){ # if first loop
      df_combined <- df
    } else {
      df_combined <- df %>% bind_rows(df_combined,.)
    }
  }
  
  return(df_combined)
}


get_mean_signals <- function(df){
  df %>%
    summarise(
      delta_signal_poly_sem = sd(delta_signal_poly)/sqrt(n()),
      delta_signal_poly_mean = delta_signal_poly %>% mean(),
      zscore_sem = sd(zscore)/sqrt(n()),
      zscore_mean = zscore %>% mean(),
      zscore_blsub_sem = sd(zscore_blsub)/sqrt(n()),
      zscore_blsub_mean = zscore_blsub %>% mean(), 
      sample_count = n(),
      .groups = 'drop'
    )
}


get_peth_binned_summary <- function(df_peth, peth_tm_bins, grouping_vars){
  
  # for each bin defined in peth_tm_bins
  for(bin_id in seq(1,nrow(peth_tm_bins))){
  
    peth_tm_bin <- peth_tm_bins[bin_id,] # get tm_bin info for loop
    
    # filter time_rel to tm_bins, define time_bin,  summarise and combine
    if(bin_id == 1){
      
      df_fp_peth_summary <- df_peth %>%
        filter(time_rel > peth_tm_bin$tm_bin_start, time_rel < peth_tm_bin$tm_bin_end) %>%
        mutate(time_bin = peth_tm_bin$tm_bin_id) %>%
        group_by(across(all_of(grouping_vars))) %>%
        get_mean_signals()
      
    } else {
      df_fp_peth_summary <- df_peth %>%
        filter(time_rel > peth_tm_bin$tm_bin_start, time_rel < peth_tm_bin$tm_bin_end) %>%
        mutate(time_bin = peth_tm_bin$tm_bin_id) %>%
        group_by(across(all_of(grouping_vars))) %>%
        get_mean_signals() %>%
        bind_rows(df_fp_peth_summary,.)
    }
  }
  
  # compute mean signal at baseline of subsequent trial
  if(sum('solution' %in% grouping_vars)){
    grouping_vars_previous <- grouping_vars
    grouping_vars_previous[grouping_vars_previous=='solution'] <- 'solution_previous'
    
    
    if(sum('solution_previous' %in% names(df_fp_peth)) == 1){
      df_fp_peth_summary <- df_peth %>%
        filter(time_rel > -3, time_rel < 0) %>%
        mutate(time_bin = 'baseline_subsequent') %>%
        group_by(across(all_of(grouping_vars_previous))) %>%
        get_mean_signals() %>%
        rename(solution = solution_previous) %>%
        filter(!is.na(solution)) %>%
        bind_rows(df_fp_peth_summary,.)
    }
  }
  
  
  
  
  return(df_fp_peth_summary)
}



```





## kinetics
```{r}
get_kinetics <- function(df, var_dv, rise_time_tresh){
  # df should be streams_peth_solution that contains blockname, region, trial_num, deprivation, and 'var_dv'
  
  # compute derivative of var_dv for each trial
  df_derivative <- df %>%
    group_by(blockname, region, trial_num) %>%
    mutate(derivative = !!as.name(var_dv) - lag(!!as.name(var_dv)))  %>%
    ungroup()
  
  # obtain the mean derivative trace
  df_derivative_trace_mean <- df_derivative %>%
    group_by(region, solution, time_rel) %>%
    summarise(
      derivative_sem = sd(derivative)/sqrt(n()),
      derivative_mean = derivative %>% mean(),
      .groups = 'drop'
    )
  
  # obtain the max deriavative and time of max derivative for each trial
  df_derivative_max <- df_derivative %>%
    filter(time_rel > 0, time_rel < 3) %>%
    group_by(blockname, subject, region, trial_num) %>%
    filter(derivative == max(derivative, na.rm= TRUE)) %>% # get max derivative for each trial
    ungroup() %>%
    select(blockname, subject, region, solution, trial_num, derivative, time_rel) %>%
    rename(derivative_max = derivative, derivative_max_time = time_rel)
  
  # obtain time signal passes rise_time_thresh for each trial
  df_time_rise <- df %>%
    filter(time_rel > 0, time_rel < 3) %>%
    group_by(blockname, subject, region, trial_num) %>%
    filter(!!as.name(var_dv) > rise_time_tresh) %>%           # filter to signal < threshold
    filter(time_rel == min(time_rel)) %>%                            # filter to minimum time
    ungroup() %>%
    select(blockname, subject, region, solution, trial_num, time_rel) %>%     #
    rename(time_rise = time_rel)
  
  
  # combine trial summaries
  df_kinetic_summary_trial <- df_derivative_max %>%
    full_join(df_time_rise, by = join_by(blockname, subject, region, solution, trial_num))
  
  # compute subject summaries
  df_kinetic_summary_subject_region_solution <- df_kinetic_summary_trial %>%
    group_by(subject, region, solution) %>%
    summarise(
      derivative_max_mean = derivative_max %>% mean(na.rm = T),
      derivative_max_time_mean = derivative_max_time %>% mean(na.rm = T),
      time_rise_mean = time_rise %>% mean(na.rm = T),
      .groups = 'drop'
    )
  
  return(list(df_derivative_trace_mean, df_kinetic_summary_trial, df_kinetic_summary_subject_region_solution))
}


plt_line_pairwise <- function(df, dir_output, fn_stem, var_id = 'subject', var_dv, var_within, ylims, heat_range = NA){
  
  n_within <- df %>%
    pull(!!as.name(var_within)) %>% 
    unique() %>%
    length()
  
  pltline <- df %>%
    
    ggplot(aes(region, !!as.name(var_dv))) +
    geom_line(aes(group = !!as.name(var_id)), alpha = 1/4) +
    stat_summary(fun = 'mean', geom = 'line', aes(group = 1)) +
    stat_summary(fun.data = 'mean_se', geom = 'errorbar', aes(group = 1), width = 0) +
    theme_ag01() +
    theme(axis.title.x = element_blank(),
          axis.text.x = element_text(angle = 90, hjust = 1, vjust = 0.3)) +
    coord_cartesian(xlim = c(0.5, n_within + 0.5), ylim = ylims, expand = F)
  
  
  stats_results <- df %>%
    aov_rm_one_within(dir_output,fn_stem,var_id, var_dv, var_within)
  
  
  df_pairs <- stats_results[[3]] %>%
    format_regions('contrast1_within', key_regions) %>%
    format_regions('contrast2_within', key_regions) 
  
  
  plt_comparisions <- plt_hsd_matrix_2contrasts(df_pairs, heat_range) 
  
  
  pltline + plt_comparisions +
    plot_layout(nrow = 1, widths = unit(4,'cm'), heights = unit(4, 'cm'))
  
  save_pdf(dir_output, str_c(fn_stem, '_plt_line_pairwise.pdf'), 10, 5)
  
  return(list(stats_results, pltline, plt_comparisions))
}



plt_summary_kinetics <- function(plt_data_kinetics, fn_stem_set){
  dir_output_subplots <- str_c(dir_output, fn_stem_set, '/')
  
  if(!dir.exists(dir_output_subplots)){
    dir.create(dir_output_subplots)
  }
  
  kientics_region_vs_derivativemax <- 
    plt_line_pairwise(
      df = plt_data_kinetics, 
      dir_output = dir_output_subplots,
      fn_stem = str_c(fn_stem_set, '_region_vs_derivativemax'),
      var_dv = 'derivative_max_mean',
      var_within = 'region' ,
      ylims = c(0,2.5)
    )
  
  kientics_region_vs_derivativemaxtime <- 
    plt_line_pairwise(
      df = plt_data_kinetics, 
      dir_output = dir_output_subplots,
      fn_stem = str_c(fn_stem_set, 'region_vs_derivativemaxtime'),
      var_dv = 'derivative_max_time_mean',
      var_within = 'region' ,
      ylims = c(0,2.5)
    )
  
  kientics_region_vs_timerise <- 
    plt_line_pairwise(
      df = plt_data_kinetics, 
      dir_output = dir_output_subplots,
      fn_stem = str_c(fn_stem_set, 'region_vs_timerise'),
      var_dv = 'time_rise_mean',
      var_within = 'region' ,
      ylims = c(0,1)
    )
  
  
  kientics_region_vs_derivativemax[[2]] + kientics_region_vs_derivativemax[[3]] +
    kientics_region_vs_derivativemaxtime[[2]] + kientics_region_vs_derivativemaxtime[[3]] +
    kientics_region_vs_timerise[[2]] + kientics_region_vs_timerise[[3]] +
    plot_layout(ncol = 2, widths = unit(4, 'cm'), heights = unit(4, 'cm')) +
    plot_annotation(
      title = str_c('summary - ', fn_stem_set)
    )
  
  
  save_pdf(dir_output, str_c(fn_stem_set, '_summary_figure.pdf'), 9, 9)
}
```



## correlation
```{r}
tidy_cor_output_reshape <- function(df, n_table, var_name){
  df_tidy <- df[[n_table]] %>%
    as_tibble()
  
  df_tidy <- df_tidy %>%
    mutate(var_y = colnames(df_tidy)) %>%
    gather('var_x', !!as.name(var_name), -var_y) 
  

  
  return(df_tidy)
}

tidy_cor_output <- function(df){
  tidy_cor_output_reshape(df, 1, 'r') %>%
    left_join(tidy_cor_output_reshape(df, 2, 'n'), by = c("var_y", "var_x")) %>%
    left_join(tidy_cor_output_reshape(df, 3, 'p'), by = c("var_y", "var_x"))
}


get_cormatrix <- function(df){
  df_corr = rcorr(as.matrix(df))
  tidy_cor_output(df_corr)
}

tidy_cormatrix <- function(df, var_cors, var_groups = NA){
  require(Hmisc)
  
  df <- df %>%
    ungroup()


  if(sum(is.na(var_groups)) > 0){
    df <- df %>% select(var_cors)
  
    df %>%
      group_modify(~ get_cormatrix(.))
    
  } else {
    df <- df %>% select(var_cors, var_groups)
    
    df %>%
      group_by_at(var_groups) %>%
      group_modify(~ get_cormatrix(.))
    
  }
}

plt_corrmatrix <- function(df){
  df %>%
    ggplot(aes(var_x, var_y, fill = r)) +
    geom_tile() +
    scale_fill_gradientn(colors = c('blue', 'white', 'red'), limits = c(-1,1), oob = scales::squish) +
    theme_ag01() +
    theme(
      axis.title.x = element_blank(),
      axis.title.y = element_blank(),
      axis.text.x = element_text(angle = 90, hjust = 1, vjust = 0.3)
    ) 
}
```


# analysis / plotting
## summarise data 
### set_id
```{r}

subjects <- read_xlsx('log_data_analysis.xlsx', sheet = 'subjects') %>%
  filter(inclusion_consumption == 1) %>%
  #filter(experiment == 'aaw') %>%
  pull(subject)

log_data <- read_xlsx('log_data_analysis.xlsx', sheet = 'fp') %>%
  filter(exclude != 1) %>%
  filter(subject %in% subjects) %>%
  get_set_id() %>%
  filter(!is.na(set_id))


# loop over peth_parameters in log_data_analysis.xlsx from here ------
loop_set_ids <- log_data$set_id %>% unique()
#loop_set_ids <- c('frsuc', 'wrsuc', 'wrnacl') # ~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~udpate


# ---- params
peth_filt_fulltrace <- c(-3, 8) # time_rel included in output

peth_tm_bins <- tibble(
  tm_bin_id =    c('access', 'prelick', 'initial', 'sustained', 'post'),
  tm_bin_start = c(       0,         0,         0,           2,      6),
  tm_bin_end   = c(       3,       0.3,         1,           3,      8)
)

dir_output <- './data/combined_setid/'

fns_qc_metrics <- list.files(dir_localdata_sessions, pattern = 'quality_metrics.csv', recursive = T, full.names = T)
combined_qc_metrics <- bind_rows(lapply(fns_qc_metrics, read.csv))

subjects_to_remove <- log_analysis_subjects %>%
  filter(remove == 1) %>%
  pull(subject)

for(loop_set_id in loop_set_ids){
  print(str_c('processing set_id:', loop_set_id))
  
  # setup import blocknames
  process_blocknames <- log_data %>%
    filter(set_id %in% loop_set_id) %>%
    pull(blockname)

# import peth and join in subject id
  df_fp_peth <- combine_session_fp(process_blocknames, dir_localdata_sessions) %>%
    left_join(log_analysis_fp %>% select(blockname, subject), by = 'blockname') 
  
  # exclude subjects defined in log_analysis_subjects
  df_fp_peth <- df_fp_peth %>%
    filter(!subject %in% subjects_to_remove) 
   
  # exclude fibers with poor quality
  df_fp_peth <- df_fp_peth %>%
    left_join(combined_qc_metrics %>% select(blockname, region, exclude_poor_signal), by = c('blockname', 'region')) %>%
    filter(exclude_poor_signal == 0 | is.na(exclude_poor_signal)) %>% # is.na for lha ratio
    select(-exclude_poor_signal)
  
  # filter fibers based on log_placements
  df_fp_peth <- df_fp_peth %>%
    format_regions('region',key_regions) %>%
    filter_placements('exclude_da_consumption') # filter fibers
  
  # filter time_rel
  df_fp_peth <- df_fp_peth %>% 
    filter(time_rel > peth_filt_fulltrace[1], time_rel < peth_filt_fulltrace[2])
  
  # process full dataset and only trials with licks 
  for(toggle_filt_trial_lick in  c(0,1)){ 
    
    if(toggle_filt_trial_lick == 1){
      df_fp_peth <- df_fp_peth %>%
        filter(trial_lick == 1)
      fn_prefix <- 'filtlick'
    } else {
      fn_prefix <- 'full'
    }
    
    fn_prefix <- str_c(loop_set_id, '_', fn_prefix)
    
    
    # fp trace - overall
    df_fp_peth_summary_trace_overall <- df_fp_peth %>%
      left_join(join_info) %>%
      group_by(set_id, region, solution, time_rel) %>%
      get_mean_signals() 
    
    df_fp_peth_summary_trace_overall %>%
      write_csv(str_c(dir_output, fn_prefix, '_', 'peth_summary_trace_overall.csv'))
    
    
    # fp trace - trial lick
    if(toggle_filt_trial_lick == 0){
      df_fp_peth_summary_trace_overall <- df_fp_peth %>%
        left_join(join_info) %>%
        group_by(set_id, region, trial_lick, time_rel) %>%
        get_mean_signals() 
      
      df_fp_peth_summary_trace_overall %>%
        write_csv(str_c(dir_output, fn_prefix, '_', 'peth_summary_trace_triallick.csv'))
    }
    
    # fp trace - grouped by subject
    df_fp_peth_summary_trace_subject <- df_fp_peth %>%
      left_join(join_info) %>%
      group_by(experiment, subject, set_id, region, solution, time_rel) %>%
      get_mean_signals()
    
    df_fp_peth_summary_trace_subject %>%
      write_csv(str_c(dir_output, fn_prefix, '_',  'peth_summary_trace_subject.csv'))
    
    # fp trace - grouped by binned trial
    df_fp_peth_summary_trace_binnedtrial <- df_fp_peth %>%
      left_join(join_info) %>%
      mutate(bin_trial = cut(trial_num, seq(0,100, 10), labels = sprintf("%02d", seq(0,90,10)))) %>%
      mutate(bin_trial = bin_trial %>% as.character()) %>%
      group_by(set_id, region, solution, bin_trial, time_rel) %>%
      get_mean_signals()
    
    df_fp_peth_summary_trace_binnedtrial %>%
      write_csv(str_c(dir_output, fn_prefix, '_',  'peth_summary_trace_binnedtrial.csv'))
    
    # fp summary - subject
    grouping_vars <- c('experiment', 'subject', 'set_id', 'region', 'solution', 'time_bin')
    
    df_fp_peth_summary_means_subject <- df_fp_peth %>%
      select(-subject) %>%
      left_join(join_info, by = join_by(blockname)) %>%
      get_peth_binned_summary(peth_tm_bins, grouping_vars)
    
    df_fp_peth_summary_means_subject %>%
      write_csv(str_c(dir_output, fn_prefix, '_',  'peth_summary_means_subject.csv'))
    
    # fp summary - subject - trial lick
    if(toggle_filt_trial_lick == 0){
      grouping_vars <- c('experiment', 'subject', 'set_id', 'region', 'trial_lick', 'time_bin')
      
      df_fp_peth_summary_means_subject_triallick <- df_fp_peth %>%
        select(-subject) %>%
        left_join(join_info, by = join_by(blockname)) %>%
        get_peth_binned_summary(peth_tm_bins, grouping_vars) 
      
    df_fp_peth_summary_means_subject_triallick %>%
      write_csv(str_c(dir_output, fn_prefix, '_',  'peth_summary_means_subject_triallick.csv'))
    }
    
    
    
    # fp summary - trial
    grouping_vars <- c('experiment', 'blockname', 'subject', 'set_id', 'region', 'trial_num', 'solution', 'time_bin', 'lick_count', 'lick_ts_first', 'lick_ts_last')
    
    df_fp_peth_summary_means_trial <- df_fp_peth %>%
      left_join(join_info) %>%
      get_peth_binned_summary(peth_tm_bins, grouping_vars)
    
    df_fp_peth_summary_means_trial %>%
      write_csv(str_c(dir_output, fn_prefix, '_',  'peth_summary_means_trial.csv'))
    
    
    # fp summary - trial - trial lick
    if(toggle_filt_trial_lick == 0){
      grouping_vars <- c('experiment', 'blockname', 'subject', 'set_id', 'region', 'trial_num', 'trial_lick', 'time_bin', 'lick_count', 'lick_ts_first', 'lick_ts_last')
      
      df_fp_peth_summary_means_trial_triallick <- df_fp_peth %>%
        left_join(join_info) %>%
        get_peth_binned_summary(peth_tm_bins, grouping_vars)
      
      df_fp_peth_summary_means_trial_triallick %>%
        write_csv(str_c(dir_output, fn_prefix, '_',  'peth_summary_means_trial_triallick.csv'))
    }
    
    
    # fp summary - binned trial
    grouping_vars <- c('experiment', 'blockname', 'subject', 'set_id', 'region', 'bin_trial', 'solution', 'time_bin')
    
    df_fp_peth_summary_means_binnedtrials <- df_fp_peth %>%
      left_join(join_info) %>%
      mutate(bin_trial = cut(trial_num, seq(0,100, 10), labels = sprintf("%02d", seq(0,90,10)))) %>%
      mutate(bin_trial = bin_trial %>% as.character()) %>%
      get_peth_binned_summary(peth_tm_bins, grouping_vars)
    
    df_fp_peth_summary_means_binnedtrials %>%
      write_csv(str_c(dir_output, fn_prefix, '_',  'peth_summary_means_binnedtrial.csv'))
    
    # fp summary - binned trial
    if(toggle_filt_trial_lick == 0){
      grouping_vars <- c('experiment', 'blockname', 'subject', 'set_id', 'region', 'bin_trial', 'trial_lick', 'time_bin')
      
      df_fp_peth_summary_means_binnedtrials_triallick <- df_fp_peth %>%
        left_join(join_info) %>%
        mutate(bin_trial = cut(trial_num, seq(0,100, 10), labels = sprintf("%02d", seq(0,90,10)))) %>%
        mutate(bin_trial = bin_trial %>% as.character()) %>%
        get_peth_binned_summary(peth_tm_bins, grouping_vars)
      
      df_fp_peth_summary_means_binnedtrials_triallick %>%
        write_csv(str_c(dir_output, fn_prefix, '_',  'peth_summary_means_binnedtrial_triallick.csv'))
    }
    
    # derivative summary
    if(toggle_filt_trial_lick == 1){
      df_kinetics <- df_fp_peth %>%
        left_join(log_analysis_fp %>% select(blockname, deprivation), by = 'blockname') 
      
      kenetics_list <- get_kinetics(
        df = df_kinetics,
        var_dv = 'zscore_blsub', 
        rise_time_tresh = 0.25
      )
      
      # save derivative trace 
      kenetics_list[[1]] %>%
        write_csv(str_c(dir_output, fn_prefix, '_',  'pethkinetics_summary_trace_subject.csv'))
        
      # save derivative summary trial
      kenetics_list[[2]] %>%
        write_csv(str_c(dir_output, fn_prefix, '_',  'pethkinetics_summary_means_trial.csv'))
      
      # save derivative summary solution
      kenetics_list[[3]]  %>%
        write_csv(str_c(dir_output, fn_prefix, '_',  'pethkinetics_summary_means_subject.csv'))
    }
    
    # get analysis_info and export
    meta_countfibers <- df_fp_peth %>%
      group_by(blockname, region) %>%
      filter(time == min(time)) %>%
      group_by(region) %>%
      summarise( count_fibers = n()) %>%
      mutate(region = str_c('n_', region)) %>%
      spread(region, count_fibers)
    
    meta_countsubjects <- df_fp_peth %>%
      filter(time_rel == 0) %>%
      select(subject) %>%
      unique() %>%
      summarise(count_subject = n())
    
    
    meta_counttrials_all <- df_fp_peth %>%
      filter(time_rel == 0) %>%
      group_by(region) %>%
      summarise(count_trials_solution = n())  %>%
      mutate(set_id = loop_set_id) %>%
      select(set_id, everything()) 
    
    meta_counttrials_all %>%
      write_csv(str_c(dir_output, fn_prefix, '_',  'meta_count_trial_all.csv'))
    
    meta_counttrials_solution <- df_fp_peth %>%
      filter(time_rel == 0) %>%
      group_by(region, solution) %>%
      summarise(count_trials_solution = n())  %>%
      mutate(set_id = loop_set_id) %>%
      select(set_id, everything())
    
    meta_counttrials_solution %>%
      write_csv(str_c(dir_output, fn_prefix, '_',  'meta_count_trial_solution.csv'))
    
    # save export
    analysis_summary <- tibble(
        set_id = loop_set_id,
        toggle_filt_trial_lick = toggle_filt_trial_lick
      ) %>%
      bind_cols(meta_countsubjects) %>%
      bind_cols(meta_countfibers) 
    
    analysis_summary %>%
      write_csv(str_c(dir_output, fn_prefix, '_',  'meta_setid.csv'))
  }
}
```

### correlation for 6 fiber subjects
```{r}

# 6 fiber inclusion
blocknames_6fibers <- log_analysis_fp 

# remove subjects
blocknames_6fibers <- blocknames_6fibers %>%
  filter(!subject %in% subjects_to_remove) 

# join in regions
blocknames_6fibers <- blocknames_6fibers %>%
  left_join(log_npm %>% select(blockname, region))


# filter out sessions with poor signal on at least 1 fiber
blocknames_6fibers <- blocknames_6fibers %>%
  left_join(combined_qc_metrics %>% select(blockname, region, exclude_poor_signal), by = c('blockname', 'region')) %>%
  filter(exclude_poor_signal == 0 | is.na(exclude_poor_signal)) %>% # is.na for lha ratio
  select(-exclude_poor_signal)

# filter out subjects with at least 1 removed fiber
blocknames_6fibers <- blocknames_6fibers %>%
  format_regions('region',key_regions) %>%
  filter_placements('exclude_da_consumption') # filter fibers


# filter to sessions with 6 fibers
blocknames_6fibers <- blocknames_6fibers %>%
  group_by(blockname) %>%
  mutate(region_count = n()) %>%
  ungroup() %>%
  filter(region_count == 6)

# return unique blocknames
#blocknames_6fibers <- blocknames_6fibers$blockname %>% unique()
blocknames_6fibers <- blocknames_6fibers %>%
  get_set_id() %>%
  select(subject, blockname, procedure, set_id) %>%
  unique() %>%
  filter(!is.na(set_id))
```


```{r}
subject_x_set <- blocknames_6fibers %>%
  select(subject, set_id) %>%
  unique()

print('preprocessing correlation for subjects with 6 fibers combined for each set_id...')

for(n_subject_x_set in seq(1, nrow(subject_x_set))){
  
  loop_subject_x_set <- subject_x_set[n_subject_x_set,]
  
  print(str_c(' ~ ', loop_subject_x_set$subject, '_', loop_subject_x_set$set_id, ' [', n_subject_x_set, ' / ', nrow(subject_x_set), ']'))
  
  loop_dir_output <- str_c(dir_sessions_combined_subject, loop_subject_x_set$subject, '_', loop_subject_x_set$set_id, '/corelation/')
  
  # create directory if it does not already exist
  if(!dir.exists(loop_dir_output)){
    dir.create(loop_dir_output, recursive = T)
  }
  
  # combine blocknames for peth and baseline, then pivot wide, and save dataframes
  loop_blocknames <- blocknames_6fibers %>%
    filter(subject == loop_subject_x_set$subject, 
           set_id == loop_subject_x_set$set_id) %>%
    pull(blockname)
  
  # baseline
  df_bl <- combine_session_fp_bl(loop_blocknames, dir_localdata_sessions) %>%
    mutate(subject = loop_subject_x_set$subject, 
           set_id = loop_subject_x_set$set_id)
  
  df_bl <- df_bl %>%
    select(blockname, subject, set_id, time, region, zscore) %>%
    spread(region, zscore)

  df_bl %>%
    write_feather(str_c(loop_dir_output, 'streams_baseline_cor_data.feather'))
  
  # peth
  df_peth <- combine_session_fp(loop_blocknames, dir_localdata_sessions) %>%
    mutate(subject = loop_subject_x_set$subject, 
           set_id = loop_subject_x_set$set_id) %>%
    filter(trial_lick == 1) %>%
    filter(time_rel > -3, time_rel <= 9)
  
  
    meta_temp <- df_peth %>% 
    filter(time_rel == 0) 
  
    n_sessions <- meta_temp %>%
      select(blockname) %>%
      unique()%>%
      nrow()
    
    n_trial <- meta_temp %>%
      select(blockname, trial_num) %>%
      unique() %>%
      nrow()
    
  tibble(
    n_sessions = n_sessions,
    n_trial = n_trial,
    filt_lick = 1
  ) %>%
    write_csv(str_c(loop_dir_output, 'streams_peth_cor_meta.csv'))
  
  df_peth <- df_peth %>%
    select(blockname, subject, set_id, trial_num, solution, time, time_rel, region, zscore_blsub) %>%
    spread(region, zscore_blsub)
  
  df_peth %>%
    write_feather(str_c(loop_dir_output, 'streams_peth_cor_data.feather'))
  
  # determine number of trials for each solution
  trial_counts <- df_peth %>%
    select(c(c('nac', 'nac_shelllat', 'nac_corr', 'dms', 'dls', 'ts'), c('subject', 'set_id', 'solution', 'time_rel'))) %>%
    group_by_at(c('subject', 'set_id', 'solution', 'time_rel')) %>%
    summarise(count = n()) %>%
    select(count) %>%
    unique() 
  
  if(min(trial_counts$count) > 4){
    # compute correlations, summaries, and write 
    ## baseline
    corr_baseline <- tidy_cormatrix(df_bl, c('nac', 'nac_shelllat', 'nac_corr', 'dms', 'dls', 'ts'), c('subject', 'set_id')) %>%
      format_regions('var_y', key_regions) %>%
      format_regions('var_x', key_regions) 
    
    corr_baseline %>%
      write_csv(str_c(loop_dir_output, 'streams_baseline_corr.csv'))
    
    ## peth - time_rel
    corr_peth_timerel <- tidy_cormatrix(df_peth, c('nac', 'nac_shelllat', 'nac_corr', 'dms', 'dls', 'ts'), c('subject', 'set_id', 'time_rel')) %>%
      format_regions('var_y', key_regions) %>%
      format_regions('var_x', key_regions)
    
    corr_peth_timerel %>%
      write_csv(str_c(loop_dir_output, 'streams_peth_corr_timerel.csv'))
    
    ## peth - window 
    corr_peth_access <- df_peth %>%
      mutate(time_rel_bin = case_when(
        time_rel > -2 & time_rel < 0 ~ 'Pre',
        time_rel >= 1 & time_rel < 3 ~ 'Sustained',
        time_rel >= 6 & time_rel < 8 ~ 'Post'
      )) %>%
      filter(!is.na(time_rel_bin)) %>%
      tidy_cormatrix(c('nac', 'nac_shelllat', 'nac_corr', 'dms', 'dls', 'ts'), c('subject', 'set_id', 'time_rel_bin')) %>%
      format_regions('var_y', key_regions) %>%
      format_regions('var_x', key_regions)
    
    corr_peth_access %>%
      write_csv(str_c(loop_dir_output, 'streams_peth_corr_windows.csv'))
    
    ## peth - solution x time_rel
    corr_peth_timerel_sol <- tidy_cormatrix(df_peth, c('nac', 'nac_shelllat', 'nac_corr', 'dms', 'dls', 'ts'), c('subject', 'set_id', 'solution', 'time_rel')) %>%
      format_regions('var_y', key_regions) %>%
      format_regions('var_x', key_regions)
    
    corr_peth_timerel_sol %>%
      write_csv(str_c(loop_dir_output, 'streams_peth_corr_timerel_sol.csv'))
  } else {
    print('**TOO FEW TRIALS FOR CORRELATION-- SKIPPING**')
  }
  
  
  
}
```




```{r}
combine_session_fp_bl <- function(process_blocknames, dir_localdata_sessions){
  
  for(process_blockname in process_blocknames){
    dir_session_process <- str_c(dir_localdata_sessions, process_blockname, '/')
    
    ## read in fp data
    df <- read_feather(str_c(dir_session_process, process_blockname, '_streams_baseline_preprocessed.feather')) %>%
      select(any_of(c("blockname", "region", "time", "signal", "delta_signal_poly", "zscore", "zscore_blsub")))
    
    if(process_blockname == process_blocknames[1]){ # if first loop
      df_combined <- df
    } else {
      df_combined <- df %>% bind_rows(df_combined,.)
    }
  }
  
  return(df_combined)
}
```



### lick vs no-lick
```{r}
# summarise lick vs no lick across all main set_id
run_licknolick_main_set_ids <- 0

if(run_licknolick_main_set_ids == 1){
  process_blocknames <- log_data %>%
      filter(set_id %in% c('wrsuc', 'frsuc','wrnacl')) %>%
      pull(blockname)
    
  # import peth and join in subject id
  df_fp_peth <- combine_session_fp(process_blocknames, dir_localdata_sessions) %>%
    left_join(log_analysis_fp %>% select(blockname, subject), by = 'blockname') 
  
  # exclude subjects defined in log_analysis_subjects
  df_fp_peth <- df_fp_peth %>%
    filter(!subject %in% subjects_to_remove)
   
  # exclude fibers with poor quality
  df_fp_peth <- df_fp_peth %>%
    left_join(combined_qc_metrics %>% select(blockname, region, exclude_poor_signal), by = c('blockname', 'region')) %>%
    filter(exclude_poor_signal == 0 | is.na(exclude_poor_signal)) %>% # is.na for lha ratio
    select(-exclude_poor_signal)
  
  # filter fibers based on log_placements
  df_fp_peth <- df_fp_peth %>%
    format_regions('region',key_regions) %>%
    filter_placements('exclude_da_consumption') # filter fibers
  
  # filter time_rel
  df_fp_peth <- df_fp_peth %>% 
    filter(time_rel > peth_filt_fulltrace[1], time_rel < peth_filt_fulltrace[2])
  
  # process full dataset and only trials with licks 
    
  fn_prefix <- str_c('combined_main_set_id_lickvsnolick')
  
  
  # fp trace - overall
  df_fp_peth_summary_trace_overall <- df_fp_peth %>%
    left_join(join_info) %>%
    group_by(region, trial_lick, time_rel) %>%
    get_mean_signals() 
  
  df_fp_peth_summary_trace_overall %>%
    write_csv(str_c(dir_output, fn_prefix, '_', 'peth_summary_trace_overall.csv'))
  
  
  # fp trace - grouped by subject
  df_fp_peth_summary_trace_subject <- df_fp_peth %>%
    left_join(join_info) %>%
    group_by(experiment, subject, region, trial_lick, time_rel) %>%
    get_mean_signals()
  
  df_fp_peth_summary_trace_subject %>%
    write_csv(str_c(dir_output, fn_prefix, '_',  'peth_summary_trace_subject.csv'))
  
  
  # fp summary - trial
  grouping_vars <- c('experiment', 'blockname', 'subject', 'set_id', 'region', 'trial_num', 'trial_lick', 'time_bin', 'lick_count', 'lick_ts_first', 'lick_ts_last')
  
  df_fp_peth_summary_means_trial <- df_fp_peth %>%
    left_join(join_info) %>%
    get_peth_binned_summary(peth_tm_bins, grouping_vars)
  
  df_fp_peth_summary_means_trial %>%
    write_csv(str_c(dir_output, fn_prefix, '_',  'peth_summary_means_trial.csv'))
  
  
  # fp summary - binned trial
  grouping_vars <- c('experiment', 'blockname', 'subject', 'region', 'bin_trial', 'trial_lick', 'time_bin')
  
  df_fp_peth_summary_means_binnedtrials <- df_fp_peth %>%
    left_join(join_info) %>%
    mutate(bin_trial = cut(trial_num, seq(0,100, 10), labels = sprintf("%02d", seq(0,90,10)))) %>%
    mutate(bin_trial = bin_trial %>% as.character()) %>%
    get_peth_binned_summary(peth_tm_bins, grouping_vars)
  
  df_fp_peth_summary_means_binnedtrials %>%
    write_csv(str_c(dir_output, fn_prefix, '_',  'peth_summary_means_binnedtrial.csv'))
  
  # fp summary - subject
  grouping_vars <- c('experiment', 'subject', 'region', 'trial_lick', 'time_bin')
  
  df_fp_peth_summary_means_subject <- df_fp_peth %>%
    select(-subject) %>%
    left_join(join_info, by = join_by(blockname)) %>%
    get_peth_binned_summary(peth_tm_bins, grouping_vars)
  
  df_fp_peth_summary_means_subject %>%
    write_csv(str_c(dir_output, fn_prefix, '_',  'peth_summary_means_subject.csv'))
  
  # get analysis_info and export
  meta_countfibers <- df_fp_peth %>%
    group_by(blockname, region) %>%
    filter(time == min(time)) %>%
    group_by(region) %>%
    summarise( count_fibers = n()) %>%
    mutate(region = str_c('n_', region)) %>%
    spread(region, count_fibers)
  
  meta_countsubjects <- df_fp_peth %>%
    filter(time_rel == 0) %>%
    select(subject) %>%
    unique() %>%
    summarise(count_subject = n())
  
  
  meta_counttrials_all <- df_fp_peth %>%
    filter(time_rel == 0) %>%
    group_by(region) %>%
    summarise(count_trials_solution = n())  %>%
    mutate(set_id = loop_set_id) %>%
    select(set_id, everything()) 
  
  meta_counttrials_all %>%
    write_csv(str_c(dir_output, fn_prefix, '_',  'meta_count_trial_all.csv'))
  
  meta_counttrials_solution <- df_fp_peth %>%
    filter(time_rel == 0) %>%
    group_by(region, solution) %>%
    summarise(count_trials_solution = n())  %>%
    mutate(set_id = loop_set_id) %>%
    select(set_id, everything())
  
  meta_counttrials_solution %>%
    write_csv(str_c(dir_output, fn_prefix, '_',  'meta_count_trial_solution.csv'))
  
  # save export
  analysis_summary <- tibble(
    set_id = loop_set_id,
    toggle_filt_trial_lick = toggle_filt_trial_lick
  ) %>%
    bind_cols(meta_countsubjects) %>%
    bind_cols(meta_countfibers) 
  
  analysis_summary %>%
    write_csv(str_c(dir_output, fn_prefix, '_',  'meta_setid.csv'))
}
```


### kinetics
```{r}
analysis_summary %>% write_csv(str_c(dir_output, fn_prefix, '_',  'meta_setid.csv'))
```

```{r}
# nacl000 only
plt_data_kinetics <- df_kinetic_summary_subject_region_solution %>%
  filter(solution == 'nacl000') %>%
  select(-solution) %>%
  group_by(subject, region) %>%
  summarise_all(mean)


plt_summary_kinetics(
  plt_data_kinetics = plt_data_kinetics, 
  fn_stem_set = 'kinetics_nacl000'
  )


```


# final
## lha
```{r}
dir_output_fp_lha <- './analysis_output/peth_lha/'

filt_and_format_data <- function(df){
  df %>% 
    filter(region %>% str_detect('LHA')) %>%
    filter(set_id %in% c('frsuc', 'wrsuc', 'wrnacl')) %>%
    mutate(region = region %>% factor(levels = unique(key_regions$region_label))) %>%
    format_set_id(key_set_id) 
}

fns <- list.files(dir_output)
fns_filt <- fns[fns %>% str_detect('filtlick')]
fns_filt <- fns_filt[fns_filt %>% str_detect('peth_summary_trace_overal')]
fns_filt <- fns_filt %>% str_remove('.csv')

df <- combined_import(import_directory = dir_output, 
                filter_strings = fns_filt,
                prefixes = NA,
                suffixes = c('.csv'),
                verbose = 0
                )[[1]]

plt_data <- df %>% 
  filt_and_format_data()
```

### trace
```{r}
fn_stem <- 'fp_lha_trace'

plt <- plt_data %>%
  ggplot(aes(time_rel, zscore_blsub_mean, group = solution, color = solution, fill = solution)) +
  annotate("rect", xmin = 0, xmax = 3, ymin = -Inf, ymax = Inf, alpha = 1/3, fill = "darkgrey") +
  geom_hline(yintercept = 0, color = 'darkgrey', size = 0.5) +
  geom_ribbon(
    aes(
      ymin = zscore_blsub_mean - zscore_blsub_sem,
      ymax
      = zscore_blsub_mean + zscore_blsub_sem
        ),
    alpha = 1/3,
    color = NA
    ) +
  geom_line() +
  facet_grid(set_id~region) +
  scale_color_manual(values = c(color_values_nacl, color_values_suc)) +
  scale_fill_manual(values = c(color_values_nacl, color_values_suc)) +
  theme_ag01() +
  theme(strip.text = element_text(margin = margin(t = 5, r = 5, b = 5, l = 5))) +
  theme(panel.spacing.y = unit(1, "lines")) +
  force_panelsizes(rows = unit(2, 'cm'), cols = unit(2, 'cm'))


plt <- plt %>%
  add_scale_bar(
    origin = c(-3, -1), 
    x_len = 1, 
    y_len = 1
  )

plt

save_pdf(dir_output_fp_lha, str_c(fn_stem, '.pdf'), 6, 6)
plt_data %>% write_csv(str_c(dir_output_fp_lha, fn_stem, '_data.csv'))
```

### summary - sustained
```{r}
fns <- list.files(dir_output)
fns_filt <- fns[fns %>% str_detect('filtlick')]
fns_filt <- fns_filt[fns_filt %>% str_detect('peth_summary_means_subject')]
fns_filt <- fns_filt %>% str_remove('.csv')

df <- combined_import(import_directory = dir_output, 
                filter_strings = fns_filt,
                prefixes = NA,
                suffixes = c('.csv'),
                verbose = 0
                )[[1]] %>% 
  filt_and_format_data() %>%
  mutate(region_facet = case_when(
    region == 'LHA:Ratio' ~ 2,
    region == 'LHA:GABA' ~ 1,
    region == 'LHA:Glut' ~ 1
  )) 
```

#### wr suc

```{r}
fn_stem <- 'fp_lha_summary_wrsuc'

plt_data <- df %>%
  filter(set_id == 'WR:Suc') %>%
  filter(time_bin == 'sustained') 


plt_data %>%
  ggplot(aes(solution, zscore_blsub_mean, color = region)) +
  #geom_line(aes(group = interaction(region, subject)), alpha = 1/3) +
  geom_hline(yintercept = 0, size = 1/4, color = 'darkgrey') +
  stat_summary(fun = 'mean', geom = 'line', aes(group = region)) +
  stat_summary(fun.data = 'mean_se', geom = 'errorbar', aes(group = region), width = 0) +
  theme_ag01() +
  scale_color_manual(values = color_values_regions) +
  theme(axis.text.x = element_blank())+
  facet_grid(set_id~., scales = 'free') +
  coord_cartesian(xlim = c(0.5, 5.5), ylim = c(-2, 3), clip = 'off', expand = 0) +
  force_panelsizes(rows = unit(2,'cm'), cols = unit(1.5, 'cm')) +
  ylab('Z-score sustained (2-3 s)') +
  xlab('')



save_pdf(dir_output_fp_lha, str_c(fn_stem, '.pdf'), 6, 6)
plt_data %>% write_csv(str_c(dir_output_fp_lha, fn_stem, '_data.csv'))

plt_data %>%
  filter(region %in% c('LHA:GABA', 'LHA:Glut')) %>%
  aov_rm_two_within(dir_output_fp_lha,str_c(fn_stem,'_interaction'), 'subject','zscore_blsub_mean','region', 'solution')


plt_data %>%
  filter(region == 'LHA:GABA') %>%
  aov_rm_one_within(dir_output_fp_lha,str_c(fn_stem,'_gaba'), 'subject','zscore_blsub_mean','solution')

plt_data %>%
  filter(region == 'LHA:Glut') %>%
  aov_rm_one_within(dir_output_fp_lha,str_c(fn_stem,'_glut'), 'subject','zscore_blsub_mean','solution')

plt_data %>%
  filter(region == 'LHA:Ratio') %>%
  aov_rm_one_within(dir_output_fp_lha,str_c(fn_stem,'_ratio'), 'subject','zscore_blsub_mean','solution')

save_aov
```

#### fr suc
```{r}
fn_stem <- 'fp_lha_summary_frsuc'

plt_data <- df %>%
  filter(set_id == 'FR:Suc') %>%
  filter(time_bin == 'sustained') 


plt_data %>%
  ggplot(aes(solution, zscore_blsub_mean, color = region)) +
  #geom_line(aes(group = interaction(region, subject)), alpha = 1/3) +
  geom_hline(yintercept = 0, size = 1/4, color = 'darkgrey') +
  stat_summary(fun = 'mean', geom = 'line', aes(group = region)) +
  stat_summary(fun.data = 'mean_se', geom = 'errorbar', aes(group = region), width = 0) +
  theme_ag01() +
  scale_color_manual(values = color_values_regions) +
  theme(axis.text.x = element_blank())+
  facet_grid(set_id~., scales = 'free') +
  coord_cartesian(xlim = c(0.5, 5.5), ylim = c(-2, 3), clip = 'off', expand = 0) +
  force_panelsizes(rows = unit(2,'cm'), cols = unit(1.5, 'cm')) +
  ylab('Z-score sustained (2-3 s)') +
  xlab('')



save_pdf(dir_output_fp_lha, str_c(fn_stem, '.pdf'), 6, 6)
plt_data %>% write_csv(str_c(dir_output_fp_lha, fn_stem, '_data.csv'))

plt_data %>%
  filter(region %in% c('LHA:GABA', 'LHA:Glut')) %>%
  aov_rm_two_within(dir_output_fp_lha,str_c(fn_stem,'_interaction'), 'subject','zscore_blsub_mean','region', 'solution')


plt_data %>%
  filter(region == 'LHA:GABA') %>%
  aov_rm_one_within(dir_output_fp_lha,str_c(fn_stem,'_gaba'), 'subject','zscore_blsub_mean','solution')

plt_data %>%
  filter(region == 'LHA:Glut') %>%
  aov_rm_one_within(dir_output_fp_lha,str_c(fn_stem,'_glut'), 'subject','zscore_blsub_mean','solution')

plt_data %>%
  filter(region == 'LHA:Ratio') %>%
  aov_rm_one_within(dir_output_fp_lha,str_c(fn_stem,'_ratio'), 'subject','zscore_blsub_mean','solution')
```


#### wr nacl
```{r}
fn_stem <- 'fp_lha_summary_wrnacl'

plt_data <- df %>%
  filter(set_id == 'WR:NaCl') %>%
  filter(time_bin == 'sustained') 


plt_data %>%
  ggplot(aes(solution, zscore_blsub_mean, color = region)) +
  #geom_line(aes(group = interaction(region, subject)), alpha = 1/3) +
  geom_hline(yintercept = 0, size = 1/4, color = 'darkgrey') +
  stat_summary(fun = 'mean', geom = 'line', aes(group = region)) +
  stat_summary(fun.data = 'mean_se', geom = 'errorbar', aes(group = region), width = 0) +
  theme_ag01() +
  scale_color_manual(values = color_values_regions) +
  theme(axis.text.x = element_blank())+
  facet_grid(set_id~., scales = 'free') +
  coord_cartesian(xlim = c(0.5, 5.5), ylim = c(-2, 3), clip = 'off', expand = 0) +
  force_panelsizes(rows = unit(2,'cm'), cols = unit(1.5, 'cm')) +
  ylab('Z-score sustained (2-3 s)') +
  xlab('')


save_pdf(dir_output_fp_lha, str_c(fn_stem, '.pdf'), 6, 6)
plt_data %>% write_csv(str_c(dir_output_fp_lha, fn_stem, '_data.csv'))

plt_data %>%
  filter(region %in% c('LHA:GABA', 'LHA:Glut')) %>%
  aov_rm_two_within(dir_output_fp_lha,str_c(fn_stem,'_interaction'), 'subject','zscore_blsub_mean','region', 'solution')


plt_data %>%
  filter(region == 'LHA:GABA') %>%
  aov_rm_one_within(dir_output_fp_lha,str_c(fn_stem,'_gaba'), 'subject','zscore_blsub_mean','solution')

plt_data %>%
  filter(region == 'LHA:Glut') %>%
  aov_rm_one_within(dir_output_fp_lha,str_c(fn_stem,'_glut'), 'subject','zscore_blsub_mean','solution')

plt_data %>%
  filter(region == 'LHA:Ratio') %>%
  aov_rm_one_within(dir_output_fp_lha,str_c(fn_stem,'_ratio'), 'subject','zscore_blsub_mean','solution')

```

#### range
```{r}
fn_stem <- 'fp_lha_range'

plt_data <-  df %>%
  filter(time_bin == 'sustained') %>%
  select(set_id, subject, region, solution, zscore_blsub_mean) %>%
  mutate(solution_magnitude = case_when(
    solution %in% c('sucrose00', 'nacl000') ~ 'low',
    solution %in% c('sucrose30', 'nacl150') ~ 'high'
  )) %>%
  filter(!is.na(solution_magnitude) ) %>%
  select(-solution) %>%
  spread(solution_magnitude, zscore_blsub_mean) %>%
  mutate(range = high - low) 


plt_data %>%
  ggplot(aes(set_id, abs(range), fill = region, color = region)) +
  stat_summary(fun.data = 'mean_se', geom = 'errorbar', position = position_dodge(width = 0.7), width = 0.4) +
  stat_summary(fun = 'mean', geom = 'col', position = position_dodge(width = 0.7), width = 0.6) +
  geom_jitter(position = position_jitterdodge(jitter.width = 0.3, dodge.width = 0.7), shape = 21, color = 'white', stroke = 0.25, size = 2) +
  theme_ag01() +
  scale_color_manual(values = color_values_regions) +
  scale_fill_manual(values = color_values_regions) +
  ylab('|Range FP Z-Score|') +
  xlab('') +
  coord_cartesian(xlim = c(0.5, 3.5), ylim = c(0, 5), clip = 'off', expand = 0) +
  force_panelsizes(rows = unit(3,'cm'), cols = unit(6, 'cm')) 

save_pdf(dir_output_fp_lha, str_c(fn_stem, '.pdf'), 6, 6)
plt_data %>% write_csv(str_c(dir_output_fp_lha, fn_stem, '_data.csv'))

stats_list <- plt_data %>%
  aov_rm_two_within(dir_output_fp_lha,fn_stem,'subject','range','region','set_id')



```

```{r}
plt_data %>%
  filter(region == 'LHA:GABA') %>%
  aov_rm_one_within(dir_output_fp_lha,str_c(fn_stem, 'lhagaba'),'subject','range','set_id')

plt_data %>%
  filter(region == 'LHA:Glut') %>%
  aov_rm_one_within(dir_output_fp_lha,str_c(fn_stem, 'lhaglut'),'subject','range','set_id')

plt_data %>%
  filter(region == 'LHA:Ratio') %>%
  aov_rm_one_within(dir_output_fp_lha,str_c(fn_stem, 'lhaglut'),'subject','range','set_id')
```



```{r}
stats_list[[3]] %>%
  select(starts_with('contrast'), p_value, sig_symbol) %>%
  filter(contrast1_within1 == contrast2_within1)


stats_list[[3]] %>%
  select(starts_with('contrast'), p_value, sig_symbol) %>%
  filter(contrast1_within2 == contrast2_within2)


```

#### corr range vs licking
```{r}
fn_stem <- 'fp_lha_cor_range_vs_licking'

# fp data
plt_data <-  df %>%
  filter(time_bin == 'sustained') %>%
  select(set_id, subject, region, solution, zscore_blsub_mean) %>%
  mutate(solution_magnitude = case_when(
    solution %in% c('sucrose00', 'nacl000') ~ 'low',
    solution %in% c('sucrose30', 'nacl150') ~ 'high'
  )) %>%
  filter(!is.na(solution_magnitude) ) %>%
  select(-solution) %>%
  spread(solution_magnitude, zscore_blsub_mean) %>%
  mutate(range = high - low) 

# licking data
process_blocknames <- log_analysis_fp %>%
  filter(procedure %>% str_detect('multi')) %>%
  filter(subject %in% unique(plt_data$subject)) %>%
  pull(blockname)

df_spout_summary_combined <- combine_session_files(process_blocknames, dir_localdata_sessions, '_data_spout_summary.csv')

join_info <- log_analysis_fp %>% 
  get_set_id() %>% 
  select(blockname, experiment, subject, set_id)

df_spout_summary_combined <- df_spout_summary_combined %>%
  left_join(join_info) %>%
  group_by(experiment, subject, set_id, solution) %>%
  summarise(lick_count_trial_mean = mean(lick_count_trial_mean), 
            trial_lick_proportion = mean(trial_lick_proportion)) %>%
  format_set_id(key_set_id)

df_spout_summary_combined <- df_spout_summary_combined %>%
  select(set_id, subject, solution, lick_count_trial_mean) %>%
  mutate(solution_magnitude = case_when(
    solution %in% c('sucrose00', 'nacl000') ~ 'low',
    solution %in% c('sucrose30', 'nacl150') ~ 'high'
  )) %>%
  filter(!is.na(solution_magnitude) ) %>%
  select(-solution) %>%
  spread(solution_magnitude, lick_count_trial_mean) %>%
  mutate(range_lick = high - low) %>%
  select(-high, -low)

plt_data <- plt_data %>%
  left_join(df_spout_summary_combined)
```

```{r}
fn_stem <- 'fp_lha_rangelick_vs_rangefp'

plt_data %>%
  ggplot(aes(abs(range_lick), abs(range), color = set_id)) +
  geom_point() + 
  facet_grid(.~region, scales = 'free') +
  geom_smooth(method = 'lm', size = 0.3, alpha = 1/5, aes( group = 1), color = 'black') +
  stat_cor(method = "pearson", size = 1.5, aes( group = 1), color = 'black') +
  theme_ag01() +
  scale_color_manual(values = color_values_experiment_set) +
  scale_fill_manual(values = color_values_experiment_set) +
  ylab('|Range FP Z-Score|') +
  xlab('|Range Consumption|') +
  coord_cartesian(xlim = c(0, 30), ylim = c(0, 6), clip = 'off', expand = 0) +
  force_panelsizes(rows = unit(3,'cm'), cols = unit(1.5, 'cm')) +
  theme(panel.spacing = unit(1, "lines"))

save_pdf(dir_output_fp_lha, str_c(fn_stem, '.pdf'), 6, 6)
plt_data %>% write_csv(str_c(dir_output_fp_lha, fn_stem, '_data.csv'))

```



### summary - post
```{r}
fns <- list.files(dir_output)
fns_filt <- fns[fns %>% str_detect('filtlick')]
fns_filt <- fns_filt[fns_filt %>% str_detect('peth_summary_means_subject')]
fns_filt <- fns_filt %>% str_remove('.csv')

df <- combined_import(import_directory = dir_output, 
                filter_strings = fns_filt,
                prefixes = NA,
                suffixes = c('.csv'),
                verbose = 0
                )[[1]] %>% 
  filt_and_format_data() %>%  
  mutate(region_facet = case_when(
    region == 'LHA:Ratio' ~ 2,
    region == 'LHA:GABA' ~ 1,
    region == 'LHA:Glut' ~ 1
  )) 
```

#### wr suc

```{r}
fn_stem <- 'fp_lha_summary_wrsuc_post'

plt_data <- df %>%
  filter(set_id == 'WR:Suc') %>%
  filter(time_bin == 'post') 


plt_data %>%
  ggplot(aes(solution, zscore_blsub_mean, color = region)) +
  #geom_line(aes(group = interaction(region, subject)), alpha = 1/3) +
  geom_hline(yintercept = 0, size = 1/4, color = 'darkgrey') +
  stat_summary(fun = 'mean', geom = 'line', aes(group = region)) +
  stat_summary(fun.data = 'mean_se', geom = 'errorbar', aes(group = region), width = 0) +
  theme_ag01() +
  scale_color_manual(values = color_values_regions) +
  theme(axis.text.x = element_blank())+
  facet_grid(set_id~., scales = 'free') +
  coord_cartesian(xlim = c(0.5, 5.5), ylim = c(-0.5, 1), clip = 'off', expand = 0) +
  force_panelsizes(rows = unit(2,'cm'), cols = unit(1.5, 'cm')) +
  ylab('Z-score post (6-8 s)') +
  xlab('')



save_pdf(dir_output_fp_lha, str_c(fn_stem, '.pdf'), 6, 6)
plt_data %>% write_csv(str_c(dir_output_fp_lha, fn_stem, '_data.csv'))

plt_data %>%
  filter(region %in% c('LHA:GABA', 'LHA:Glut')) %>%
  aov_rm_two_within(dir_output_fp_lha,str_c(fn_stem,'_interaction'), 'subject','zscore_blsub_mean','region', 'solution')


plt_data %>%
  filter(region == 'LHA:GABA') %>%
  aov_rm_one_within(dir_output_fp_lha,str_c(fn_stem,'_gaba'), 'subject','zscore_blsub_mean','solution')

plt_data %>%
  filter(region == 'LHA:Glut') %>%
  aov_rm_one_within(dir_output_fp_lha,str_c(fn_stem,'_glut'), 'subject','zscore_blsub_mean','solution')

plt_data %>%
  filter(region == 'LHA:Ratio') %>%
  aov_rm_one_within(dir_output_fp_lha,str_c(fn_stem,'_ratio'), 'subject','zscore_blsub_mean','solution')

```

#### fr suc
```{r}
fn_stem <- 'fp_lha_summary_frsuc_post'

plt_data <- df %>%
  filter(set_id == 'FR:Suc') %>%
  filter(time_bin == 'post') 


plt_data %>%
  ggplot(aes(solution, zscore_blsub_mean, color = region)) +
  #geom_line(aes(group = interaction(region, subject)), alpha = 1/3) +
  geom_hline(yintercept = 0, size = 1/4, color = 'darkgrey') +
  stat_summary(fun = 'mean', geom = 'line', aes(group = region)) +
  stat_summary(fun.data = 'mean_se', geom = 'errorbar', aes(group = region), width = 0) +
  theme_ag01() +
  scale_color_manual(values = color_values_regions) +
  theme(axis.text.x = element_blank())+
  facet_grid(set_id~., scales = 'free') +
  coord_cartesian(xlim = c(0.5, 5.5), ylim = c(-0.5, 1), clip = 'off', expand = 0) +
  force_panelsizes(rows = unit(2,'cm'), cols = unit(1.5, 'cm')) +
  ylab('Z-score post (6-8 s)') +
  xlab('')



save_pdf(dir_output_fp_lha, str_c(fn_stem, '.pdf'), 6, 6)
plt_data %>% write_csv(str_c(dir_output_fp_lha, fn_stem, '_data.csv'))

plt_data %>%
  filter(region %in% c('LHA:GABA', 'LHA:Glut')) %>%
  aov_rm_two_within(dir_output_fp_lha,str_c(fn_stem,'_interaction'), 'subject','zscore_blsub_mean','region', 'solution')


plt_data %>%
  filter(region == 'LHA:GABA') %>%
  aov_rm_one_within(dir_output_fp_lha,str_c(fn_stem,'_gaba'), 'subject','zscore_blsub_mean','solution')

plt_data %>%
  filter(region == 'LHA:Glut') %>%
  aov_rm_one_within(dir_output_fp_lha,str_c(fn_stem,'_glut'), 'subject','zscore_blsub_mean','solution')

plt_data %>%
  filter(region == 'LHA:Ratio') %>%
  aov_rm_one_within(dir_output_fp_lha,str_c(fn_stem,'_ratio'), 'subject','zscore_blsub_mean','solution')
```


#### wr nacl
```{r}
fn_stem <- 'fp_lha_summary_wrnacl_post'

plt_data <- df %>%
  filter(set_id == 'WR:NaCl') %>%
  filter(time_bin == 'post') 


plt_data %>%
  ggplot(aes(solution, zscore_blsub_mean, color = region)) +
  #geom_line(aes(group = interaction(region, subject)), alpha = 1/3) +
  geom_hline(yintercept = 0, size = 1/4, color = 'darkgrey') +
  stat_summary(fun = 'mean', geom = 'line', aes(group = region)) +
  stat_summary(fun.data = 'mean_se', geom = 'errorbar', aes(group = region), width = 0) +
  theme_ag01() +
  scale_color_manual(values = color_values_regions) +
  theme(axis.text.x = element_blank())+
  facet_grid(set_id~., scales = 'free') +
  coord_cartesian(xlim = c(0.5, 5.5), ylim = c(-0.5, 1), clip = 'off', expand = 0) +
  force_panelsizes(rows = unit(2,'cm'), cols = unit(1.5, 'cm')) +
  ylab('Z-score post (6-8 s)') +
  xlab('')



save_pdf(dir_output_fp_lha, str_c(fn_stem, '.pdf'), 6, 6)
plt_data %>% write_csv(str_c(dir_output_fp_lha, fn_stem, '_data.csv'))

plt_data %>%
  filter(region %in% c('LHA:GABA', 'LHA:Glut')) %>%
  aov_rm_two_within(dir_output_fp_lha,str_c(fn_stem,'_interaction'), 'subject','zscore_blsub_mean','region', 'solution')

plt_data %>%
  filter(region == 'LHA:GABA') %>%
  aov_rm_one_within(dir_output_fp_lha,str_c(fn_stem,'_gaba'), 'subject','zscore_blsub_mean','solution')

plt_data %>%
  filter(region == 'LHA:Glut') %>%
  aov_rm_one_within(dir_output_fp_lha,str_c(fn_stem,'_glut'), 'subject','zscore_blsub_mean','solution')

plt_data %>%
  filter(region == 'LHA:Ratio') %>%
  aov_rm_one_within(dir_output_fp_lha,str_c(fn_stem,'_ratio'), 'subject','zscore_blsub_mean','solution')

```

```{r}
first_loop <- 1

for(loop_set_id in sort(unique(plt_data$set_id))){
  
  df_set <- plt_data %>%
    filter(set_id == loop_set_id)
  
  for(loop_region in sort(unique(df_set$region))){
    for(loop_time_bin in sort(unique(df_set$time_bin))) {
      
      stats_results <- df_set %>%
        filter(region == loop_region) %>%
        filter(time_bin == loop_time_bin) %>%
        aov_rm_one_within(NA,NA,'subject','zscore_blsub_mean','solution')
      
      
      stats_results[[2]]  <- stats_results[[2]] %>%
          mutate(set_id = loop_set_id,
                 region = loop_region,
                 time_bin = loop_time_bin) %>%
          select(set_id, region, time_bin, everything())
      
      stats_results[[3]] <- stats_results[[3]] %>%
          mutate(set_id = loop_set_id,
                 region = loop_region,
                 time_bin = loop_time_bin) %>%
          select(set_id, region, time_bin, everything())
      
      if(first_loop){
        combined_aov <- stats_results[[2]] 
        combined_ph <- stats_results[[3]]
        first_loop <- 0
      } else {
        combined_aov <- stats_results[[2]] %>%
          bind_rows(combined_aov,.)
        combined_ph <- stats_results[[3]]%>%
          bind_rows(combined_ph,.)
        
      }
      
      
    }
  }
}

combined_aov %>%
  mutate(region = region %>% factor(levels = key_regions$region_label %>% unique())) %>%
  filter(time_bin != 'baseline') %>%
  filter(effect == 'solution') %>%
  select(set_id, region, time_bin, sig_symbol) %>%
  filter(sig_symbol != 'n.s.') %>%
  ggplot(aes(region, set_id, label = sig_symbol)) +
  geom_text() +
  theme(axis.text.x = element_text(angle = 90, hjust = 1, vjust = 0.3)) +
  facet_grid(time_bin~.)

plt_data %>%
  filter(!subject %>% str_detect('abw')) %>%
  select(set_id, region, subject) %>%
  unique() %>%
  group_by(set_id, region) %>%
  filter(!region %in% c('LHA:GABA', 'LHA:Glut')) %>%
  summarise(fiber_count = n()) 

```



### corr lick vs resp
```{r}
fns <- list.files(dir_output)
fns_filt <- fns[fns %>% str_detect('peth_summary_means_trial_triallick')]
fns_filt <- fns_filt %>% str_remove('.csv')

df <- combined_import(import_directory = dir_output, 
                filter_strings = fns_filt,
                prefixes = NA,
                suffixes = c('.csv'),
                verbose = 0
                )[[1]] %>% 
  filt_and_format_data() %>%  
  mutate(region_facet = case_when(
    region == 'LHA:Ratio' ~ 2,
    region == 'LHA:GABA' ~ 1,
    region == 'LHA:Glut' ~ 1
  )) %>%
  filter(trial_lick == 1)
```


```{r, fig.width = 9, fig.height = 6}

fn_stem <- 'fp_lha_cor_zscore_vs_lick'

df %>%
  filter(time_bin == 'sustained') %>%
  ggplot(aes(zscore_blsub_mean, lick_count)) +
  geom_jitter(size = 0.1, alpha = 1/8) +
  geom_smooth(method = 'lm', size = 0.3, alpha = 1/5, color = 'black') +
  stat_cor(method = "pearson", label.y = 30, label.x = 0, size = 2) +
  facet_grid(set_id~region) +
  theme_ag01() +
  coord_cartesian(xlim = c(-6,12), ylim = c(0,30), expand = F, clip = 'off') +
  scale_x_continuous(breaks = seq(-6,12,6)) +
  theme(strip.text = element_text(margin = margin(t = 5, r = 5, b = 5, l = 5))) +
  theme(panel.spacing = unit(1, "lines")) +
  force_panelsizes(rows = unit(2,'cm'), cols = unit(4, 'cm'))


save_pdf(dir_output_fp_lha, str_c(fn_stem, '.pdf'), 6, 6)
plt_data %>% write_csv(str_c(dir_output_fp_lha, fn_stem, '_data.csv'))
```

```{r}
corr_sbj <- df %>%
  filter(trial_lick == 1) %>%
  filter(time_bin == 'sustained') %>%
  tidy_cor('zscore_blsub_mean', 'lick_count', 'subject', 'region', 'set_id') %>%
  mutate(estimate_squared = estimate^2)


fn_stem <- 'fp_lha_cor_zscore_vs_lick_subject_summary_wrsuc' #~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~

plt_data <- corr_sbj %>%
  filter(set_id == 'WR:Suc') 

plt_data %>%
  ggplot(aes(region, estimate_squared)) +
  geom_hline(yintercept = 0, color = 'darkgrey', size = 0.25) +
  geom_line(aes(group = subject), alpha = 1/3) +
  stat_summary(fun = 'mean', geom = 'line', aes(group = set_id)) +
  stat_summary(fun.data = 'mean_se', geom = 'errorbar', aes(group = set_id), width = 0) +
  theme_ag01() +
  coord_cartesian(xlim = c(0.5,3.5), ylim = c(0,0.3), expand = F, clip = 'off') +
  scale_y_continuous(breaks = seq(0,0.3,0.1)) +
  facet_grid(set_id~., scales = 'free')+
  theme(axis.text.x = element_text(angle = 90, hjust = 1, vjust = 0.3)) +
  theme(strip.text = element_text(margin = margin(t = 5, r = 5, b = 5, l = 5))) +
  theme(panel.spacing = unit(1, "lines")) +
  force_panelsizes(rows = unit(2,'cm'), cols = unit(2, 'cm'))
 
save_pdf(dir_output_fp_lha, str_c(fn_stem, '.pdf'), 6, 6)
plt_data %>% write_csv(str_c(dir_output_fp_lha, fn_stem, '_data.csv'))
plt_data %>% aov_rm_one_within(dir_output_fp_lha,fn_stem,'subject','estimate_squared', 'region')

fn_stem <- 'fp_lha_cor_zscore_vs_lick_subject_summary_frsuc' #~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~

plt_data <- corr_sbj %>%
  filter(set_id == 'FR:Suc')

plt_data %>%
  ggplot(aes(region, estimate_squared)) +
  geom_hline(yintercept = 0, color = 'darkgrey', size = 0.25) +
  geom_line(aes(group = subject), alpha = 1/3) +
  stat_summary(fun = 'mean', geom = 'line', aes(group = set_id)) +
  stat_summary(fun.data = 'mean_se', geom = 'errorbar', aes(group = set_id), width = 0) +
  theme_ag01() +
  coord_cartesian(xlim = c(0.5,3.5), ylim = c(0,0.6), expand = F, clip = 'off') +
  scale_y_continuous(breaks = seq(0,0.6,0.2)) +
  facet_grid(set_id~., scales = 'free')+
  theme(axis.text.x = element_text(angle = 90, hjust = 1, vjust = 0.3)) +
  theme(strip.text = element_text(margin = margin(t = 5, r = 5, b = 5, l = 5))) +
  theme(panel.spacing = unit(1, "lines")) +
  force_panelsizes(rows = unit(2,'cm'), cols = unit(2, 'cm'))

save_pdf(dir_output_fp_lha, str_c(fn_stem, '.pdf'), 6, 6)
plt_data %>% write_csv(str_c(dir_output_fp_lha, fn_stem, '_data.csv'))
plt_data %>% aov_rm_one_within(dir_output_fp_lha,fn_stem,'subject','estimate_squared', 'region')

fn_stem <- 'fp_lha_cor_zscore_vs_lick_subject_summary_wrnacl' #~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~

plt_data <- corr_sbj %>%
  filter(set_id == 'WR:NaCl')

plt_data %>%
  ggplot(aes(region, estimate_squared)) +
  geom_hline(yintercept = 0, color = 'darkgrey', size = 0.25) +
  geom_line(aes(group = subject), alpha = 1/3) +
  stat_summary(fun = 'mean', geom = 'line', aes(group = set_id)) +
  stat_summary(fun.data = 'mean_se', geom = 'errorbar', aes(group = set_id), width = 0) +
  theme_ag01() +
  coord_cartesian(xlim = c(0.5,3.5), ylim = c(0,0.8), expand = F, clip = 'off') +
  scale_y_continuous(breaks = seq(0,0.8,0.2)) +
  facet_grid(set_id~., scales = 'free')+
  theme(axis.text.x = element_text(angle = 90, hjust = 1, vjust = 0.3)) +
  theme(strip.text = element_text(margin = margin(t = 5, r = 5, b = 5, l = 5))) +
  theme(panel.spacing = unit(1, "lines")) +
  force_panelsizes(rows = unit(2,'cm'), cols = unit(2, 'cm'))

save_pdf(dir_output_fp_lha, str_c(fn_stem, '.pdf'), 6, 6)
plt_data %>% write_csv(str_c(dir_output_fp_lha, fn_stem, '_data.csv'))
plt_data %>% aov_rm_one_within(dir_output_fp_lha,fn_stem,'subject','estimate_squared', 'region')
```

```{r}
corr_sbj %>%
  filter(set_id == 'WR:Suc') %>%
  aov_rm_one_within(NA,NA,'subject','estimate_squared', 'region')

corr_sbj %>%
  filter(set_id == 'FR:Suc') %>%
  aov_rm_one_within(NA,NA,'subject','estimate_squared', 'region')

corr_sbj %>%
  filter(set_id == 'WR:NaCl') %>%
  aov_rm_one_within(NA,NA,'subject','estimate_squared', 'region')
```



```{r}
breakhereplease
```


## str
```{r}
dir_output_fp_str <- './analysis_output/peth_str/'

filt_and_format_data <- function(df){
  
  df %>% 
    filter(!region %>% str_detect('LHA')) %>%
    filter(set_id %in% c('frsuc', 'wrsuc', 'wrnacl')) %>%
    mutate(region = region %>% factor(levels = unique(key_regions$region_label))) %>%
    format_set_id(key_set_id) 
  
}

fns <- list.files(dir_output)
fns_filt <- fns[fns %>% str_detect('filtlick')]
fns_filt <- fns_filt[fns_filt %>% str_detect('peth_summary_trace_overal')]
fns_filt <- fns_filt[fns_filt != 'filtlick_peth_summary_trace_overall.csv']
fns_filt <- fns_filt %>% str_remove('.csv')

df <- combined_import(import_directory = dir_output, 
                filter_strings = fns_filt,
                prefixes = NA,
                suffixes = c('.csv'),
                verbose = 0
                )[[1]]

plt_data <- df %>% 
  filt_and_format_data()

```


### trace 
```{r, fig.width = 12, fig.height = 5}
fn_stem <- 'fp_str_trace'

plt <- plt_data %>%
  ggplot(aes(time_rel, zscore_blsub_mean, group = solution, color = solution, fill = solution)) +
  annotate("rect", xmin = 0, xmax = 3, ymin = -Inf, ymax = Inf, alpha = 1/3, fill = "darkgrey") +
  geom_hline(yintercept = 0, color = 'darkgrey', size = 0.5) +
  geom_ribbon(
    aes(
      ymin = zscore_blsub_mean - zscore_blsub_sem,
      ymax
      = zscore_blsub_mean + zscore_blsub_sem
        ),
    alpha = 1/3,
    color = NA
    ) +
  geom_line() +
  facet_grid(set_id~region) +
  scale_color_manual(values = c(color_values_nacl, color_values_suc)) +
  scale_fill_manual(values = c(color_values_nacl, color_values_suc)) +
  theme_ag01() +
  theme(strip.text = element_text(margin = margin(t = 5, r = 5, b = 5, l = 5))) +
  theme(panel.spacing.y = unit(0.5, "lines")) +
  force_panelsizes(rows = unit(2, 'cm'), cols = unit(2.3, 'cm'))


plt <- plt %>%
  add_scale_bar(
    origin = c(-3, -1), 
    x_len = 1, 
    y_len = 1
  )

plt

save_pdf(dir_output_fp_str, str_c(fn_stem, '.pdf'), 9, 4)
plt_data %>% write_csv(str_c(dir_output_fp_str, fn_stem, '_data.csv'))
```


### summary
```{r}
fns <- list.files(dir_output)
fns_filt <- fns[fns %>% str_detect('filtlick')]
fns_filt <- fns_filt[fns_filt %>% str_detect('peth_summary_means_subject')]
fns_filt <- fns_filt %>% str_remove('.csv')

df <- combined_import(import_directory = dir_output, 
                filter_strings = fns_filt,
                prefixes = NA,
                suffixes = c('.csv'),
                verbose = 0
                )[[1]] %>% 
  filt_and_format_data() 
```

#### combined stats - sustained
```{r}
stats_data <- df %>%
  filter(time_bin == 'sustained') 

set_ids <- stats_data$set_id %>% unique()
regions <- stats_data$region %>% unique()

first_loop <- 1

for(loop_set_id in set_ids){
  for(loop_region in regions){
    stats_list <- stats_data %>%
      filter(
        set_id == loop_set_id,
        region == loop_region
      ) %>%
      aov_rm_one_within(NA,NA, 'subject','zscore_blsub_mean','solution')
    
    
    stats_list[[2]] <- stats_list[[2]] %>% 
      mutate(set_id = loop_set_id, region = loop_region) %>%
      select(set_id, region, everything())
    
    stats_list[[3]] <- stats_list[[3]] %>% 
      mutate(set_id = loop_set_id, region = loop_region) %>%
      select(set_id, region, everything())
    
    if(first_loop == 1){
      combined_aov <- stats_list[[2]]
      combined_hsd <- stats_list[[3]]
      first_loop <- 0
    } else {
      combined_aov <- stats_list[[2]] %>% bind_rows(combined_aov,.)
      combined_hsd <- stats_list[[3]] %>% bind_rows(combined_hsd,.)
      }
    
  }
}

combined_aov %>%
  write_csv(str_c(dir_output_fp_str, 'fp_str_summary_sustained_combined_stats_aov.csv'))

combined_hsd %>%
  write_csv(str_c(dir_output_fp_str, 'fp_str_summary_sustained_combined_stats_hsd.csv'))
```

```{r}
combined_aov %>%
  mutate(region = factor(region, levels = key_regions$region_label %>% unique())) %>%
  filter(effect == 'solution') %>%
  select(set_id, region, p_value) %>%
  quick_sig() %>%
  ggplot(aes(region, set_id, label = sig_symbol)) +
  geom_text()
```


```{r}
stats_data <- df %>%
  filter(set_id %in% c('WR:Suc', 'FR:Suc')) %>%
  filter(time_bin == 'sustained') 

regions <- stats_data$region %>% unique()

first_loop <- 1

for(loop_region in regions){
  
  stats_list <- stats_data %>%
    filter(
      region == loop_region
    ) %>%
    aov_rm_two_within(NA,NA, 'subject','zscore_blsub_mean','solution', 'set_id')
  
  
  stats_list[[2]] <- stats_list[[2]] %>% 
    mutate(region = loop_region) %>%
    select(region, everything())
  
  stats_list[[3]] <- stats_list[[3]] %>% 
    mutate(region = loop_region) %>%
    select(region, everything())
  
  if(first_loop == 1){
    combined_aov <- stats_list[[2]]
    combined_hsd <- stats_list[[3]]
    first_loop <- 0
  } else {
    combined_aov <- stats_list[[2]] %>% bind_rows(combined_aov,.)
    combined_hsd <- stats_list[[3]] %>% bind_rows(combined_hsd,.)
  }
  
}

combined_aov %>%
  write_csv(str_c(dir_output_fp_str, 'fp_str_summary_sustained_combined_interaction_stats_aov.csv'))

combined_hsd %>%
  write_csv(str_c(dir_output_fp_str, 'fp_str_summary_sustained_combined_interaction_stats_stats_hsd.csv'))
```


```{r}
combined_aov %>%
  mutate(region = factor(region, levels = key_regions$region_label %>% unique())) %>%
  filter(effect == 'solution*set_id') %>%
  select(region, p_value) %>%
  quick_sig() %>%
  ggplot(aes(region, 1, label = sig_symbol)) +
  geom_text()
```


#### combined stats - post
```{r}
stats_data <- df %>%
  filter(time_bin == 'post') 

set_ids <- stats_data$set_id %>% unique()
regions <- stats_data$region %>% unique()

first_loop <- 1

for(loop_set_id in set_ids){
  for(loop_region in regions){
    stats_list <- stats_data %>%
      filter(
        set_id == loop_set_id,
        region == loop_region
      ) %>%
      aov_rm_one_within(NA,NA, 'subject','zscore_blsub_mean','solution')
    
    
    stats_list[[2]] <- stats_list[[2]] %>% 
      mutate(set_id = loop_set_id, region = loop_region) %>%
      select(set_id, region, everything())
    
    stats_list[[3]] <- stats_list[[3]] %>% 
      mutate(set_id = loop_set_id, region = loop_region) %>%
      select(set_id, region, everything())
    
    if(first_loop == 1){
      combined_aov <- stats_list[[2]]
      combined_hsd <- stats_list[[3]]
      first_loop <- 0
    } else {
      combined_aov <- stats_list[[2]] %>% bind_rows(combined_aov,.)
      combined_hsd <- stats_list[[3]] %>% bind_rows(combined_hsd,.)
      }
    
  }
}

combined_aov %>%
  write_csv(str_c(dir_output_fp_str, 'fp_str_summary_post_combined_stats_aov.csv'))

combined_hsd %>%
  write_csv(str_c(dir_output_fp_str, 'fp_str_summary_post_combined_stats_hsd.csv'))

df$time_bin %>% unique()
```

```{r}
combined_aov %>%
  mutate(region = factor(region, levels = key_regions$region_label %>% unique())) %>%
  filter(effect == 'solution') %>%
  select(set_id, region, p_value) %>%
  quick_sig() %>%
  ggplot(aes(region, set_id, label = sig_symbol)) +
  geom_text()
```


```{r}
stats_data <- df %>%
  filter(set_id %in% c('WR:Suc', 'FR:Suc')) %>%
  filter(time_bin == 'post') 

regions <- stats_data$region %>% unique()

first_loop <- 1

for(loop_region in regions){
  
  stats_list <- stats_data %>%
    filter(
      region == loop_region
    ) %>%
    aov_rm_two_within(NA,NA, 'subject','zscore_blsub_mean','solution', 'set_id')
  
  
  stats_list[[2]] <- stats_list[[2]] %>% 
    mutate(region = loop_region) %>%
    select(region, everything())
  
  stats_list[[3]] <- stats_list[[3]] %>% 
    mutate(region = loop_region) %>%
    select(region, everything())
  
  if(first_loop == 1){
    combined_aov <- stats_list[[2]]
    combined_hsd <- stats_list[[3]]
    first_loop <- 0
  } else {
    combined_aov <- stats_list[[2]] %>% bind_rows(combined_aov,.)
    combined_hsd <- stats_list[[3]] %>% bind_rows(combined_hsd,.)
  }
  
}

combined_aov %>%
  write_csv(str_c(dir_output_fp_str, 'fp_str_summary_post_combined_interaction_stats_aov.csv'))

combined_hsd %>%
  write_csv(str_c(dir_output_fp_str, 'fp_str_summary_post_combined_interaction_stats_hsd.csv'))
```


```{r}
combined_aov %>%
  mutate(region = factor(region, levels = key_regions$region_label %>% unique())) %>%
  filter(effect == 'solution*set_id') %>%
  select(region, p_value) %>%
  quick_sig() %>%
  ggplot(aes(region, 1, label = sig_symbol)) +
  geom_text()
```

#### combined plot
```{r}

```

#### combined subject
```{r, fig.height = 9, fig.width = 12}
fn_stem <- 'fp_str_summary_combined_subject'

plt_data <- df %>%
  filter(time_bin %in% c('sustained', 'post')) %>%
  mutate(time_bin = factor(time_bin, levels = c('sustained', 'post')))

plt_data %>%
  left_join(join_solution_x) %>%
  ggplot(aes(plt_x, zscore_blsub_mean, color = set_id)) +
  geom_line(aes(group = interaction(region, subject)), alpha = 1/4) +
  geom_hline(yintercept = 0, size = 1/4, color = 'darkgrey') +
  stat_summary(fun = 'mean', geom = 'line', aes(group = set_id)) +
  stat_summary(fun.data = 'mean_se', geom = 'errorbar', aes(group = set_id), width = 0) +
  theme_ag01() +
  scale_color_manual(values = color_values_experiment_set) +
  theme(axis.text.x = element_blank())+
  facet_grid(interaction(set_id, time_bin)~region, scales = 'free') +
  #facet_wrap(.~interaction(region, set_id, time_bin), scales = 'free', nrow = 6) +
  #coord_cartesian(xlim = c(0.5, 5.5), ylim = c(-1, 3), clip = 'off', expand = 0) +
  force_panelsizes(rows = unit(2,'cm'), cols = unit(1, 'cm')) +
  #theme(strip.text.x = element_blank()) +
  ylab('Z-score sustained (2-3 s)') +
  xlab('')

save_pdf(dir_output_fp_str, str_c(fn_stem, '.pdf'), 6, 6)
plt_data %>% write_csv(str_c(dir_output_fp_str, fn_stem, '_data.csv'))

```


#### combined sustained
```{r}
fn_stem <- 'fp_str_summary_combined_sustained'

plt_data <- df %>%
  filter(time_bin == 'sustained') 

plt_data %>%
  left_join(join_solution_x) %>%
  ggplot(aes(plt_x, zscore_blsub_mean, color = set_id)) +
  #geom_line(aes(group = interaction(region, subject)), alpha = 1/3) +
  geom_hline(yintercept = 0, size = 1/4, color = 'darkgrey') +
  stat_summary(fun = 'mean', geom = 'line', aes(group = set_id)) +
  stat_summary(fun.data = 'mean_se', geom = 'errorbar', aes(group = set_id), width = 0) +
  theme_ag01() +
  scale_color_manual(values = color_values_experiment_set) +
  theme(axis.text.x = element_blank())+
  facet_grid(.~region, scales = 'free') +
  coord_cartesian(xlim = c(0.5, 5.5), ylim = c(-2, 6), clip = 'off', expand = 0) +
  force_panelsizes(rows = unit(2,'cm'), cols = unit(1.5, 'cm')) +
  theme(strip.text = element_blank()) +
  ylab('Z-score sustained (2-3 s)') +
  xlab('')

save_pdf(dir_output_fp_str, str_c(fn_stem, '.pdf'), 6, 6)
plt_data %>% write_csv(str_c(dir_output_fp_str, fn_stem, '_data.csv'))

```




#### combined post
```{r}
fn_stem <- 'fp_str_summary_combined_post'

plt_data <- df %>%
  filter(time_bin == 'post') 

plt_data %>%
  left_join(join_solution_x) %>%
  ggplot(aes(plt_x, zscore_blsub_mean, color = set_id)) +
  #geom_line(aes(group = interaction(region, subject)), alpha = 1/3) +
  geom_hline(yintercept = 0, size = 1/4, color = 'darkgrey') +
  stat_summary(fun = 'mean', geom = 'line', aes(group = set_id)) +
  stat_summary(fun.data = 'mean_se', geom = 'errorbar', aes(group = set_id), width = 0) +
  theme_ag01() +
  scale_color_manual(values = color_values_experiment_set) +
  theme(axis.text.x = element_blank())+
  facet_grid(.~region, scales = 'free') +
  coord_cartesian(xlim = c(0.5, 5.5), ylim = c(-1, 1.5), clip = 'off', expand = 0) +
  force_panelsizes(rows = unit(2,'cm'), cols = unit(1.5, 'cm')) +
  theme(strip.text = element_blank()) +
  ylab('Z-score post (6-8 s)') +
  xlab('')

save_pdf(dir_output_fp_str, str_c(fn_stem, '.pdf'), 6, 6)
plt_data %>% write_csv(str_c(dir_output_fp_str, fn_stem, '_data.csv'))



```



### range combined
```{r}
fn_stem <- 'fp_str_range_dodge'

plt_data <-  df %>%
  filter(time_bin == 'sustained') %>%
  select(set_id, subject, region, solution, zscore_blsub_mean) %>%
  mutate(solution_magnitude = case_when(
    solution %in% c('sucrose00', 'nacl150') ~ 'low',
    solution %in% c('sucrose30', 'nacl000') ~ 'high'
  )) %>%
  filter(!is.na(solution_magnitude) ) %>%
  select(-solution) %>%
  spread(solution_magnitude, zscore_blsub_mean) %>%
  mutate(range = high - low) 


plt_data %>%
  ggplot(aes(set_id, range, fill = region, color = region)) +
  stat_summary(fun.data = 'mean_se', geom = 'errorbar', position = position_dodge(width = 0.9), width = 0.4) +
  stat_summary(fun = 'mean', geom = 'col', position = position_dodge(width = 0.9), width = 0.75) +
  geom_jitter(position = position_jitterdodge(jitter.width = 0.3, dodge.width = 0.9), shape = 21, color = 'white', stroke = 0.25, size = 2) +
  theme_ag01() +
  scale_color_manual(values = color_values_regions_da7) +
  scale_fill_manual(values = color_values_regions_da7) +
  ylab('Range') +
  xlab('') +
  coord_cartesian(xlim = c(0.5, 3.5), ylim = c(0, 10), clip = 'off', expand = 0) +
  force_panelsizes(rows = unit(3,'cm'), cols = unit(12, 'cm')) 

save_pdf(dir_output_fp_str, str_c(fn_stem, '.pdf'), 6, 6)
plt_data %>% write_csv(str_c(dir_output_fp_str, fn_stem, '_data.csv'))

```


```{r}
fn_stem <- 'fp_str_range_sustained_heat'

plt_data <-  df %>%
  filter(time_bin == 'sustained') %>%
  select(set_id, subject, region, solution, zscore_blsub_mean) %>%
  mutate(solution_magnitude = case_when(
    solution %in% c('sucrose00', 'nacl150') ~ 'low',
    solution %in% c('sucrose30', 'nacl000') ~ 'high'
  )) %>%
  filter(!is.na(solution_magnitude) ) %>%
  select(-solution) %>%
  spread(solution_magnitude, zscore_blsub_mean) %>%
  mutate(range = high - low) 
  
plt_data_summary <-plt_data %>%
  group_by(set_id, region) %>%
  summarise(range_mean = range %>% mean(), .groups = 'drop')

plt_data_summary %>%
  ggplot(aes(region, set_id, fill = range_mean)) +
  geom_tile() +
  scale_fill_viridis_c(limits = c(-1,5), oob = scales::squish) +
  ylab('') +
  xlab('') +
  coord_cartesian(xlim = c(0.5, 7.5), ylim = c(0.5, 3.5), clip = 'off', expand = 0) +
  theme(axis.text.x = element_text(angle = 90, hjust = 1, vjust = 0.3)) +
  force_panelsizes(rows = unit(2,'cm'), cols = unit(2.5, 'cm')) 

save_pdf(dir_output_fp_str, str_c(fn_stem, '.pdf'), 6, 6)
plt_data %>% write_csv(str_c(dir_output_fp_str, fn_stem, '_data.csv'))

```

```{r}
fn_stem <- 'fp_str_range_post_heat'

plt_data <-  df %>%
  filter(time_bin == 'post') %>%
  select(set_id, subject, region, solution, zscore_blsub_mean) %>%
  mutate(solution_magnitude = case_when(
    solution %in% c('sucrose00', 'nacl150') ~ 'low',
    solution %in% c('sucrose30', 'nacl000') ~ 'high'
  )) %>%
  filter(!is.na(solution_magnitude) ) %>%
  select(-solution) %>%
  spread(solution_magnitude, zscore_blsub_mean) %>%
  mutate(range = high - low) 
  
plt_data_summary <-plt_data %>%
  group_by(set_id, region) %>%
  summarise(range_mean = range %>% mean(), .groups = 'drop')
 
plt_data_summary %>%
  ggplot(aes(region, set_id, fill = range_mean)) +
  geom_tile() +
  scale_fill_viridis_c(limits = c(-1,2), oob = scales::squish) +
  ylab('') +
  xlab('') +
  coord_cartesian(xlim = c(0.5, 7.5), ylim = c(0.5, 3.5), clip = 'off', expand = 0) +
  theme(axis.text.x = element_text(angle = 90, hjust = 1, vjust = 0.3)) +
  force_panelsizes(rows = unit(2,'cm'), cols = unit(2.5, 'cm')) 

save_pdf(dir_output_fp_str, str_c(fn_stem, '.pdf'), 6, 6)
plt_data %>% write_csv(str_c(dir_output_fp_str, fn_stem, '_data.csv'))

```

```{r}
plt_data <-  df %>%
  filter(time_bin == 'sustained') %>%
  select(set_id, subject, region, solution, zscore_blsub_mean) %>%
  mutate(solution_magnitude = case_when(
    solution %in% c('sucrose00', 'nacl150') ~ 'low',
    solution %in% c('sucrose30', 'nacl000') ~ 'high'
  )) %>%
  filter(!is.na(solution_magnitude) ) %>%
  select(-solution) %>%
  spread(solution_magnitude, zscore_blsub_mean) %>%
  mutate(range = high - low) 


plt_range <- c(-5, 15)
label_y <- 15


plt01 <- plt_data %>%
  select(set_id, subject, region, range) %>%
  spread(set_id, range) %>%
  ggplot(aes(`FR:Suc`, `WR:NaCl`)) +
  geom_abline(slope = 1, intercept = 0, color = 'darkgrey', size = 0.5) +
  geom_hline(yintercept = 0, color = 'darkgrey', size = 0.5) +
  geom_vline(xintercept = 0, color = 'darkgrey', size = 0.5) +
  geom_point(shape = 21, fill = 'black', color = 'white', stroke = 0.1) +
  geom_smooth(method = 'lm', size = 0.3, alpha = 1/5) +
  stat_cor(method = "pearson", size = 2, label.y = label_y, label.x = 0) +
  theme_ag01() +
  coord_cartesian(xlim = plt_range, ylim = plt_range, expand = F, clip = 'off') 


plt02 <- plt_data %>%
  select(set_id, subject, region, range) %>%
  spread(set_id, range) %>%
  ggplot(aes(`FR:Suc`, `WR:Suc`)) +
  geom_abline(slope = 1, intercept = 0, color = 'darkgrey', size = 0.5) +
  geom_hline(yintercept = 0, color = 'darkgrey', size = 0.5) +
  geom_vline(xintercept = 0, color = 'darkgrey', size = 0.5) +
  geom_point(shape = 21, fill = 'black', color = 'white', stroke = 0.1) +
  geom_smooth(method = 'lm', size = 0.3, alpha = 1/5) +
  stat_cor(method = "pearson", size = 2, label.y = label_y, label.x = 0) +
  theme_ag01()+
  coord_cartesian(xlim = plt_range, ylim = plt_range, expand = F, clip = 'off')

plt03 <- plt_data %>%
  select(set_id, subject, region, range) %>%
  spread(set_id, range) %>%
  ggplot(aes(`WR:Suc`, `WR:NaCl`)) +
  geom_abline(slope = 1, intercept = 0, color = 'darkgrey', size = 0.5) +
  geom_hline(yintercept = 0, color = 'darkgrey', size = 0.5) +
  geom_vline(xintercept = 0, color = 'darkgrey', size = 0.5) +
  geom_point(shape = 21, fill = 'black', color = 'white', stroke = 0.1) +
  geom_smooth(method = 'lm', size = 0.3, alpha = 1/5) +
  stat_cor(method = "pearson", size = 2, label.y = label_y, label.x = 0) +
  theme_ag01()+
  coord_cartesian(xlim = plt_range, ylim = plt_range, expand = F, clip = 'off')



plt01 + plt02 + plt03 +
  plot_layout(nrow = 1, widths = unit(3, 'cm'), heights = unit(3, 'cm'))
```

```{r}
plt_data <-  df %>%
  filter(time_bin == 'post') %>%
  select(set_id, subject, region, solution, zscore_blsub_mean) %>%
  mutate(solution_magnitude = case_when(
    solution %in% c('sucrose00', 'nacl150') ~ 'low',
    solution %in% c('sucrose30', 'nacl000') ~ 'high'
  )) %>%
  filter(!is.na(solution_magnitude) ) %>%
  select(-solution) %>%
  spread(solution_magnitude, zscore_blsub_mean) %>%
  mutate(range = high - low) 


plt_range <- c(-2.5, 5)
label_y <- 5


plt01 <- plt_data %>%
  select(set_id, subject, region, range) %>%
  spread(set_id, range) %>%
  ggplot(aes(`FR:Suc`, `WR:NaCl`)) +
  geom_abline(slope = 1, intercept = 0, color = 'darkgrey', size = 0.5) +
  geom_hline(yintercept = 0, color = 'darkgrey', size = 0.5) +
  geom_vline(xintercept = 0, color = 'darkgrey', size = 0.5) +
  geom_point(shape = 21, fill = 'black', color = 'white', stroke = 0.1) +
  geom_smooth(method = 'lm', size = 0.3, alpha = 1/5) +
  stat_cor(method = "pearson", size = 2, label.y = label_y, label.x = 0) +
  theme_ag01() +
  coord_cartesian(xlim = plt_range, ylim = plt_range, expand = F, clip = 'off') 


plt02 <- plt_data %>%
  select(set_id, subject, region, range) %>%
  spread(set_id, range) %>%
  ggplot(aes(`FR:Suc`, `WR:Suc`)) +
  geom_abline(slope = 1, intercept = 0, color = 'darkgrey', size = 0.5) +
  geom_hline(yintercept = 0, color = 'darkgrey', size = 0.5) +
  geom_vline(xintercept = 0, color = 'darkgrey', size = 0.5) +
  geom_point(shape = 21, fill = 'black', color = 'white', stroke = 0.1) +
  geom_smooth(method = 'lm', size = 0.3, alpha = 1/5) +
  stat_cor(method = "pearson", size = 2, label.y = label_y, label.x = 0) +
  theme_ag01()+
  coord_cartesian(xlim = plt_range, ylim = plt_range, expand = F, clip = 'off')

plt03 <- plt_data %>%
  select(set_id, subject, region, range) %>%
  spread(set_id, range) %>%
  ggplot(aes(`WR:Suc`, `WR:NaCl`)) +
  geom_abline(slope = 1, intercept = 0, color = 'darkgrey', size = 0.5) +
  geom_hline(yintercept = 0, color = 'darkgrey', size = 0.5) +
  geom_vline(xintercept = 0, color = 'darkgrey', size = 0.5) +
  geom_point(shape = 21, fill = 'black', color = 'white', stroke = 0.1) +
  geom_smooth(method = 'lm', size = 0.3, alpha = 1/5) +
  stat_cor(method = "pearson", size = 2, label.y = label_y, label.x = 0) +
  theme_ag01()+
  coord_cartesian(xlim = plt_range, ylim = plt_range, expand = F, clip = 'off')


plt01 + plt02 + plt03 +
  plot_layout(nrow = 1, widths = unit(3, 'cm'), heights = unit(3, 'cm'))
```

```{r}
plt_data <-  df %>%
  filter(time_bin %in% c('sustained', 'post')) %>%
  select(set_id, subject, region, time_bin, solution, zscore_blsub_mean) %>%
  mutate(solution_magnitude = case_when(
    solution %in% c('sucrose00', 'nacl150') ~ 'low',
    solution %in% c('sucrose30', 'nacl000') ~ 'high'
  )) %>%
  filter(!is.na(solution_magnitude) ) %>%
  select(-solution) %>%
  spread(solution_magnitude, zscore_blsub_mean) %>%
  mutate(range = high - low) 


plt_range <- c(-5, 15)
label_y <- 15


plt_data %>%
  select(set_id, time_bin, subject, region, range) %>%
  spread(time_bin, range) %>%
  ggplot(aes(sustained, post)) +
  geom_abline(slope = 1, intercept = 0, color = 'darkgrey', size = 0.5) +
  geom_hline(yintercept = 0, color = 'darkgrey', size = 0.5) +
  geom_vline(xintercept = 0, color = 'darkgrey', size = 0.5) +
  geom_point(shape = 21, fill = 'black', color = 'white', stroke = 0.1) +
  geom_smooth(method = 'lm', size = 0.3, alpha = 1/5) +
  stat_cor(method = "pearson", size = 2, label.y = 4, label.x = 0) +
  theme_ag01() +
  facet_grid(.~set_id) +
  coord_cartesian(xlim = plt_range, ylim = c(-2.5, 5), expand = F) +
  force_panelsizes(rows = unit(3, 'cm'), cols = unit(3, 'cm'))
```

### lick vs no lick
#### trace - lick/nolick
```{r}
# for each set_id individually
fns <- list.files(dir_output)
fns_filt <- fns[fns %>% str_detect('full')]
fns_filt <- fns_filt[fns_filt %>% str_detect('full_peth_summary_trace_triallick')]
fns_filt <- fns_filt %>% str_remove('.csv')

df_lick <- combined_import(import_directory = dir_output, 
                filter_strings = fns_filt,
                prefixes = NA,
                suffixes = c('.csv'),
                verbose = 0
                )[[1]]

plt_data_lick <- df_lick %>% 
  filt_and_format_data() %>%
  mutate(trial_lick = 
           case_when(
             trial_lick == 0 ~ 'no_lick',
             trial_lick == 1 ~ 'lick'
           ))


# across all set_ids
fns <- list.files(dir_output)
fns_filt <- fns[fns %>% str_detect('full')]
fns_filt <- fns_filt[fns_filt %>% str_detect('full_peth_summary_trace_triallick')]
fns_filt <- fns_filt %>% str_remove('.csv')

df_lick_overall <- read.csv(str_c(dir_output, 'combined_main_set_id_lickvsnolick_peth_summary_trace_overall.csv'))

plt_data_lick_overall <- df_lick_overall %>% 
  filter(!region %>% str_detect('LHA')) %>%
  mutate(region = region %>% factor(levels = unique(key_regions$region_label))) %>%
  mutate(trial_lick = 
           case_when(
             trial_lick == 0 ~ 'no_lick',
             trial_lick == 1 ~ 'lick'
           ))
```

```{r, fig.width = 12, fig.height = 5}
fn_stem <- 'fp_str_lickvnolick_setid_overall'

plt <- plt_data_lick_overall %>%
  #group_by(trial_lick, time_rel, region) %>%
  #summarise(zscore_blsub_mean = mean(zscore_blsub_mean), zscore_blsub_sem = mean(zscore_blsub_sem)) %>%
  filter(time_rel < 3, time_rel > -0.5) %>%
  ggplot(aes(time_rel, zscore_blsub_mean, group = trial_lick, color = trial_lick, fill = trial_lick)) +
  annotate("rect", xmin = 0, xmax = 3, ymin = -Inf, ymax = Inf, alpha = 1/3, fill = "darkgrey") +
  geom_vline(xintercept = 0.3, color = 'darkgrey', size = 0.5, linetype = 2) +
  geom_hline(yintercept = 0, color = 'darkgrey', size = 0.5) +
  geom_ribbon(
    aes(
      ymin = zscore_blsub_mean - zscore_blsub_sem,
      ymax
      = zscore_blsub_mean + zscore_blsub_sem
        ),
    alpha = 1/3,
    color = NA
    ) +
  geom_line() +
  facet_grid(.~region) +
  scale_color_manual(values = c('blue', 'black')) +
  scale_fill_manual(values = c('blue', 'black')) +
  theme_ag01() +
  theme(strip.text = element_text(margin = margin(t = 5, r = 5, b = 5, l = 5))) +
  theme(panel.spacing.y = unit(0.5, "lines")) +
  force_panelsizes(rows = unit(1, 'cm'), cols = unit(1.5, 'cm'))


plt <- plt %>%
  add_scale_bar(
    origin = c(-0.5, -0.5), 
    x_len = 1, 
    y_len = 1
  )

plt

save_pdf(dir_output_fp_str, str_c(fn_stem, '.pdf'), 6, 6)
plt_data %>% write_csv(str_c(dir_output_fp_str, fn_stem, '_data.csv'))
```



```{r, fig.width = 12, fig.height = 5}
fn_stem <- 'fp_str_lickvnolick_setid_trace'

plt <- plt_data_lick %>%
  #group_by(trial_lick, time_rel, region) %>%
  #summarise(zscore_blsub_mean = mean(zscore_blsub_mean), zscore_blsub_sem = mean(zscore_blsub_sem)) %>%
  filter(time_rel < 3, time_rel > -0.5) %>%
  ggplot(aes(time_rel, zscore_blsub_mean, group = trial_lick, color = trial_lick, fill = trial_lick)) +
  annotate("rect", xmin = 0, xmax = 3, ymin = -Inf, ymax = Inf, alpha = 1/3, fill = "darkgrey") +
  geom_vline(xintercept = 0.3, color = 'darkgrey', size = 0.5, linetype = 2) +
  geom_hline(yintercept = 0, color = 'darkgrey', size = 0.5) +
  geom_ribbon(
    aes(
      ymin = zscore_blsub_mean - zscore_blsub_sem,
      ymax
      = zscore_blsub_mean + zscore_blsub_sem
        ),
    alpha = 1/3,
    color = NA
    ) +
  geom_line() +
  facet_grid(set_id~region) +
  scale_color_manual(values = c('blue', 'black')) +
  scale_fill_manual(values = c('blue', 'black')) +
  theme_ag01() +
  theme(strip.text = element_text(margin = margin(t = 5, r = 5, b = 5, l = 5))) +
  theme(panel.spacing.y = unit(0.5, "lines")) +
  force_panelsizes(rows = unit(2, 'cm'), cols = unit(1.5, 'cm'))


plt <- plt %>%
  add_scale_bar(
    origin = c(-0.5, -0.5), 
    x_len = 1, 
    y_len = 1
  )

plt

save_pdf(dir_output_fp_str, str_c(fn_stem, '.pdf'), 6, 6)
plt_data %>% write_csv(str_c(dir_output_fp_str, fn_stem, '_data.csv'))
```


#### summary - prelick
```{r}

# for each set_id individually
fns <- list.files(dir_output)
fns_filt <- fns[fns %>% str_detect('triallick')]
fns_filt <- fns_filt[fns_filt %>% str_detect('peth_summary_means_subject')]
fns_filt <- fns_filt %>% str_remove('.csv')

df <- combined_import(import_directory = dir_output, 
                filter_strings = fns_filt,
                prefixes = NA,
                suffixes = c('.csv'),
                verbose = 0
                )[[1]] %>% 
  filt_and_format_data() 

plt_data <-  df %>%
  filter(time_bin == 'prelick') %>%
  select(set_id, subject, region, trial_lick, zscore_blsub_mean)


# across all set_ids
df <- read.csv(str_c(dir_output, 'combined_main_set_id_lickvsnolick_peth_summary_means_subject.csv')) 


plt_data_summary <- df %>%
  filter(!region %>% str_detect('LHA')) %>%
  mutate(region = region %>% factor(levels = unique(key_regions$region_label))) %>%
  select(subject, region, time_bin, trial_lick, zscore_blsub_mean)
```


```{r}
fn_stem <- 'fp_str_summary_lickvsnolick_prelick'

plt_data <- plt_data_summary %>%
  filter(time_bin == 'prelick') 

plt_data %>%
  mutate(trial_lick = ifelse(trial_lick == '0', '0', '≥1')) %>%
  mutate(trial_lick = trial_lick %>% factor(levels = c('0', '≥1'))) %>%
  ggplot(aes(trial_lick, zscore_blsub_mean)) +
  geom_line(aes(group = interaction(region, subject)), alpha = 1/3, size = 1/4) +
  geom_hline(yintercept = 0, size = 1/4, color = 'darkgrey') +
  stat_summary(fun = 'mean', geom = 'line', aes(group = 1)) +
  stat_summary(fun.data = 'mean_se', geom = 'errorbar', aes(group = 1), width = 0) +
  theme_ag01() +
  #scale_x_continuous(breaks = c(0,1)) +
  facet_grid(.~region, scales = 'free') +
  coord_cartesian(xlim = c(0.5, 2.5), ylim = c(-1,3), clip = 'off', expand = 0) +
  force_panelsizes(rows = unit(1,'cm'), cols = unit(1.5, 'cm')) +
  theme(strip.text.x = element_blank()) +
  ylab('Z-score pre-lick (0.0-0.3 s)') +
  xlab('')

save_pdf(dir_output_fp_str, str_c(fn_stem, '.pdf'), 6, 6)
plt_data %>% write_csv(str_c(dir_output_fp_str, fn_stem, '_data.csv'))
```

#### combined stats - prelick
```{r}
stats_data <- plt_data_summary %>%
  filter(time_bin == 'prelick') 

stats_results <- stats_data %>%
   mutate(trial_lick = ifelse(trial_lick == 1, 'lick', 'nolick')) %>%
   spread(trial_lick, zscore_blsub_mean) %>%
   tidy_ttest_paired(NA, NA, 'lick', 'nolick', 'region') %>%
   quick_sig()

stats_results %>%
  select(region, sig_symbol)

stats_results %>% write_csv(str_c(dir_output_fp_str, 'fp_str_summary_lickvsnolick_prelick_stats.csv'))
```


#### range
```{r}

# for each set_id individually
fns <- list.files(dir_output)
fns_filt <- fns[fns %>% str_detect('triallick')]
fns_filt <- fns_filt[fns_filt %>% str_detect('peth_summary_means_subject')]
fns_filt <- fns_filt %>% str_remove('.csv')


df <- combined_import(import_directory = dir_output, 
                filter_strings = fns_filt,
                prefixes = NA,
                suffixes = c('.csv'),
                verbose = 0
                )[[1]] %>% 
  filt_and_format_data() 

plt_data <-  df %>%
  filter(time_bin == 'prelick') %>%
  select(set_id, subject, region, trial_lick, zscore_blsub_mean) %>%
  spread(trial_lick, zscore_blsub_mean) %>%
  mutate(range = `1` - `0`)


# across all set_ids
df <- read.csv(str_c(dir_output, 'combined_main_set_id_lickvsnolick_peth_summary_means_subject.csv')) %>%
  filter(time_bin == 'prelick') 




plt_data_summary <- df %>%
  filter(!region %>% str_detect('LHA')) %>%
  mutate(region = region %>% factor(levels = unique(key_regions$region_label))) %>%
  select(subject, region, trial_lick, zscore_blsub_mean) %>%
  spread(trial_lick, zscore_blsub_mean) %>%
  mutate(range = 
           `1` - `0`)



```


```{r}
fn_stem <- 'fp_str_summary_lickvsnolick_prelick_heat' 


plt_data_summary <- plt_data %>%
  group_by(set_id, region) %>%
  summarise(range_mean = range %>% mean(na.rm = T), .groups = 'drop')

plt_data_summary %>%
  ggplot(aes(region, set_id, fill = range_mean)) +
  geom_tile() +
  scale_fill_viridis_c(limits = c(-0.2,1), oob = scales::squish) +
  ylab('') +
  xlab('') +
  coord_cartesian(xlim = c(0.5, 7.5), ylim = c(0.5, 3.5), clip = 'off', expand = 0) +
  theme(axis.text.x = element_text(angle = 90, hjust = 1, vjust = 0.3)) +
  force_panelsizes(rows = unit(2,'cm'), cols = unit(2.5, 'cm')) 

save_pdf(dir_output_fp_str, str_c(fn_stem, '.pdf'), 6, 6)
plt_data %>% write_csv(str_c(dir_output_fp_str, fn_stem, '_data.csv'))

```



### placement plots
```{r}
range_prelick <- read.csv('./analysis_output/peth_str/fp_str_summary_lickvsnolick_prelick_heat_data.csv') %>%
  mutate(time_bin = 'prelick') %>%
  select(set_id, subject, region, time_bin, range) 

range_sustained <- read.csv('./analysis_output/peth_str/fp_str_range_sustained_heat_data.csv')%>%
  mutate(time_bin = 'sustained') %>%
  select(set_id, subject, region, time_bin, range) 

range_post <- read.csv('./analysis_output/peth_str/fp_str_range_post_heat_data.csv')%>%
  mutate(time_bin = 'post') %>%
  select(set_id, subject, region, time_bin, range) 


summary_range_combined <- range_prelick %>%
  bind_rows(range_sustained) %>%
  bind_rows(range_post)
```



```{r}
fn_stem <- 'placement_vs_range'

source('./functions/plotting_placements.R')

modify_plt_corr <- function(plt, loop_time_bin){
  plt <- plt +
    theme(strip.text = element_blank()) 
  
    if(loop_time_bin == 'prelick'){
      plt <- plt %>%
        remove_x_all()
    }
  
    if(loop_time_bin == 'sustained'){
      plt <- plt %>%
        remove_x_all()
      }
  
  
  return(plt)
}

set.seed(33)

for(loop_set_id in c('WR:NaCl', 'FR:Suc', 'WR:Suc')){
  for(loop_time_bin in c('prelick', 'sustained', 'post')){
    
    loop_set_label <- loop_set_id %>% str_remove(':')
    fn_stem02 <-  str_c(fn_stem,'_', loop_set_label, '_', loop_time_bin)
    
    df <- summary_range_combined %>%
      filter(set_id == loop_set_id) %>%
      filter(time_bin == loop_time_bin) %>%
      join_placements() %>%
      select(set_id, subject, time_bin, region, range, starts_with('hit')) %>%
      mutate(region = region %>% factor(levels = unique(key_regions$region_label))) %>%
      filter(!is.na(range))
    
    
    
    var_color <- 'range'
    
    if(loop_time_bin == 'prelick'){color_limits <- c(-0.2,1)}
    if(loop_time_bin == 'sustained'){color_limits <- c(-1,5)}
    if(loop_time_bin == 'post'){color_limits <- c(-1,2)}

    plt_str(
      df = df,
      var_color = !!sym(var_color),
      var_color_name = 'Range',
      vars_facet = c('.','.'),
      plt_plane = 'sagittal',
      plt_dim_base = 3,
      color_limits = color_limits
      )

    save_pdf(str_c(dir_output_fp_str, 'placements/'), str_c(fn_stem02, '_sagittal.pdf'),6,6)

    plt_str(
      df = df,
      var_color = !!sym(var_color),
      var_color_name = 'Range',
      vars_facet = c('.','.'),
      plt_plane = 'horizontal',
      plt_dim_base = 3,
      color_limits = color_limits
      )

    save_pdf(str_c(dir_output_fp_str, 'placements/'), str_c(fn_stem02, '_horizontal.pdf'),6,6)

    plt_str(
      df = df,
      var_color = !!sym(var_color),
      var_color_name = 'Range',
      vars_facet = c('.','.'),
      plt_plane = 'coronal',
      plt_dim_base = 3,
      color_limits = color_limits
      )

    save_pdf(str_c(dir_output_fp_str, 'placements/'), str_c(fn_stem02, '_coronal.pdf'),6,6)

    plt_str_3d(
      df = df,
      var_color = var_color,
      color_limits = color_limits,
      dir_output = str_c(dir_output_fp_str, 'placements/'),
      fn_stem = str_c(fn_stem02),
      toggle_save = 1
      )
    
    # correlations
    if(loop_time_bin == 'prelick'){ylim_all <- c(-2,3)}
    if(loop_time_bin == 'sustained'){ylim_all <- c(-4,12)}
    if(loop_time_bin == 'post'){ylim_all <- c(-2,4)}
    
    plt_list <- plt_corr_generic(
      df = df, 
      ylim_all = ylim_all, 
      xlim_ap = c(-3, 0, 3),
      xlim_ml = c(0, 2, 4),
      xlim_dv = c(-6, -4, -2),
      var_dep = var_color, 
      var_dep_label = 'Range', 
      plt_dims = c(2.5, 2.5)
    )
    
    
    plt_list[['stats_output']] 
    
    # run pearsons
    plt_list[['AP']] %>% modify_plt_corr(loop_time_bin) +
      plt_list[['ML']] %>% modify_plt_corr(loop_time_bin) + 
      plt_list[['DV']] %>% modify_plt_corr(loop_time_bin) +
      plot_layout(nrow = 1, widths = unit(3, 'cm'), heights = unit(3, 'cm'), guides = 'collect')
    
    save_pdf(
      str_c(dir_output_fp_str, 'placements/'),
      str_c(fn_stem02, '_corr', '.pdf'),
      12, 
      6
    )
    
    df %>%
      write_csv(str_c(dir_output_fp_str, 'placements/', fn_stem02, '_corr_data.csv'))
    
    plt_list[['stats_output']]  %>%
      write_csv(str_c(dir_output_fp_str, 'placements/', fn_stem02, '_corr_stats.csv'))
  
  }
}
``` 

#### colored by fiber locaiton
```{r}
dir_output <- dir_output_fp_str
fn_stem <- 'placement_generic'

plt_data <- summary_range_combined %>%
    select(subject, region) %>%
    unique() %>%
    join_placements() %>%
    select(subject, region, starts_with('hit')) %>%
    mutate(region = region %>% factor(levels = unique(key_regions$region_label)))


plt_data %>%
  group_by(region) %>%
  summarise(count = n())
```


```{r}
df <- plt_data

var_color <- 'region'
var_color_name <- 'Region'
color_limits <- c(0,0.8)

plt_str_d(
  df = df, 
  var_color = !!sym(var_color),
  var_color_name = var_color_name,
  vars_facet = c('.','.'),
  plt_plane = 'sagittal',
  plt_dim_base = 3,
  color_values = color_values_regions_da7
  )

save_pdf(str_c(dir_output, 'placements/'), str_c(fn_stem, '_sagittal.pdf'),6,6)

plt_str_d(
  df = df,
  var_color = !!sym(var_color),
  var_color_name = var_color_name,
  vars_facet = c('.','.'),
  plt_plane = 'horizontal',
  plt_dim_base = 3,
  color_values = color_values_regions_da7
  ) 

save_pdf(str_c(dir_output, 'placements/'), str_c(fn_stem, '_horizontal.pdf'),6,6)

plt_str_d(
  df = df,
  var_color = !!sym(var_color),
  var_color_name = var_color_name,
  vars_facet = c('.','.'),
  plt_plane = 'coronal',
  plt_dim_base = 3,
  color_values = color_values_regions_da7
  ) 

save_pdf(str_c(dir_output, 'placements/'), str_c(fn_stem, '_coronal.pdf'),6,6)

df_3d <- df %>%
  select(region) %>%
  unique() %>%
  arrange(region) %>%
  mutate(color_value = color_values_regions_da7) %>%
  left_join(df,.)

plt_str_3d_d(
  df = df_3d, 
  var_color = var_color, 
  color_values = 'color_value',
  dir_output = str_c(dir_output, 'placements/'),
  fn_stem = str_c(fn_stem),
  toggle_save = 1
  )

```


### corr lick vs resp
```{r}
dir_import <- './data/combined_setid/'

fns <- list.files(dir_import)
fns_filt <- fns[fns %>% str_detect('filtlick_peth_summary_means_trial')]
fns_filt <- fns_filt %>% str_remove('.csv')

df <- combined_import(import_directory = dir_import, 
                filter_strings = fns_filt,
                prefixes = NA,
                suffixes = c('.csv'),
                verbose = 0
                )[[1]] %>% 
  filt_and_format_data() %>%
  filter(time_bin == 'sustained')
```


```{r, fig.width = 18, fig.height = 6}

fn_stem <- 'fp_str_cor_zscore_vs_lick'


df_plt <- df %>%
  filter(time_bin == 'sustained') 

df %>%
  filter(time_bin == 'sustained') %>%
  ggplot(aes(zscore_blsub_mean, lick_count)) +
  geom_jitter(size = 0.1, alpha = 1/8) +
  geom_smooth(method = 'lm', size = 0.3, alpha = 1/5, color = 'black') +
  stat_cor(method = "pearson", label.y = 29, label.x = -8, size = 2) +
  facet_grid(set_id~region) +
  theme_ag01() +
  coord_cartesian(xlim = c(-10,20), ylim = c(0,30), expand = F, clip = 'on') +
  scale_x_continuous(breaks = seq(-10,20,10)) +
  theme(strip.text = element_text(margin = margin(t = 5, r = 5, b = 5, l = 5))) +
  theme(panel.spacing = unit(1, "lines")) +
  ylab('Lick count') +
  xlab('Z-score sustained (2-3s)') +
  force_panelsizes(rows = unit(2,'cm'), cols = unit(2, 'cm'))


save_pdf(dir_output_fp_str, str_c(fn_stem, '.pdf'), 12, 6)
plt_data %>% write_csv(str_c(dir_output_fp_str, fn_stem, '_data.csv'))
```

```{r}
corr_sbj <- df %>%
  filter(time_bin == 'sustained') %>%
  tidy_cor('zscore_blsub_mean', 'lick_count', 'subject', 'region', 'set_id') %>%
  mutate(estimate_squared = estimate^2) %>% 
  ungroup()


fn_stem <- 'fp_str_cor_zscore_vs_lick_subject_summary_combined' #~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~


corr_sbj %>%
  ggplot(aes(set_id, estimate_squared, fill = region, color = region)) +
  stat_summary(fun.data = 'mean_se', geom = 'errorbar', position = position_dodge(width = 0.9), width = 0.4) +
  stat_summary(fun = 'mean', geom = 'col', position = position_dodge(width = 0.9), width = 0.75) +
  geom_jitter(position = position_jitterdodge(jitter.width = 0.3, dodge.width = 0.9), shape = 21, color = 'white', stroke = 0.25, size = 2) +
  theme_ag01() +
  scale_color_manual(values = color_values_regions_da7) +
  scale_fill_manual(values = color_values_regions_da7) +
  ylab('R^2') +
  xlab('') +
  coord_cartesian(xlim = c(0.5, 3.5), ylim = c(0, 1), clip = 'off', expand = 0) +
  force_panelsizes(rows = unit(3,'cm'), cols = unit(12, 'cm')) 


save_pdf(dir_output_fp_str, str_c(fn_stem, '.pdf'), 8, 4)

corr_sbj %>% write_csv(str_c(dir_output_fp_str, fn_stem, '_data.csv'))

stats_list <- corr_sbj %>%
  mutate(subject = str_c(subject, row_number())) %>%
  aov_rm_two_between(dir_output_fp_str,fn_stem,'subject','estimate_squared', 'region', 'set_id')
```


```{r}
stats_list[[3]] %>%
  filter(contrast1_between2 == contrast2_between2) %>%
  select(contrast1_between2, contrast1_between1, contrast2_between1, p_value, sig_symbol) %>%
  filter(sig_symbol != 'n.s.')


stats_list[[3]] %>%
  filter(contrast1_between1 == contrast2_between1) %>%
  select(contrast1_between2, contrast2_between2, contrast1_between1, p_value, sig_symbol) %>%
  filter(sig_symbol != 'n.s.')
```

### lick count binned vs solution heat
```{r, fig.width = 12, fig.height = 4}
fn_stem <- 'fp_str_solution_vs_lickcountbinned_heat' 

plt_data <- df %>%
  select(subject, region, set_id, trial_num, solution, lick_count, zscore_blsub_mean) %>%
  mutate(lick_count_bin = cut(lick_count, seq(0,25,5))) %>%
  group_by(set_id, region, subject, solution, lick_count_bin) %>%
  summarise(zscore_blsub_mean = zscore_blsub_mean %>% mean(),
            sample_count_per_subject = n()) %>%
  filter(sample_count_per_subject >= 3) %>%
  group_by(set_id, region, solution, lick_count_bin) %>%
  summarise(zscore_blsub_mean = zscore_blsub_mean %>% mean(), .groups = 'drop') %>%
  left_join(join_solution_x)


plt_data %>%
  filter(!is.na(lick_count_bin)) %>%
  ggplot(aes(plt_x, lick_count_bin, fill = zscore_blsub_mean)) +
  geom_tile() +
  facet_grid(set_id~region) +
  theme_ag01() +
  coord_cartesian(xlim = c(0.5,5.5), ylim = c(0.5, 5.5), expand = F) +
  scale_fill_viridis_c(limits = c(-1,4), oob = scales::squish) +
  force_panelsizes(rows = unit(2,'cm'), cols = unit(2, 'cm')) +
  ylab('Binned lick count') +
  xlab('Solution value (rank)')

save_pdf(dir_output_fp_str, str_c(fn_stem, '.pdf'), 8, 4)

plt_data %>% write_csv(str_c(dir_output_fp_str, fn_stem, '_data.csv'))
```


### kinetics
```{r}
# todo:
#  - loop over set_id
#  - define solutions of intereste with vector
#  - replace zscore_blsub with vardv
#  - derive streams_peth_solution_derivative in get_kinetics

dir_output <- "./analysis_output/peth_str/"

df_peth <- read.csv('./data/combined_setid/wrnacl_filtlick_peth_summary_trace_overall.csv')
df_derivative <- read.csv('./data/combined_setid/wrnacl_filtlick_pethkinetics_summary_trace_subject.csv')

df_kinetic_summary_trial <- read.csv('./data/combined_setid/wrnacl_filtlick_pethkinetics_summary_means_trial.csv')
df_kinetic_summary_subject_region_solution <- read.csv('./data/combined_setid/wrnacl_filtlick_pethkinetics_summary_means_subject.csv')

df_peth <- df_peth %>%
  filter(!region %>% str_detect('LHA')) %>%
  mutate(region = region %>% factor(levels = key_regions$region_label %>% unique()))

df_derivative <- df_derivative %>%
  filter(!region %>% str_detect('LHA')) %>%
  mutate(region = region %>% factor(levels = key_regions$region_label %>% unique()))

df_kinetic_summary_subject_region_solution <- df_kinetic_summary_subject_region_solution %>%
  filter(!region %>% str_detect('LHA')) %>%
  mutate(region = region %>% factor(levels = key_regions$region_label %>% unique()))

# nacl000 only
plt_data_kinetics <- df_kinetic_summary_subject_region_solution %>%
  filter(solution == 'nacl000') %>%
  select(-solution) %>%
  group_by(subject, region) %>%
  summarise_all(mean)

plt_summary_kineticsv02(
  plt_data_kinetics = plt_data_kinetics, 
  fn_stem_set = 'kinetics_nacl000', 
  dir_output_fp_str
  )

# duplicate files into dir_output_fp_str
source_folder <- "./data/combined_setid/kinetics_nacl000/"
destination_folder <- dir_output_fp_str


```


```{r}
plt <- df_derivative %>%
  filter(!region %>% str_detect('LHA')) %>%
  group_by(region, solution, time_rel) %>%
  filter(solution == 'nacl000') %>%
  filter(time_rel > -1, time_rel < 3) %>%
  ggplot(aes(time_rel, derivative_mean, color = region,  fill = region)) +
  annotate("rect", xmin = 0, xmax = 3, ymin = -Inf, ymax = Inf, alpha = 1/3, fill = "darkgrey") +
  geom_ribbon(aes(ymax = derivative_mean + derivative_sem, ymin = derivative_mean - derivative_sem), alpha = 1/3, color = NA) +
  geom_line() +
  scale_color_manual(values = color_values_regions_da7) +
  scale_fill_manual(values = color_values_regions_da7) +
  theme_ag01() +
  force_panelsizes(rows = unit(4, 'cm'), cols = unit(11, 'cm')) +
  ggtitle('WR:NaCl / water')



plt %>%
  add_scale_bar(
    origin = c(-1, -0.1), 
    x_len = 1, 
    y_len = 0.25
  )

save_pdf(dir_output_fp_str, 'kinetics_nacl000_trace_derivative.pdf',6,4)
```


```{r}
plt <- df_peth %>%
  filter(!region %>% str_detect('LHA')) %>%
  group_by(region, solution, time_rel) %>%
  filter(solution == 'nacl000') %>%
  filter(time_rel > -1, time_rel < 3) %>%
  ggplot(aes(time_rel, zscore_blsub_mean, color = region,  fill = region)) +
  annotate("rect", xmin = 0, xmax = 3, ymin = -Inf, ymax = Inf, alpha = 1/3, fill = "darkgrey") +
  geom_ribbon(aes(ymax = zscore_blsub_mean + zscore_blsub_sem, ymin = zscore_blsub_mean - zscore_blsub_sem), alpha = 1/3, color = NA) +
  geom_line() +
  scale_color_manual(values = color_values_regions_da7) +
  scale_fill_manual(values = color_values_regions_da7) +
  theme_ag01() +
  force_panelsizes(rows = unit(4, 'cm'), cols = unit(11, 'cm')) +
  ggtitle('WR:NaCl / water')

plt %>%
  add_scale_bar(
    origin = c(-1, -0.2), 
    x_len = 1, 
    y_len = 1
  )

save_pdf(dir_output_fp_str, 'kinetics_nacl000_trace_raw.pdf',6,4)
```


## str correlation
```{r}
# read in data
dir_output_fp_str_cor <- './analysis_output/peth_str_cor/'

## baseline
fns_streams_bl_corr <- list.files(dir_sessions_combined_subject, pattern = 'streams_baseline_corr.csv', recursive = T, full.names = T)

streams_bl_corr <- bind_rows(lapply(fns_streams_bl_corr, read.csv)) %>%
  filter(set_id %in% c('wrnacl', 'wrsuc', 'frsuc')) %>%
  format_set_id(key_set_id) %>%
  mutate(
    var_x = var_x %>% factor(levels = key_regions$region_label %>% unique()),
    var_y = var_y %>% factor(levels = key_regions$region_label %>% unique())
    )

## peth time_rel
fns_streams_peth_corr_timerel <- list.files(dir_sessions_combined_subject, pattern = 'streams_peth_corr_timerel.csv', recursive = T, full.names = T)

streams_peth_corr_timerel <- bind_rows(lapply(fns_streams_peth_corr_timerel, read.csv)) %>%
  filter(set_id %in% c('wrnacl', 'wrsuc', 'frsuc')) %>%
  format_set_id(key_set_id) %>%
  mutate(
    var_x = var_x %>% factor(levels = key_regions$region_label %>% unique()),
    var_y = var_y %>% factor(levels = key_regions$region_label %>% unique())
    )


## peth time_rel
fns_streams_peth_corr_windows <- list.files(dir_sessions_combined_subject, pattern = 'streams_peth_corr_windows.csv', recursive = T, full.names = T)

streams_peth_corr_windows <- bind_rows(lapply(fns_streams_peth_corr_windows, read.csv)) %>%
  filter(set_id %in% c('wrnacl', 'wrsuc', 'frsuc')) %>%
  format_set_id(key_set_id) %>%
  mutate(
    var_x = var_x %>% factor(levels = key_regions$region_label %>% unique()),
    var_y = var_y %>% factor(levels = key_regions$region_label %>% unique())
    )


```

### baseline correlation across homeostatic demand
```{r}
fn_stem <- 'cor_baseline_setid'

plt_data_subject <- streams_bl_corr %>%
  mutate(set_id = set_id %>% factor(levels = c('FR:Suc', 'WR:Suc', 'WR:NaCl'))) %>%
  group_by(set_id, subject, var_x, var_y) %>%
  filter(var_x != var_y) %>%
  summarise(r = mean(r), .groups = 'drop') %>%
  group_by(set_id, subject) %>%
  summarise(r = mean(r), .groups = 'drop')

plt_data_summary <- streams_bl_corr %>%
  mutate(set_id = set_id %>% factor(levels = c('FR:Suc', 'WR:Suc', 'WR:NaCl'))) %>%
  group_by(set_id, var_x, var_y) %>%
  summarise(r = mean(r))

plt_corrmatrix(plt_data_summary) +
  facet_grid(.~set_id) +
  ggtitle('Baseline correlation \n') +
  force_panelsizes(rows = unit(3, 'cm'), cols = unit(3, 'cm'))

save_pdf(dir_output_fp_str_cor, str_c(fn_stem, '_heat', '.pdf'), 6, 4)


plt_data_subject %>%
  ggplot(aes(set_id, r, group = 1)) +
  geom_line(aes(group = subject), alpha = 1/3, size = 1/3) +
  stat_summary(fun = 'mean', geom = 'line') +
  stat_summary(fun.data = 'mean_se', geom = 'errorbar', width = 0) +
  theme_ag01() +
  theme(axis.text.x = element_text(angle = 90, hjust = 1, vjust = 0.3)) +
  coord_cartesian(xlim = c(0.5, 3.5), ylim = c(0, 0.8), expand = F) +
  #scale_y_continuous(breaks = seq(0,0.6,0.2)) +
  xlab('') +
  ylab('Mean R') +
  force_panelsizes(rows = unit(3, 'cm'), cols = unit(3.3512, 'cm'))

save_pdf(dir_output_fp_str_cor, str_c(fn_stem, '_summary', '.pdf'), 6, 4)

plt_data_subject %>%
  aov_rm_one_within(dir_output_fp_str_cor,str_c(fn_stem,'_summary'),'subject','r','set_id')

```


```{r}
fn_stem <- 'cor_peth_setid'

plt_data_summary <- streams_peth_corr_windows %>%
  mutate(set_id = set_id %>% factor(levels = c('FR:Suc', 'WR:Suc', 'WR:NaCl'))) %>%
  mutate(time_rel_bin = factor(time_rel_bin, levels = c('Pre', 'Sustained', 'Post'))) 


plt_data_subject <- streams_peth_corr_windows %>%
  mutate(set_id = set_id %>% factor(levels = c('FR:Suc', 'WR:Suc', 'WR:NaCl'))) %>%
  mutate(time_rel_bin = factor(time_rel_bin, levels = c('Pre', 'Sustained', 'Post'))) %>%
  filter(var_x != var_y) %>%
  group_by(subject, set_id, time_rel_bin, var_x, var_y) %>%
  summarise(r = mean(r)) %>%
  group_by(subject, set_id, time_rel_bin) %>%
  summarise(r = mean(r), .groups = 'drop') 


plt_corrmatrix(plt_data_summary) +
  facet_grid(time_rel_bin~set_id) +
  ggtitle('Consumption correlation \n') +
  force_panelsizes(rows = unit(3, 'cm'), cols = unit(3, 'cm'))

save_pdf(dir_output_fp_str_cor, str_c(fn_stem, '_heat', '.pdf'), 6, 6)

plt_data_subject %>%
  ggplot(aes(time_rel_bin, r, group = 1)) +
  geom_line(aes(group = subject), alpha = 1/3, size = 1/3) +
  stat_summary(fun = 'mean', geom = 'line') +
  stat_summary(fun.data = 'mean_se', geom = 'errorbar', width = 0) +
  theme_ag01() +
  facet_grid(.~set_id) +
  theme(axis.text.x = element_text(angle = 90, hjust = 1, vjust = 0.3)) +
  coord_cartesian(xlim = c(0.25, 3.25), ylim = c(0, 1), expand = F) +
  scale_y_continuous(breaks = seq(0,1,0.25)) +
  xlab('') +
  ylab('Mean R') +
  force_panelsizes(rows = unit(4, 'cm'), cols = unit(1, 'cm'))

save_pdf(dir_output_fp_str_cor, str_c(fn_stem, '_summary', '.pdf'), 6, 4)

stats_list <- plt_data_subject %>%
  aov_rm_two_within(dir_output_fp_str_cor,str_c(fn_stem,'_summary'),'subject','r','set_id', 'time_rel_bin')

stats_list[[3]] %>%
  filter(contrast1_within1 == contrast2_within1) %>%
  filter(sig_symbol != 'n.s.') %>%
  ggplot(aes(contrast1_within2, contrast2_within2, label = sig_symbol)) +
  geom_text() +
  facet_grid(.~contrast1_within1)

stats_list[[3]] %>%
  filter(contrast1_within2 == contrast2_within2)
```


```{r}
plt_data <- streams_peth_corr_timerel %>%
  filter(var_x != var_y) %>%
  group_by(subject, set_id, time_rel) %>%
  summarise(r = mean(r)) 

plt_data %>%
  ggplot(aes(time_rel, r, color = set_id, fill = set_id, group = set_id)) +
  geom_hline(yintercept = c(0.2, 0.4, 0.6), color = 'darkgrey', size = 1/3) +
  annotate("rect", xmin = 0, xmax = 3, ymin = -Inf, ymax = Inf, alpha = 1/3, fill = "darkgrey") +
  stat_summary(fun.data = 'mean_se', geom = 'ribbon', color = NA, alpha = 1/3) +
  stat_summary(fun = 'mean', geom = 'line') +
  scale_color_manual(values = color_values_experiment_set) +
  scale_fill_manual(values = color_values_experiment_set) +
  theme_ag01() +
  force_panelsizes(rows = unit(3, 'cm'), cols = unit(3.3512, 'cm')) +
  coord_cartesian(xlim = c(-3,9), ylim = c(0, 0.6), expand = F) +
  scale_y_continuous(breaks = seq(0,0.6,0.2)) +
  ylab('Mean R') +
  xlab('Time (s)')

save_pdf(dir_output_fp_str_cor, str_c(fn_stem, '_trace', '.pdf'), 6, 4)
plt_data %>% write_csv(str_c(dir_output_fp_str_cor, fn_stem, '_trace_data.csv'))
```


```{r}
fn_stem <- 'cor_peth_pairwise_ecdf'

plt_data <- streams_peth_corr_windows %>%
  filter(var_x != var_y) %>%
  mutate(set_id = set_id %>% factor(levels = c('FR:Suc', 'WR:Suc', 'WR:NaCl'))) %>%
  mutate(time_rel_bin = factor(time_rel_bin, levels = c('Pre', 'Sustained', 'Post'))) %>%
  filter(time_rel_bin == 'Sustained')


regions <- unique(plt_data$var_x)

for(region in regions){
  loop_df <- plt_data %>%
    filter(var_x == region | var_y == region) %>%
    mutate(pairwise_region01 = region) %>%
    mutate(pairwise_region02 = case_when(
      var_x == region ~ var_y,
      var_y == region ~ var_x
    )
    ) %>%
    select(-var_x, -var_y)
  
  if(region == regions[1]){
    cor_pairwise <- loop_df
  } else {
    cor_pairwise <- loop_df %>%
      bind_rows(cor_pairwise,.)
  }
}

cor_pairwise <- cor_pairwise %>%
  group_by(subject, pairwise_region01, pairwise_region02) %>%
  summarise(r = mean(r), .groups = 'drop') %>%
  mutate(pairwise_region01 = pairwise_region01 %>% factor(levels = key_regions$region_label %>% unique()))


cor_pairwise %>%
  ggplot(aes(r, color = pairwise_region01)) +
  geom_vline(xintercept = 0, color = 'darkgrey', size = 1/3) +
  stat_ecdf() +
  theme_ag01() +
  force_panelsizes(rows = unit(3, 'cm'), cols = unit(3, 'cm')) +
  coord_cartesian(xlim = c(-1,1), ylim = c(0, 1), expand = F, clip = 'off') +
  scale_color_manual(values = color_values_regions_da) +
  theme(panel.spacing = unit(1.5, "lines")) +
  theme(strip.text = element_text(margin = margin(b = 5))) +
  xlab('Pairwise R') +
  ylab('Proportion')

cor_pairwise %>% write_csv(str_c(dir_output_fp_str_cor, fn_stem, '_data.csv'))
save_pdf(dir_output_fp_str_cor, str_c(fn_stem, '.pdf'), 6, 4)
```


```{r}
fn_stem <- 'cor_peth_sustaind_pairwisecor'

plt_data_summary <- cor_pairwise %>%
  group_by(subject, pairwise_region01) %>%
  summarise(r = mean(r), .groups = 'drop') 

plt_line <- plt_data_summary %>%
  ggplot(aes(pairwise_region01, r, group = 1)) +
  geom_hline(yintercept = 0, color = 'darkgrey', size = 1/3) +
  geom_line(aes(group = subject), size = 1/2, alpha = 1/3) +
  stat_summary(fun = 'mean', geom = 'line') +
  stat_summary(fun.data = 'mean_se', geom = 'errorbar', width = 0) +
  theme_ag01() +
  force_panelsizes(rows = unit(3, 'cm'), cols = unit(3, 'cm')) +
  coord_cartesian(xlim = c(0.5,6.5), ylim = c(-.25, 1), expand = F, clip = 'off') +
  scale_color_manual(values = color_values_regions_da) +
  theme(axis.text.x = element_text(angle = 90, hjust = 1, vjust = 0.3)) +
  xlab('Pairwise Region') +
  ylab('Pairwise R')


stats_list <- plt_data_summary %>%
  aov_rm_one_within(dir_output_fp_str_cor, fn_stem,'subject','r','pairwise_region01') 
  


plt_pairwise <- plt_line_pairwise(
      df = plt_data_summary %>% left_join(key_regions %>% rename(pairwise_region01 = region_label)), 
      dir_output = dir_output_fp_str_cor,
      fn_stem = fn_stem,
      var_dv = 'r',
      var_within = 'region' ,
      ylims = c(-1, 1)
    )


plt_line + plt_pairwise[[3]] +
    plot_layout(ncol = 2, widths = unit(3, 'cm'), heights = unit(3, 'cm')) 


cor_pairwise %>% write_csv(str_c(dir_output_fp_str_cor, fn_stem, '_data.csv'))
save_pdf(dir_output_fp_str_cor, str_c(fn_stem, '.pdf'), 6, 4)


cor_pairwise %>%
  select(subject) %>%
  unique()
```


## rep subject
```{r}
rep_subject <- 'acd01'
```

rango

```{r}
# setup import blocknames
process_blocknames <- log_data %>%
  filter(subject == rep_subject) %>%
  filter(set_id %in% c('frsuc', 'wrnacl', 'wrsuc')) %>%
  pull(blockname)

# import peth and join in subject id
df_fp_peth_rep <- combine_session_fp(process_blocknames, dir_localdata_sessions) %>%
  left_join(log_analysis_fp %>% select(blockname, subject), by = 'blockname') %>%
  left_join(log_data %>% select(blockname, set_id), by = 'blockname')


df_fp_peth_rep <- df_fp_peth_rep %>%
  filter(trial_lick == 1) %>%
  format_regions('region', key_regions)
```


```{r}
join_trial_num_solution <- df_fp_peth_rep %>%
  filter(time_rel == 0) %>%
  select(blockname, set_id, trial_num, solution) %>%
  unique() %>%
  arrange(solution, set_id, trial_num) %>%
  group_by(set_id, solution) %>%
  mutate(trial_num_solution = row_number()) 


join_trial_num_global <- df_fp_peth_rep %>%
  filter(time_rel > 0, time_rel <= 3) %>%
  group_by(blockname, set_id, solution, trial_num) %>%
  summarise(zscore_blsub_global = zscore_blsub %>% mean(), .groups = 'drop') %>%
  group_by(set_id, solution) %>%
  arrange(set_id, solution, zscore_blsub_global) %>%
  mutate(trial_num_global = row_number())
  
```

```{r, fig.width = 12, fig.height = 6}
fn_stem <- 'fp_strrepsbj_heat'

plt_data <- df_fp_peth_rep %>%
  left_join(join_trial_num_global) %>%
  filter(time_rel > -3, time_rel <= 12) %>%
  filter(set_id == 'wrnacl') 

plt_data %>%
  ggplot(aes(time_rel, trial_num_global, fill = zscore_blsub)) +
  geom_tile() +
  scale_fill_viridis_c(option = 'inferno', limits = c(-5,8), oob = scales::squish) +
  facet_grid(solution~region) +
  geom_vline(xintercept = c(0, 3), color = 'white', linewidth = 1/4) +
  theme_ag01() +
  coord_cartesian(xlim = c(-3, 12), ylim = c(0, 80), expand = F) +
  force_panelsizes(rows = unit(1.5, 'cm'), cols = unit(2.5, 'cm'))

save_pdf(dir_output_fp_str, str_c(fn_stem, '.pdf'), 9, 4)
plt_data %>% write_csv(str_c(dir_output_fp_str, fn_stem, '_data.csv'))
```

```{r, fig.width = 12, fig.height = 6}
fn_stem <- 'fp_strrepsbj_trace'

df_fp_peth_rep_summary <- df_fp_peth_rep %>%
  left_join(join_trial_num_solution) %>%
  filter(time_rel > -3, time_rel <= 12) %>%
  filter(set_id == 'wrnacl') %>%
  group_by(set_id, region, solution, time_rel) %>%
  summarise(
    zscore_blsub_sem = sd(zscore_blsub) / sqrt(n()),
    zscore_blsub = zscore_blsub %>% mean()
    )

plt <- df_fp_peth_rep_summary %>%
  ggplot(aes(time_rel, zscore_blsub, color = solution, fill = solution)) +
  annotate("rect", xmin = 0, xmax = 3, ymin = -Inf, ymax = Inf, alpha = 1/3, fill = "darkgrey") +
  geom_hline(yintercept = 0, color = 'darkgrey', size = 0.5) +
  geom_ribbon(aes(ymax = zscore_blsub + zscore_blsub_sem, ymin = zscore_blsub - zscore_blsub_sem), alpha = 1/3, color = NA) +
  geom_line() +
  facet_grid(.~region) +
  theme_ag01() +
  scale_color_manual(values = color_values_nacl) +
  scale_fill_manual(values = color_values_nacl) +
  force_panelsizes(rows = unit(2.5, 'cm'), cols = unit(2.5, 'cm'))

plt <- plt %>%
  add_scale_bar(
    origin = c(-3, -1), 
    x_len = 1, 
    y_len = 1
  )

plt 

save_pdf(dir_output_fp_str, str_c(fn_stem, '.pdf'), 9, 4)
df_fp_peth_rep_summary %>% write_csv(str_c(dir_output_fp_str, fn_stem, '_data.csv'))

```




